---
title: "summary.bins"
author: "Kevin O Brien"
date: "6 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

summary.bins Summarizing Binned Variable

### Description 

summary method for class "bins" and "optimal_bins".

### Usage 
<pre><code>

## S3 method for class 'bins'
summary(object, ...)
## S3 method for class 'bins'
print(x, ...)

</code></pre>
### Arguments
 
object an object of class "bins" and "optimal_bins", usually, a result of a call to binning().
... further arguments passed to or from other methods.

x an object of class "bins" and "optimal_bins", usually, a result of a call to binning().

### Details 

print.bins() tries to be smart about formatting the frequency of bins, binned type, number of bins.
summary.bins tries to be smart about formatting the levles, frequency of levels(bins), the ratio of
levels in total observations. And this information is data.frame object.
See vignette("transformation") for an introduction to these concepts.

### Value 

The function summary.bins() computes and returns a data.frame of summary statistics of the binned
given in object. Variables of data frame is as follows.
*  levels : levles of factor.
*  freq : frequency of levels.
*  rate : ratio of levels in total observations. it is not percentage.

### See Also
 
binning

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# Binning the carat variable. default type argument is "quantile"
bin <- binning(carseats$Income)
# Print bins class object
bin
# Summarise bins class object
summary(bin)
```

