---
title: "Untitled"
author: "Kevin O Brien"
date: "6 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


summary.transform Summarizing transformation information

### Description 

print and summary method for "transform" class.

### Usage 
<pre><code>

## S3 method for class 'transform'
summary(object, ...)

</code></pre>
### Arguments
 
object an object of class "transform", usually, a result of a call to transform().
... further arguments passed to or from other methods.

### Details 

summary.transform compares the distribution of data before and after data conversion.

### See Also
 
transform, summary.transform.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```

```{r}
# Standardization ------------------------------
advertising_minmax <- transform(carseats$Advertising, method = "minmax")
advertising_minmax
summary(advertising_minmax)
plot(advertising_minmax)
```
```{r}
# Resolving Skewness --------------------------
advertising_log <- transform(carseats$Advertising, method = "log")
advertising_log
summary(advertising_log)
plot(advertising_log)
```
