---
title: "Untitled"
author: "Kevin O Brien"
date: "6 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

summary.imputation Summarizing imputation information

### Description 

print and summary method for "imputation" class.
summary.imputation 81

### Usage 
<pre><code>

## S3 method for class 'imputation'
summary(object, ...)

</code></pre>
### Arguments
 
object an object of class "imputation", usually, a result of a call to ``imputate_na()`` or
imputate_outlier().
... further arguments passed to or from other methods.

### Details 

summary.imputation tries to be smart about formatting two kinds of imputation.

### See Also
 
imputate_na, imputate_outlier, summary.imputation.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```

```{r}
# Imputate missing values -----------------------------
# If the variable of interest is a numarical variable
income <- imputate_na(carseats, Income, US, method = "rpart")
income
summary(income)
plot(income)
# If the variable of interest is a categorical variable
urban <- imputate_na(carseats, Urban, US, method = "mice")
urban
summary(urban)
plot(urban)
```
```{r}
# Imputate outliers ----------------------------------
# If the variable of interest is a numarical variable
price <- imputate_outlier(carseats, Price, method = "capping")
price
summary(price)
plot(price)
```