---
title: "Untitled"
author: "Kevin O Brien"
date: "28 August 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

6 binning_by
binning_by Optimal Binning for Scoring Modeling

### Description 

The binning_by() finding class intervals for numerical variable using optical binning. Optimal
binning categorizes a numeric characteristic into bins for ulterior usage in scoring modeling.

### Usage 
<pre><code>

binning_by(df, y, x, p = 0.05, ordered = TRUE, labels = NULL)

</code></pre>
### Arguments
 
df a data frame.
y binary response variable (0,1). Integer(int) is required. Name of y must not have
a dot. Name "default" is not allowed.
x continuous characteristic. At least 5 different values. 
### Value 
 Inf is not allowed.
Name of x must not have a dot.
p percentage of records per bin. Default 5% (0.05). This parameter only accepts
values greater that 0.00 (0%) and lower than 0.50 (50%).
ordered whether to build an ordered factor or not.
labels the label names to use for each of the bins.

### Details 

This function is useful when used with the mutate/transmute function of the dplyr package. And
this function is implemented using smbinning() function of smbinning package.

### Value 

an object of optimal_bins class. Attributes of optimal_bins class is as follows.
*  type : binning type, "optimal".
*  breaks : the number of intervals into which x is to be cut.
*  levels : levels of binned value.
*  raw : raw data, x argument value.
*  ivtable : information value table
*  iv : information value
*  flag : information value
"optimal_bins" class attributes information
Attributes of the "optimal_bins" classs that is as follows.
*  class : "optimal_bins".
*  levels : factor or ordered factor levels
*  type : binning method
*  breaks : breaks for binning
*  raw : before the binned the raw data
*  ivtable : information value table
*  iv : information value
*  target : binary response variable
See vignette("transformation") for an introduction to these concepts.

### See Also
 
binning, smbinning.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# optimal binning
bin <- binning_by(carseats, "US", "Advertising")
bin
# summary optimal_bins class
summary(bin)
# visualize optimal_bins class
plot(bin, sub = "bins of Advertising variable")
```