---
title: "``dlookr::binning``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

Binning the Numeric Data

### Description 

The ``binning()`` converts a numeric variable to a categorization variable.

### Usage 
<pre><code>

binning(x, nbins, 
          type = c("quantile", "equal", "pretty", "kmeans", "bclust"), 
          ordered = TRUE, 
          labels = NULL)

</code></pre>
### Arguments
 
* ``x``: numeric vector for binning.
* ``nbins``: number of classes. required. if missing, nclass.Sturges is used.
* ``type``: binning method. one of "quantile", "equal", "equal", "pretty", "kmeans", "bclust"
 - The "quantile" style provides quantile breaks. 
 - The "equal" style divides the range of the variable into nbins parts. 
 - The "pretty" style chooses a number of breaks not necessarily equal to nbins using base::pretty function. 
 - The "kmeans" style uses stats::kmeans function to generate the breaks.
 - The "bclust" style uses e1071::bclust function to generate the breaks using bagged clustering. 
 - "kmeans" and "bclust" type logic was implemented by ``classInt::classIntervals`` function.

* ``ordered``: whether to build an ordered factor or not.
* ``labels``: the label names to use for each of the bins.



### Examples

```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# Binning the carat variable. default type argument is "quantile"
bin <- binning(carseats$Income)
# Print bins class object
bin
```

```{r}
# Summarise bins class object
summary(bin)
```

```{r}
# Plot bins class object
plot(bin)
# Using labels argument
bin <- binning(carseats$Income, nbins = 4,
labels = c("LQ1", "UQ1", "LQ3", "UQ3"))
bin
```

```{r}
# Using another type argument
bin <- binning(carseats$Income, nbins = 5, type = "equal")
bin
bin <- binning(carseats$Income, nbins = 5, type = "pretty")
bin
bin <- binning(carseats$Income, nbins = 5, type = "kmeans")
bin
bin <- binning(carseats$Income, nbins = 5, type = "bclust")
bin
```

### Using pipes & dplyr

```{r}
library(dplyr)
carseats %>%
mutate(Income_bin = binning(carseats$Income)) %>%
group_by(ShelveLoc, Income_bin) %>%
summarise(freq = n()) %>%
arrange(desc(freq)) %>%
head(10)
```

### Details 

This function is useful when used with the mutate/transmute function of the dplyr package.

### Value 

An object of bins class. Attributes of bins class is as follows.
*  type : binning type, "quantile", "equal", "pretty", "kmeans", "bclust".
*  breaks : the number of intervals into which x is to be cut.
*  levels : levels of binned value.
*  raw : raw data, x argument value.
"bins" class attributes information
Attributes of the "bins" classs that is as follows.
*  class : "bins".
*  levels : factor or ordered factor levels
binning 5
*  type : binning method
*  breaks : breaks for binning
*  raw : before the binned the raw data
See vignette("transformation") for an introduction to these concepts.

### See Also
 
binning_by, print.bins, summary.bins.