---
title: "``dlookr::describe``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

describe Compute descriptive statistic

### Description 

The describe() compute descriptive statistic of numeric variable for exploratory data analysis.

### Usage 
<pre><code>

describe(.data, ...)
## S3 method for class 'data.frame'
describe(.data, ...)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* ... one or more unquoted expressions separated by commas. You can treat variable names like they are positions. Positive values select variables; negative values to drop variables. If the first expression is negative, describe() will automatically start with all variables. 
 - These arguments are automatically quoted and evaluated in a context where column names represent column positions. They support unquoting and splicing.
 - See vignette("EDA") for an introduction to these concepts.




### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# Describe descriptive statistics of numerical variables
describe(carseats)
# Select the variable to describe
describe(carseats, Sales, Price)
describe(carseats, -Sales, -Price)
describe(carseats, 5)
```

```{r}
# Using dplyr::grouped_dt
library(dplyr)
gdata <- group_by(carseats, ShelveLoc, US)
describe(gdata, "Income")
# Using pipes ---------------------------------
# Positive values select variables
carseats %>%
describe(Sales, CompPrice, Income)
# Negative values to drop variables
carseats %>%
describe(-Sales, -CompPrice, -Income)
```

```{r}
# Using pipes & dplyr -------------------------
# Find the statistic of all numerical variables by 'ShelveLoc' and 'US',
# and extract only those with 'ShelveLoc' variable level is "Good".
carseats %>%
group_by(ShelveLoc, US) %>%
describe() %>%
filter(ShelveLoc == "Good")
# extract only those with 'Urban' variable level is "Yes",
# and find 'Sales' statistics by 'ShelveLoc' and 'US'
carseats %>%
filter(Urban == "Yes") %>%
group_by(ShelveLoc, US) %>%
describe(Sales)

```

### Details 

This function is useful when used with the group_by function of the dplyr package. If you want
to calculate the statistic by level of the categorical data you are interested in, rather than the whole
statistic, you can use grouped_df as the group_by() function.

### Value 

An object of the same class as .data.
Descriptive statistic information
The information derived from the numerical data describe is as follows.
*  n : number of observations excluding missing values
*  na : number of missing values
*  mean : arithmetic average
*  sd : standard devation
*  se_mean : standrd error mean. sd/sqrt(n)
*  IQR : interquartile range (Q3-Q1)
*  skewness : skewness
*  kurtosis : kurtosis
*  p25 : Q1. 25% percentile
*  p50 : median. 50% percentile
*  p75 : Q3. 75% percentile
*  p01, p05, p10, p20, p30 : 1%, 5%, 20%, 30% percentiles
*  p40, p60, p70, p80 : 40%, 60%, 70%, 80% percentiles
*  p90, p95, p99, p100 : 90%, 95%, 99%, 100% percentiles

### See Also
 
describe.tbl_dbi, diagnose_numeric.data.frame.