---
title: "Untitled"
author: "Kevin O Brien"
date: "28 August 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
eda_report.tbl_dbi Reporting the information of EDA for table of the DBMS

### Description 

The eda_report() report the information of Exploratory data analysis for object inheriting from the
DBMS table through tbl_dbi

### Usage 
<pre><code>

## S3 method for class 'tbl_dbi'
eda_report(.data, target = NULL,
output_format = c("pdf", "html"), output_file = NULL,
font_family = NULL, output_dir = tempdir(), ``in_database = FALSE``,
collect_size = Inf, ...)

</code></pre>
### Arguments
 
* `.data``:   a tbl_dbi.
* ``target``: target variable.
output_format report output type. Choose either "pdf" and "html". "pdf" create pdf file by
knitr::knit(). "html" create html file by rmarkdown::render().
output_file name of generated file. default is NULL.
font_family charcter. font family name for figure in pdf.
output_dir name of directory to generate report file. default is tempdir().
* ``in_database``: Specifies whether to perform in-database operations. If TRUE, most operations
are performed in the DBMS. if FALSE, table data is taken in R and operated
in-memory. Not yet supported in_database = TRUE.
* ``collect_size``: a integer. The number of data samples from the DBMS to R. Applies only if
``in_database = FALSE``.
* ``...``: arguments to be passed to methods.
eda_report.tbl_dbi 41

### Details 

Generate generalized data EDA reports automatically. You can choose to output to pdf and html
files. This is useful for EDA a data frame with a large number of variables than data with a small
number of variables. For pdf output, Korean Gothic font must be installed in Korean operating
system.
Reported information
The EDA process will report the following information:
*  Introduction
- Information of Dataset
- Information of Variables
- About EDA Report
*  Univariate Analysis
- Descriptive Statistics
- Normality Test of Numerical Variables
* Statistics and Visualization of (Sample) Data
*  Relationship Between Variables
- Correlation Coefficient
* Correlation Coefficient by Variable Combination
* Correlation Plot of Numerical Variables
*  Target based Analysis
- Gruoped Descriptive Statistics
* Gruoped Numerical Variables
* Gruoped Categorical Variables
- Gruoped Relationship Between Variables
* Grouped Correlation Coefficient
* Grouped Correlation Plot of Numerical Variables
See vignette("EDA") for an introduction to these concepts.

### See Also
 
eda_report.data.frame.

### Examples
```{r}

library(dplyr)
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA

# connect DBMS
con_sqlite <- DBI::dbConnect(RSQLite::SQLite(), ":memory:")
# copy carseats to the DBMS with a table named TB_CARSEATS
copy_to(con_sqlite, carseats, name = "TB_CARSEATS", overwrite = TRUE)
## target variable is categorical variable
# reporting the EDA information
# create pdf file. file name is EDA_Report.pdf
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(US)
# create pdf file. file name is EDA.pdf
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report("US", output_file = "EDA.pdf")
# create html file. file name is EDA_Report.html
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report("US", output_format = "html")
# create html file. file name is EDA.html
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(US, output_format = "html", output_file = "EDA.html")
## target variable is numerical variable
# reporting the EDA information, and collect size is 350
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(Sales, collect_size = 350)
# create pdf file. file name is EDA2.pdf
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report("Sales", output_file = "EDA2.pdf")
# create html file. file name is EDA_Report.html
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report("Sales", output_format = "html")
# create html file. file name is EDA2.html
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(Sales, output_format = "html", output_file = "EDA2.html")
## target variable is null
# reporting the EDA information
con_sqlite %>%
tbl("TB_CARSEATS") %>%
find_class 43
eda_report()
# create pdf file. file name is EDA2.pdf
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(output_file = "EDA2.pdf")
# create html file. file name is EDA_Report.html
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(output_format = "html")
# create html file. file name is EDA2.html
con_sqlite %>%
tbl("TB_CARSEATS") %>%
eda_report(output_format = "html", output_file = "EDA2.html")
```
