---
title: "``eda_report``"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

eda_report Reporting the information of EDA

### Description 

The eda_report() report the information of Exploratory data analysis for object inheriting from
data.frame.

### Usage 
<pre><code>

eda_report(.data, ...)
## S3 method for class 'data.frame'
eda_report(.data, target = NULL,
output_format = c("pdf", "html"), output_file = NULL,
output_dir = tempdir(), font_family = NULL, browse = TRUE, ...)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* ``...``: arguments to be passed to methods.
* ``target``: target variable.
* ``output_format``: report output type. Choose either "pdf" and "html". "pdf" create pdf file by knitr::knit(). "html" create html file by ``rmarkdown::render()``.
* ``output_file``: name of generated file. default is NULL.
* ``output_dir``: name of directory to generate report file. default is tempdir().
* ``font_family``: charcter. font family name for figure in pdf.
* ``browse``: logical. choose whether to output the report results to the browser.



### Examples

```{r}

library(dplyr)
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
## target variable is categorical variable
```


```{r}
# reporting the EDA information
# create pdf file. file name is EDA_Report.pdf
eda_report(carseats, US)
# create pdf file. file name is EDA.pdf
eda_report(carseats, "US", output_file = "EDA.pdf")
# create pdf file. file name is EDA.pdf and not browse
eda_report(carseats, "US", output_dir = ".", output_file = "EDA.pdf", browse = FALSE)
# create html file. file name is EDA_Report.html
eda_report(carseats, "US", output_format = "html")
```

```{r}
# create html file. file name is EDA.html
eda_report(carseats, US, output_format = "html", output_file = "EDA.html")
## target variable is numerical variable
# reporting the EDA information
eda_report(carseats, Sales)
# create pdf file. file name is EDA2.pdf
```



```{r}
eda_report(carseats, "Sales", output_file = "EDA2.pdf")
# create html file. file name is EDA_Report.html
eda_report(carseats, "Sales", output_format = "html")
# create html file. file name is EDA2.html
eda_report(carseats, Sales, output_format = "html", output_file = "EDA2.html")
## target variable is null
# reporting the EDA information
```


```{r}
eda_report(carseats)
# create pdf file. file name is EDA2.pdf
eda_report(carseats, output_file = "EDA2.pdf")
# create html file. file name is EDA_Report.html
eda_report(carseats, output_format = "html")
# create html file. file name is EDA2.html
eda_report(carseats, output_format = "html", output_file = "EDA2.html")
```

### Details 

Generate generalized data EDA reports automatically. You can choose to output to pdf and html
files. This is useful for EDA a data frame with a large number of variables than data with a small
number of variables. For pdf output, Korean Gothic font must be installed in Korean operating
system.
Reported information
The EDA process will report the following information:
*  Introduction
- Information of Dataset
- Information of Variables
- About EDA Report
*  Univariate Analysis
- Descriptive Statistics
- Normality Test of Numerical Variables
* Statistics and Visualization of (Sample) Data
*  Relationship Between Variables
- Correlation Coefficient
* Correlation Coefficient by Variable Combination
* Correlation Plot of Numerical Variables
*  Target based Analysis
eda_report 39
- Gruoped Descriptive Statistics
* Gruoped Numerical Variables
* Gruoped Categorical Variables
- Gruoped Relationship Between Variables
* Grouped Correlation Coefficient
* Grouped Correlation Plot of Numerical Variables
See vignette("EDA") for an introduction to these concepts.