---
title: "``dlookr::normality``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```
 Performs the Shapiro-Wilk test of normality

### Description 

The normality() performs Shapiro-Wilk test of normality of numeric values.

### Usage 
<pre><code>

normality(.data, ...)

## S3 method for class 'data.frame'
normality(.data, ..., sample = 5000)

</code></pre>

### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* ``...``: one or more unquoted expressions separated by commas. You can treat variable names like they are positions. 
 - Positive values select variables; negative values to drop variables. If the first expression is negative, ``normality()`` will automatically start with all variables.
 - These arguments are automatically quoted and evaluated in a context where column names represent column positions. They support unquoting and splicing.
* ``sample``:  the numer of samples to perform the test.

 - See vignette("EDA") for an introduction to these concepts.



### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# Normality test of numerical variables
```

```{r}
normality(carseats)
# Select the variable to describe
normality(carseats, Sales, Price)
normality(carseats, -Sales, -Price)
normality(carseats, 1)
normality(carseats, Sales, Price, sample = 300)
```

```{r}
# Using dplyr::grouped_dt
library(dplyr)
gdata <- group_by(carseats, ShelveLoc, US)
normality(gdata, "Sales")
normality(gdata, sample = 250)
```

```{r}
# Using pipes ---------------------------------
# Normality test of all numerical variables
carseats %>%
normality()
# Positive values select variables
carseats %>%
normality(Sales, Price)
# Positions values select variables
carseats %>%
normality(1)
```

```{r}
# Using pipes & dplyr -------------------------
# Test all numerical variables by 'ShelveLoc' and 'US',
# and extract only those with 'ShelveLoc' variable level is "Good".
carseats %>%
group_by(ShelveLoc, US) %>%
normality() %>%
filter(ShelveLoc == "Good")
```

```{r}
# extract only those with 'Urban' variable level is "Yes",
# and test 'Sales' by 'ShelveLoc' and 'US'
carseats %>%
  filter(Urban == "Yes") %>%
  group_by(ShelveLoc, US) %>%
  normality(Sales)
```

```{r}
# Test log(Income) variables by 'ShelveLoc' and 'US',
# and extract only p.value greater than 0.01.
carseats %>%
mutate(log_income = log(Income)) %>%
group_by(ShelveLoc, US) %>%
normality(log_income) %>%
filter(p_value > 0.01)
```

### Details 

This function is useful when used with the group_by function of the dplyr package. If you want to test by level of the categorical data you are interested in, rather than the whole observation, you can use ``group_tf`` as the ``group_by`` function. This function is computed shapiro.test function.

### Value 

An object of the same class as .data.
Normality test information
The information derived from the numerical data test is as follows.
*  statistic : the value of the Shapiro-Wilk statistic.
*  p_value : an approximate p-value for the test. This is said in Roystion(1995) to be adequate
for p_value < 0.1.
*  sample : the numer of samples to perform the test. The number of observations supported by
the stats::shapiro.test function is 3 to 5000.
normality 55

### See Also
 
normality.tbl_dbi, diagnose_numeric.data.frame, describe.data.frame, plot_normality.data.frame.