---
title: "``dlookr::print.relate``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```


 Summarizing relate information

### Description 

print and summary method for "relate" class.

### Usage 
<pre><code>

## S3 method for class 'relate'
print(x, ...)
76 print.relate

</code></pre>
### Arguments
 
x an object of class "relate", usually, a result of a call to relate().
... further arguments passed to or from other methods.

### Details 

print.relate tries to be smart about formatting four kinds of relate. summary.relate tries to be smart
about formatting four kinds of relate.

### See Also
 
plot.relate.

### Examples
```{r}

## Not run:
# Generate data for the example
diamonds2 <- diamonds
diamonds2[sample(seq(NROW(diamonds2)), 250), "price"] <- NA
diamonds2[sample(seq(NROW(diamonds2)), 20), "clarity"] <- NA
```

```{r}
# Binning the carat variable. default type argument is "quantile"
bin <- binning(diamonds2$carat)
# Print bins class object
bin
# Summarise bins class object
summary(bin)
```

```{r}
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```

```{r}
# If the target variable is a categorical variable
categ <- target_by(carseats, US)
# If the variable of interest is a numarical variable
cat_num <- relate(categ, Sales)
cat_num
summary(cat_num)
plot(cat_num)
```

```{r}
# If the variable of interest is a categorical variable
cat_cat <- relate(categ, ShelveLoc)
cat_cat
summary(cat_cat)

plot(cat_cat)
```

```{r}
##---------------------------------------------------
# If the target variable is a categorical variable
num <- target_by(carseats, Sales)
# If the variable of interest is a numarical variable
num_num <- relate(num, Price)
num_num
summary(num_num)
plot(num_num)
```

```{r}
# If the variable of interest is a categorical variable
num_cat <- relate(num, ShelveLoc)
num_cat
summary(num_cat)
plot(num_cat)
```