---
title: "``dlookr::relate``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

Relationship between target variable and variable of interest

### Description 

The relationship between the target variable and the variable of interest (predictor) is briefly analyzed.

### Usage 
<pre><code>
relate(.data, predictor)
</code></pre>

### Arguments
 
* ``.data``: A target_df.
* ``predictor``: variable of interest. predictor.

See vignette("relate") for an introduction to these concepts.



### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# If the target variable is a categorical variable
categ <- target_by(carseats, US)
```
```{r}
# If the variable of interest is a numarical variable
cat_num <- relate(categ, Sales)
cat_num
summary(cat_num)
plot(cat_num)
```

```{r}
# If the variable of interest is a categorical variable
cat_cat <- relate(categ, ShelveLoc)
cat_cat
summary(cat_cat)
plot(cat_cat)
```
```{r}
##---------------------------------------------------
# If the target variable is a categorical variable
num <- target_by(carseats, Sales)
# If the variable of interest is a numarical variable
num_num <- relate(num, Price)
num_num
summary(num_num)
plot(num_num)
```

```{r}
# If the variable of interest is a categorical variable
num_cat <- relate(num, ShelveLoc)
num_cat
summary(num_cat)
plot(num_cat)
```

### Details 

Returns the four types of results that correspond to the combination of the target variable and the
data type of the variable of interest.
*  target variable: categorical variable
- predictor: categorical variable
* contegency table
* c("xtabs", "table") class
- predictor: numerical variable
* descriptive statistic for each levles and total observation.
78 relate
*  target variable: numerical variable
- predictor: categorical variable
* ANOVA test. "lm" class.
- predictor: numerical variable
* simple linear model. "lm" class.

### Value 

An object of the class as relate. Attributes of relate class is as follows.
*  target : name of target variable
*  predictor : name of predictor
*  model : levels of binned value.
*  raw : table_df with two variables target and predictor.
Descriptive statistic information
The information derived from the numerical data describe is as follows.
*  mean : arithmetic average
*  sd : standard devation
*  se_mean : standrd error mean. sd/sqrt(n)
*  IQR : interqurtle range (Q3-Q1)
*  skewness : skewness
*  kurtosis : kurtosis
*  p25 : Q1. 25% percentile
*  p50 : median. 50% percentile
*  p75 : Q3. 75% percentile
*  p01, p05, p10, p20, p30 : 1%, 5%, 20%, 30% percentiles
*  p40, p60, p70, p80 : 40%, 60%, 70%, 80% percentiles
*  p90, p95, p99, p100 : 90%, 95%, 99%, 100% percentiles

### See Also
 
print.relate, plot.relate.

