---
title: "Untitled"
author: "Kevin O Brien"
date: "6 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
target_by Target by one variables

### Description 

In the data analysis, a target_df class is created to identify the relationship between the target variable
and the other variable.

### Usage 
<pre><code>

target_by(.data, target, ...)
## S3 method for class 'data.frame'
target_by(.data, target, ...)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* ``target``: target variable.
* ``...``: arguments to be passed to methods.

### Details 

Data analysis proceeds with the purpose of predicting target variables that correspond to the facts
of interest, or examining associations and relationships with other variables of interest. Therefore,
it is a major challenge for EDA to examine the relationship between the target variable and its corresponding
variable. Based on the derived relationships, analysts create scenarios for data analysis.
target_by() inherits the grouped_df class and returns a target_df class containing information about
the target variable and the variable.
See vignette("EDA") for an introduction to these concepts.

### Value 

an object of target_df class. Attributes of target_df class is as follows.
*  type_y : the data type of target variable.

### See Also
 
relate.
84 target_by.tbl_dbi

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# If the target variable is a categorical variable
categ <- target_by(carseats, US)
# If the variable of interest is a numarical variable
cat_num <- relate(categ, Sales)
cat_num
summary(cat_num)
plot(cat_num)
```
```{r}
# If the variable of interest is a categorical variable
cat_cat <- relate(categ, ShelveLoc)
cat_cat
summary(cat_cat)
plot(cat_cat)
```
```{r}
##---------------------------------------------------
# If the target variable is a categorical variable
num <- target_by(carseats, Sales)
# If the variable of interest is a numarical variable
num_num <- relate(num, Price)
num_num
summary(num_num)
plot(num_num)
```
```{r}
# If the variable of interest is a categorical variable
num_cat <- relate(num, ShelveLoc)
num_cat
summary(num_cat)
plot(num_cat)
```
