---
title: "``dlookr::transformation_report()``"
author: "Kevin O Brien"
date: "6 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

transformation_report Reporting the information of transformation

### Description 

The transformation_report() report the information of transformate numerical variables for object
inheriting from data.frame.

### Usage 
<pre><code>

transformation_report(.data, target = NULL, output_format = c("pdf",
"html"), output_file = NULL, output_dir = tempdir(),
font_family = NULL, browse = TRUE)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* ``target``: target variable. If the target variable is not specified, the method of using the
target variable information is not performed when the missing value is imputed.
and Optimal binning is not performed if the target variable is not a binary class.
output_format report output type. Choose either "pdf" and "html". "pdf" create pdf file by
knitr::knit(). "html" create html file by rmarkdown::render().
output_file name of generated file. default is NULL.
output_dir name of directory to generate report file. default is tempdir().
font_family charcter. font family name for figure in pdf.
browse logical. choose whether to output the report results to the browser.

### Details 

Generate transformation reports automatically. You can choose to output to pdf and html files. This
is useful for Binning a data frame with a large number of variables than data with a small number
of variables. For pdf output, Korean Gothic font must be installed in Korean operating system.
Reported information
The transformation process will report the following information:
*  Imputation
- Missing Value 

* * Variable names including missing value
- Outliers
* * Variable names including outliers
*  Resolving Skewness
- Skewed variables information

* * Variable names with an absolute value of skewness greater than or equal to 0.5
*  Binning
- Numerical Variables for Binning
- Binning
* Numeric variable names
- Optimal Binning
* Numeric variable names
See vignette("transformation") for an introduction to these concepts.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# reporting the Binning information -------------------------
```

```{r}
# create pdf file. file name is Transformation_Report.pdf & No target variable
transformation_report(carseats)
# create pdf file. file name is Transformation_Report.pdf
transformation_report(carseats, US)
```

```{r}
# create pdf file. file name is Transformation.pdf
transformation_report(carseats, "US", output_file = "Transformation.pdf")
# create html file. file name is Transformation_Report.html
transformation_report(carseats, "US", output_format = "html")
```

```{r}
# create html file. file name is Transformation.html
transformation_report(carseats, US, output_format = "html", output_file = "Transformation.html")
```