---
title: "``dlookr::transform``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

## Data Transformations

### Description 

Performs variable transformation for standardization and resolving skewness of numerical variables.

### Usage 
<pre><code>

transform(x, method = c("zscore", "minmax", "log", "log+1", "sqrt","1/x", "x^2", "x^3"))

</code></pre>
### Arguments
 
* ``x``: numeric vector for transformation.
* ``method``: method of transformations.



### See Also
 
summary.transform, plot.transform.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```

```{r}
# Standardization ------------------------------
advertising_minmax <- transform(carseats$Advertising, method = "minmax")
advertising_minmax
summary(advertising_minmax)
plot(advertising_minmax)
```

```{r}
# Resolving Skewness --------------------------
advertising_log <- transform(carseats$Advertising, method = "log")
advertising_log
summary(advertising_log)
plot(advertising_log)
```

### Using dplyr

```{r}

library(dplyr)

carseats %>%
  mutate(Advertising_log = transform(Advertising, method = "log+1")) %>%
  lm(Sales ~ Advertising_log, data = .)
```


### Value 

An object of transform class. Attributes of transform class is as follows.

*  method : method of transformation data.

####  Standardization

* "zscore" : z-score transformation. (x - mu) / sigma
* "minmax" : minmax transformation. (x - min) / (max - min)

#### Resolving Skewness

* "log" : log transformation. log(x)
* "log+1" : log transformation. log(x + 1). Used for values that contain 0.
* "sqrt" : square root transformation.
* "1/x" : 1 / x transformation
* "x^2" : x square transformation
* "x^3" : x^3 square transformation

### Details 

transform() creates an transform class. The 'transform' class includes original data, transformed
data, and method of transformation.
See vignette("transformation") for an introduction to these concepts.
transform 87
