---
title: "ds_cross_table "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```

##  Two way table

#### Description 
 
Creates two way tables of categorical variables. The tables created can be visualized as barplots
and mosaicplots.

#### Usage 
<pre><code>

ds_cross_table(data, var1, var2)
## S3 method for class 'ds_cross_table'
plot(x, stacked = FALSE, proportional = FALSE, ...)
ds_twoway_table(data, var1, var2)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* ``var1``:  First categorical variable.
var2 Second categorical variable.
* ``x`` : An object of class cross_table.
* stacked If FALSE, the columns of height are portrayed as stacked bars, and if TRUE the
columns are portrayed as juxtaposed bars.
* proportional If TRUE, the height of the bars is proportional.
... Further Arguments to be passed to or from methods.

#### Deprecated function
ds_cross_table() has been deprecated. Instead use ds_cross_table().

#### Examples 
```{r}

k <- ds_cross_table(mtcarz, cyl, gear)
k
# bar plots
plot(k)
plot(k, stacked = TRUE)
plot(k, proportional = TRUE)
# alternate
ds_twoway_table(mtcarz, cyl, gear)
```
