---
title: "``ds_freq_table ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```

Frequency table

#### Description 
 
* Frequency table for factor data and returns the frequency, cumulative frequency, frequency percent and cumulative frequency percent. 
* ``barplot.ds_freq_table()`` creates bar plot for the frequency table created using ``ds_freq_table()``.

#### Usage 
<pre><code>

ds_freq_table(data, variable)
## S3 method for class 'ds_freq_table'
plot(x, ...)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* ``variable`` :   Column in data.
* ``x`` : An object of class ds_freq_table.
* ... Further Arguments to be passed to or from methods.



#### Examples 
```{r}

# frequency table
ds_freq_table(mtcarz, cyl)
# barplot
k <- ds_freq_table(mtcarz, cyl)
plot(k)
```

#### Value
ds_freq_table returns an object of class "ds_freq_table". An object of class "ds_freq_table"
is a list containing the following components:
ftable Frequency table.

#### Deprecated function
freq_table() has been deprecated. Instead use ds_freq_table().

#### See Also
ds_freq_cont ds_cross_table
