plotmo
Plot a model’s response over a range of predictor values (the model
surface)

#### Description

Plot model surfaces for a wide variety of models.
This function plots the model’s response when varying one or two predictors while holding the other
predictors constant (a poor man’s partial-dependence plot).
It can also generate partial-dependence plots (by specifying pmethod="partdep").
Please see the plotmo vignette (also available here).

#### Usage

plotmo(object=stop("no 'object' argument"),
type=NULL, nresponse=NA, pmethod="plotmo",
pt.col=0, jitter=.5, smooth.col=0, level=0,
func=NULL, inverse.func=NULL, nrug=0, grid.col=0,
type2="persp",
degree1=TRUE, all1=FALSE, degree2=TRUE, all2=FALSE,
do.par=TRUE, clip=TRUE, ylim=NULL, caption=NULL, trace=0,
grid.func=NULL, grid.levels=NULL, extend=0,
ngrid1=50, ngrid2=20, ndiscrete=5, npoints=3000,
center=FALSE, xflip=FALSE, yflip=FALSE, swapxy=FALSE, int.only.ok=TRUE,
...)

#### Arguments

object The model object.
type Type parameter passed to predict. For allowed values see the predict method
for your object (such as predict.earth). By default, plotmo tries to automat-
ically select a suitable value for the model in question (usually "response") but
this will not always be correct. Use trace=1 to see the type argument passed
to predict.
nresponse Which column to use when predict returns multiple columns. This can be a
column index, or a column name if the predict method for the model returns
column names. The column name may be abbreviated, partial matching is used.
pmethod Plotting method. One of:
"plotmo" (default) Classic plotmo plots i.e. the background variables are fixed
at their medians (or first level for factors).
"partdep" Partial dependence plots, i.e. at each point the effect of the back-
ground variables is averaged.
"apartdep" Approximate partial dependence plots. Faster than "partdep" es-
pecially for big datasets. Like "partdep" but the background variables are av-
eraged over a subset of ngrid1 cases (default 50), rather than all cases in theplotmo
3
training data. The subset is created by selecting rows at equally spaced inter-
vals from the training data after sorting the data on the response values (ties are
randomly broken).
The same background subset of ngrid1 cases is used for both degree1 and de-
gree2 plots.
pt.col The color of response points (or response sites in degree2 plots). This refers to
the response y in the data used to build the model. Note that the displayed points
are jittered by default (see the jitter argument).
Default is 0, display no response points.
This can be a vector, like all such arguments – for example pt.col = as.numeric(survived)+2
to color points by their survival class.
You can modify the plotted points with pt.pch, pt.cex, etc. (these get passed
via plotmo’s “...” argument). For example, pt.cex = weights to size points
by their weight. To label the points, set pt.pch to a character vector.
jitter Applies only if pt.col is specified.
The default is jitter=.5, automatically apply some jitter to the points. Points
are jittered horizontally and vertically.
Use jitter=0 to disable this automatic jittering. Otherwise something like
jitter=1, but the optimum value is data dependent.
smooth.col Color of smooth line through the response points. (The points themselves will
not be plotted unless pt.col is specified.) Default is 0, no smooth line.
Example:
mod <- lm(Volume~Height, data=trees)
plotmo(mod, pt.color=1, smooth.col=2)
You can adjust the amount of smoothing with smooth.f. This gets passed as f
to lowess. The default is .5. Lower values make the line more wiggly.
level
Draw estimated confidence or prediction interval bands at the given level, if
the predict method for the model supports them.
Default is 0, bands not plotted. Else a fraction, for example level=.95. See
“Prediction intervals” in the plotmo vignette. Example:
mod <- lm(log(Volume)~log(Girth), data=trees)
plotmo(mod, level=.95)
You can modify the color of the bands with level.shade and level.shade2.
func
Superimpose func(x) on the plot. Example:
mod <- lm(Volume~Girth, data=trees)
estimated.volume <- function(x) .17 * x$Girth^2
plotmo(mod, pt.col=2, func=estimated.volume)
The func is called for each plot with a single argument which is a dataframe
with columns in the same order as the predictors in the formula or x used to
build the model. Use trace=2 to see the column names and first few rows of
this dataframe.
inverse.func
A function applied to the response before plotting. Useful to transform a trans-
formed response back to the original scale. Example:4
plotmo
mod <- lm(log(Volume)~., data=trees)
plotmo(mod, inverse.func=exp)
# exp() is inverse of log()
nrug
grid.col
type2
Number of ticks in the rug along the bottom of the plot
Default is 0, no rug.
Use nrug=TRUE for all the points.
Else specify the number of quantiles e.g. use nrug=10 for ticks at the 0, 10, 20,
..., 100 percentiles.
Modify the rug ticks with rug.col, rug.lwd, etc.
The special value nrug="density" means plot the density of the points along
the bottom. Modify the density plot with density.adjust (default is .5),
density.col, density.lty, etc.
Default is 0, no grid. Else add a background grid of the specified color to the
degree1 plots. The special value grid.col=TRUE is treated as "lightgray".
Degree2 plot type. One of "persp" (default), "image", or "contour". You
can pass arguments to these functions if necessary by using persp., image., or
contour. as a prefix. 
#### Examples
```{r}:
plotmo(mod, persp.ticktype="detailed", persp.nticks=3)
plotmo(mod, type2="image")
plotmo(mod, type2="image", image.col=heat.colors(12))
plotmo(mod, type2="contour", contour.col=2, contour.labcex=.4)
degree1
An index vector specifying which subset of degree1 (main effect) plots to in-
clude (after selecting the relevant predictors as described in “Which variables
are plotted?” in the plotmo vignette).
Default is TRUE, meaning all (the TRUE gets recycled). To plot only the third plot
use degree1=3. For no degree1 plots use degree1=0.
Note that degree1 indexes plots on the page, not columns of x. Probably the
easiest way to use this argument (and degree2) is to first use the default (and
possibly all1=TRUE) to plot all figures. This shows how the figures are num-
bered. Then replot using degree1 to select the figures you want, for example
degree1=c(1,3,4).
Can also be a character vector specifying which variables to plot. 
#### Examples
```{r}:
degree1="wind"
degree1=c("wind", "vis").
all1
degree2
Variables names are matched with grep. Thus "wind" will match all variables
with "wind" anywhere in their name. Use "^wind$" to match only the variable
named "wind".
Default is FALSE. Use TRUE to plot all predictors, not just those usually selected
by plotmo.
The all1 argument increases the number of plots; the degree1 argument re-
duces the number of plots.
An index vector specifying which subset of degree2 (interaction) plots to in-
clude.plotmo
5
Default is TRUE meaning all (after selecting the relevant interaction terms as de-
scribed in “Which variables are plotted?” in the plotmo vignette).
all2
do.par
clip
ylim
caption
trace
grid.func
Can also be a character vector specifying which variables to plot (grep is used
for matching). 
#### Examples
```{r}:
degree2="wind" plots all degree2 plots for the wind variable.
degree2=c("wind", "vis") plots just the wind:vis plot.
Default is FALSE. Use TRUE to plot all pairs of predictors, not just those usually
selected by plotmo.
One of NULL, FALSE, TRUE, or 2, as follows:
do.par=NULL. Same as do.par=FALSE if the number of plots is one; else the
same as TRUE.
do.par=FALSE. Use the current par settings. You can pass additional graphics
parameters in the “...” argument.
do.par=TRUE (default). Start a new page and call par as appropriate to display
multiple plots on the same page. This automatically sets parameters like mfrow
and mar. You can pass additional graphics parameters in the “...” argument.
do.par=2. Like do.par=TRUE but don’t restore the par settings to their original
state when plotmo exits, so you can add something to the plot.
The default is clip=TRUE, meaning ignore very outlying predictions when deter-
mining the automatic ylim. This keeps ylim fairly compact while still covering
all or nearly all the data, even if there are a few crazy predicted values. See “The
ylim and clip arguments” in the plotmo vignette.
Use clip=FALSE for no clipping.
Three possibilities:
ylim=NULL (default). Automatically determine a ylim to use across all graphs.
ylim=NA. Each graph has its own ylim.
ylim=c(ymin,ymax). Use the specified limits across all graphs.
Overall caption. By default create the caption automatically. Use caption=""
for no caption. (Use main to set the title of individual plots, can be a vector.)
Default is 0.
trace=1 (or TRUE) for a summary trace (shows how predict is invoked for the
current object).
trace=2 for detailed tracing.
trace=-1 inhibits the messages usually issued by plotmo, like the plotmo grid:,
calculating partdep, and nothing to plot messages. Error and warning
messages will be printed as usual.
Function applied to columns of the x matrix to pin the values of variables not on
the axis of the current plot (the “background” variables).
The default is a function which for numeric variables returns the median and
for logical and factors variables returns the value occurring most often in the
training data.

#### Examples
```{r}:6
plotmo
plotmo(mod, grid.func=mean)
grid.func <- function(x, ...) quantile(x)[2] # 25% quantile
plotmo(mod, grid.func=grid.func)
grid.levels
This argument is not related to the grid.col argument.
This argument can be overridden for specific variables—see grid.levels be-
low.
Default is NULL. Else a list of variables and their fixed value to be used when
the variable is not on the axis. Supersedes grid.func for variables in the list.
Names and values can be abbreviated, partial matching is used. Example:
plotmo(mod, grid.levels=list(sex="m", age=21))
extend
ngrid1
ngrid2
npoints
ndiscrete
int.only.ok
center
xflip
Amount to extend the horizontal axis in each plot. The default is 0, do not
extend (i.e. use the range of the variable in the training data). Else something
like extend=.5, which will extend both the lower and upper xlim of each plot
by 50%.
This argument is useful if you want to see how the model performs on data that is
beyond the training data; for example, you want to see how a time-series model
performs on future data.
This argument is currently implemented only for degree1 plots. Factors and
discrete variables (see the ndiscrete argument) are not extended.
Number of equally spaced x values in each degree1 plot. Default is 50. Also
used as the number of background cases for pmethod="apartdep".
Grid size for degree2 plots (ngrid2 x ngrid2 points are plotted). Default is
20.
The default will sometimes be too small for contour and image plots.
With large ngrid2 values, persp plots look better with persp.border=NA.
Number of response points to be plotted (a sample of npoints points is plotted).
Applies only if pt.col is specified.
The default is 3000 (not all, to avoid overplotting on large models). Use npoints=TRUE
or -1 for all points.
Default 5 (a somewhat arbitrary value). Variables with no more than ndiscrete
unique values are plotted as quantized in plots (a staircase rather than a curve).
Factors are always considered discrete. Variables with non-integer values are
always considered non-discrete.
Use ndiscrete=0 if you want to plot the response for a variable with just a few
integer values as a line or a curve, rather than a staircase.
Plot the model even if it is an intercept-only model (no predictors are used in the
model). Do this by plotting a single degree1 plot for the first predictor.
The default is TRUE. Use int.only.ok=FALSE to instead issue an error message
for intercept-only models.
Center the plotted response. Default is FALSE.
Default FALSE. Use TRUE to flip the direction of the x axis. This argument (and
yflip and swapxy) is useful when comparing to a plot from another source and
you want the axes to be the same. (Note that xflip and yflip cannot be used
on the persp plots, a limitation of the persp function.)plotmo
7
yflip Default FALSE. Use TRUE to flip the direction of the y axis of the degree2 graphs.
swapxy Default FALSE. Use TRUE to swap the x and y axes on the degree2 graphs.
... Dot arguments are passed to the predict and plot functions. Dot argument names,
whether prefixed or not, should be specified in full and not abbreviated.
“Prefixed” arguments are passed directly to the associated function. For exam-
ple the prefixed argument persp.col="pink" passes col="pink" to persp(),
overriding the global col setting. To send an argument to predict whose name
may alias with plotmo’s arguments, use predict. as a prefix. Example:
plotmo(mod, s=1)
# error: arg matches multiple formal args
plotmo(mod, predict.s=1) # ok now: s=1 will be passed to predict()
The prefixes recognized by plotmo are:
predict.
degree1.
persp.
contour.
image.
pt.
smooth.
level.
func.
rug.
density.
grid.
caption.
par.
passed to the predict method for the model
modifies degree1 plots e.g. degree1.col=3, degree1.lwd=2
arguments passed to persp
arguments passed to contour
arguments passed to image
see the pt.col argument (arguments passed to points and text)
see the smooth.col argument (arguments passed to lines and lowess)
see the level argument (level.shade, level.shade2, and arguments for polygon)
see the func argument (arguments passed to lines)
see the nrug argument (rug.jitter, and arguments passed to rug)
see the nrug argument (density.adjust, and arguments passed to lines)
see the grid.col argument (arguments passed to grid)
see the caption argument (arguments passed to mtext)
arguments passed to par (only necessary if a par argument name clashes with a plotmo argument)
The cex argument is relative, so specifying cex=1 is the same as not specifying
cex.
For backwards compatibility, some dot arguments are supported but not explic-
itly documented. For example, the old argument col.response is no longer
in plotmo’s formal argument list, but is still accepted and treated like the new
argument pt.col.
Note
In general this function won’t work on models that don’t save the call and data with the model in a
standard way. For further discussion please see “Accessing the model data” in the plotmo vignette.
Package authors may want to look at Guidelines for S3 Regression Models (also available here).
By default, plotmo tries to use sensible model-dependent defaults when calling predict. Use
trace=1 to see the arguments passed to predict. You can change the defaults by using plotmo’s
type argument, and by using dot arguments prefixed with predict. (see the 
#### Description
 of “...”
above).8
plotmo.misc
See Also
Please see the plotmo vignette (also available here).

#### Examples
```{r}
if (require(rpart)) {
data(kyphosis)
rpart.model <- rpart(Kyphosis~., data=kyphosis)
# pass type="prob" to plotmo's internal calls to predict.rpart, and select
# the column named "present" from the matrix returned by predict.rpart
plotmo(rpart.model, type="prob", nresponse="present")
}
if (require(earth)) {
data(ozone1)
earth.model <- earth(O3 ~ ., data=ozone1, degree=2)
plotmo(earth.model)
# plotmo(earth.model, pmethod="partdep") # partial dependence plots
}
