---
title: "``VIM::chorizonDL``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```



chorizonDL
C-horizon of the Kola data with missing values

#### Description 

This data set is the same as the chorizon data set in package mvoutlier, except that values below
the detection limit are coded as NA.

#### Format
A data frame with 606 observations on the following 110 variables.
*ID a numeric vector
XCOO a numeric vector
YCOO a numeric vector
Ag a numeric vector12
chorizonDL
Ag_INAA a numeric vector
Al a numeric vector
Al2O3 a numeric vector
As a numeric vector
As_INAA a numeric vector
Au_INAA a numeric vector
B a numeric vector
Ba a numeric vector
Ba_INAA a numeric vector
Be a numeric vector
Bi a numeric vector
Br_IC a numeric vector
Br_INAA a numeric vector
Ca a numeric vector
Ca_INAA a numeric vector
CaO a numeric vector
Cd a numeric vector
Ce_INAA a numeric vector
Cl_IC a numeric vector
Co a numeric vector
Co_INAA a numeric vector
EC a numeric vector
Cr a numeric vector
Cr_INAA a numeric vector
Cs_INAA a numeric vector
Cu a numeric vector
Eu_INAA a numeric vector
F_IC a numeric vector
Fe a numeric vector
Fe_INAA a numeric vector
Fe2O3 a numeric vector
Hf_INAA a numeric vector
Hg a numeric vector
Hg_INAA a numeric vector
Ir_INAA a numeric vector
K a numeric vector
K2O a numeric vectorchorizonDL
La a numeric vector
La_INAA a numeric vector
Li a numeric vector
LOI a numeric vector
Lu_INAA a numeric vector
wt_INAA a numeric vector
Mg a numeric vector
MgO a numeric vector
Mn a numeric vector
MnO a numeric vector
Mo a numeric vector
Mo_INAA a numeric vector
Na a numeric vector
Na_INAA a numeric vector
Na2O a numeric vector
Nd_INAA a numeric vector
Ni a numeric vector
Ni_INAA a numeric vector
NO3_IC a numeric vector
P a numeric vector
P2O5 a numeric vector
Pb a numeric vector
pH a numeric vector
PO4_IC a numeric vector
Rb a numeric vector
S a numeric vector
Sb a numeric vector
Sb_INAA a numeric vector
Sc a numeric vector
Sc_INAA a numeric vector
Se a numeric vector
Se_INAA a numeric vector
Si a numeric vector
SiO2 a numeric vector
Sm_INAA a numeric vector
Sn_INAA a numeric vector
SO4_IC a numeric vector
Sr a numeric vector
Sr_INAA a numeric vector
SUM_XRF a numeric vector
Ta_INAA a numeric vector
Tb_INAA a numeric vector
Te a numeric vector
Th a numeric vector
Th_INAA a numeric vector
Ti a numeric vector
TiO2 a numeric vector
U_INAA a numeric vector
V a numeric vector
W_INAA a numeric vector
Y a numeric vector
Yb_INAA a numeric vector
Zn a numeric vector
Zn_INAA a numeric vector
ELEV a numeric vector
*COUN a numeric vector
*ASP a numeric vector
TOPC a numeric vector
LITO a numeric vector
Al_XRF a numeric vector
Ca_XRF a numeric vector
Fe_XRF a numeric vector
K_XRF a numeric vector
Mg_XRF a numeric vector
Mn_XRF a numeric vector
Na_XRF a numeric vector
P_XRF a numeric vector
Si_XRF a numeric vector
Ti_XRF a numeric vector


#### Examples 
```{r}
data(chorizonDL, package = "VIM")
summary(chorizonDL)
```
#### Note
For a more detailed description of this data set, see chorizon in package mvoutlier.
Source
Kola Project (1993-1998)colormapMiss
15
References
Reimann, C., Filzmoser, P., Garrett, R.G. and Dutter, R. (2008) Statistical Data Analysis Explained:
Applied Environmental Statistics with R. Wiley.
See Also
chorizon
