---
title: "``dlookr::plot.transform ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

 Visualize Information for an "transform" Object

### Description 

Visualize two kinds of plot by attribute of 'transform' class. The Transformation of a numerical
variable is a density plot.

### Usage 
<pre><code>

## S3 method for class 'transform'
plot(x, ...)

</code></pre>
### Arguments
 
x an object of class "transform", usually, a result of a call to transform().
* ``...``: arguments to be passed to methods. such as graphical parameters (see par).

### See Also
 
transform, summary.transform.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```


```{r}
# Standardization ------------------------------
advertising_minmax <- transform(carseats$Advertising, method = "minmax")
advertising_minmax
summary(advertising_minmax)
plot(advertising_minmax)
```


```{r}
# Resolving Skewness 
advertising_log <- transform(carseats$Advertising, method = "log")
advertising_log
summary(advertising_log)
plot(advertising_log)
```
