---
title: "``plot_normality.tbl_dbi``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```


Plot distribution information of numerical data

### Description 

The plot_normality() visualize distribution information for normality test of the numerical(INTEGER,
NUMBER, etc.) column of the DBMS table through tbl_dbi.

### Usage 
<pre><code>

## S3 method for class 'tbl_dbi'
plot_normality(.data, ..., ``in_database = FALSE``,
collect_size = Inf)

</code></pre>
### Arguments
 
* ``.data``:   a tbl_dbi.
* ``...``: one or more unquoted expressions separated by commas. You can treat variable names like they are positions. Positive values select variables; negative values to drop variables. If the first expression is negative, ``plot_normality()`` will automatically
start with all variables. These arguments are automatically quoted and evaluated in a context where column names represent column positions. They
support unquoting and splicing.
* ``in_database``: Specifies whether to perform in-database operations. If TRUE, most operations are performed in the DBMS. if FALSE, table data is taken in R and operated
in-memory. Not yet supported in_database = TRUE.
* ``collect_size``: a integer. The number of data samples from the DBMS to R. Applies only if ``in_database = FALSE``.
See vignette("EDA") for an introduction to these concepts.

### Details 

The scope of the visualization is the provide a distribution information. Since the plot is drawn for
each variable, if you specify more than one variable in the ... argument, the specified number of
plots are drawn.
Distribution information
The plot derived from the numerical data vizualization is as follows.
*  histogram by original data
*  q-q plot by original data
*  histogram by log transfer data
*  histogram by square root transfer data

### See Also
 
plot_normality.data.frame, plot_outlier.tbl_dbi.

### Examples
```{r}

library(dplyr)
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# connect DBMS
con_sqlite <- DBI::dbConnect(RSQLite::SQLite(), ":memory:")
# copy carseats to the DBMS with a table named TB_CARSEATS
copy_to(con_sqlite, carseats, name = "TB_CARSEATS", overwrite = TRUE)
```
```{r}
# Using pipes ---------------------------------
# Visualization of all numerical variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_normality()
# Positive values select variables, and In-memory mode and collect size is 200
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_normality(Income, Price, collect_size = 200)
```

```{r}
# Positions values select variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_normality(1)
```
```{r}
# Using pipes & dplyr -------------------------
# Plot 'Sales' variable by 'ShelveLoc' and 'US'
con_sqlite %>%
tbl("TB_CARSEATS") %>%
group_by(ShelveLoc, US) %>%
plot_normality(Sales)
```
```{r}
# extract only those with 'ShelveLoc' variable level is "Good",
# and plot 'Income' by 'US'
con_sqlite %>%
tbl("TB_CARSEATS") %>%
filter(ShelveLoc == "Good") %>%
group_by(US) %>%
plot_normality(Income)
```