---
title: "``dlookr::plot.optimal_bins ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```


Visualize Distribution for an "optimal_bins" Object

### Description 

It generates plots for distribution, bad rate, and weight of evidence after running smbinning and
saving its output.
See vignette("transformation") for an introduction to these concepts.

### Usage 
<pre><code>

## S3 method for class 'optimal_bins'
plot(x, type = c("dist", "goodrate", "badrate",
"WoE"), sub = "", ...)

</code></pre>
### Arguments
 
x an object of class "optimal_bins", usually, a result of a call to binning_by().
type options for visualization. Distribution ("dist"), Good Rate ("goodrate"), Bad
Rate ("badrate"), and Weight of Evidence ("WoE").
plot.relate 61
sub subtitle for the chart (optional).
* ``...``: arguments to be passed to methods. such as graphical parameters (see par). only
applies to the first graph that is implemented with the boxplot() function.

### See Also
 
binning_by, plot.bins, smbinning.plot.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# optimal binning
bin <- binning_by(carseats, "US", "Advertising")
bin
# summary optimal_bins class
summary(bin)
# information value
attr(bin, "iv")
# information value table
attr(bin, "ivtable")
# visualize optimal_bins class
plot(bin, sub = "bins of Advertising variable")
```