---
title: "``dlookr::plot.imputation``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```


plot.imputation Visualize Information for an "imputation" Object

### Description 

Visualize two kinds of plot by attribute of 'imputation' class. The imputation of a numerical variable
is a density plot, and the imputation of a categorical variable is a bar plot.

### Usage 
<pre><code>

## S3 method for class 'imputation'
plot(x, ...)

</code></pre>
### Arguments
 
x an object of class "imputation", usually, a result of a call to imputate_na() or
imputate_outlier().
* ``...``: arguments to be passed to methods. such as graphical parameters (see par). only
applies when the model argument is TRUE, and is used for ... of the plot.lm ()
function.

### See Also
 
imputate_na, imputate_outlier, summary.imputation.
60 plot.optimal_bins

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```

```{r}
# Imputate missing values -----------------------------
# If the variable of interest is a numarical variable
income <- imputate_na(carseats, Income, US, method = "rpart")
income
summary(income)
plot(income)
# If the variable of interest is a categorical variable
urban <- imputate_na(carseats, Urban, US, method = "mice")
urban
summary(urban)
plot(urban)
```

```{r}
# Imputate outliers ----------------------------------
# If the variable of interest is a numarical variable
price <- imputate_outlier(carseats, Price, method = "capping")
price
summary(price)
plot(price)
```