---
title: "``dlookr::plot_outlier.tbl_dbi``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```


 Plot outlier information of numerical data diagnosis in the DBMS

### Description 

The plot_outlier() visualize outlier information for diagnosing the quality of the numerical(INTEGER,
NUMBER, etc.) column of the DBMS table through tbl_dbi.

### Usage 
<pre><code>

## S3 method for class 'tbl_dbi'
plot_outlier(.data, ..., col = "lightblue",
``in_database = FALSE``, collect_size = Inf)

</code></pre>
### Arguments
 
* `.data``:   a tbl_dbi.
... one or more unquoted expressions separated by commas. You can treat variable names like they are positions. Positive values select variables; negative values to drop variables. If the first expression is negative, ``plot_outlier()`` will automatically start with all variables. These arguments are automatically quoted and
evaluated in a context where column names represent column positions. They support unquoting and splicing.
col a color to be used to fill the bars. The default is "lightblue".
* ``in_database``: Specifies whether to perform in-database operations. If TRUE, most operations
are performed in the DBMS. if FALSE, table data is taken in R and operated in-memory. Not yet supported ``in_database = TRUE``.
* ``collect_size``: a integer. The number of data samples from the DBMS to R. Applies only if
``in_database = FALSE``.

### Details 

The scope of the diagnosis is the provide a outlier information. Since the plot is drawn for each
variable, if you specify more than one variable in the ... argument, the specified number of plots are
drawn.

Outlier diagnostic information
The plot derived from the numerical data diagnosis is as follows.

*  With outliers box plot
*  Without outliers box plot
*  With outliers histogram
*  Without outliers histogram
See vignette("diagonosis") for an introduction to these concepts.

### See Also
 
plot_outlier.data.frame, diagnose_outlier.tbl_dbi.

### Examples
```{r}

library(dplyr)
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```
```{r}
# connect DBMS
con_sqlite <- DBI::dbConnect(RSQLite::SQLite(), ":memory:")
# copy carseats to the DBMS with a table named TB_CARSEATS
copy_to(con_sqlite, carseats, name = "TB_CARSEATS", overwrite = TRUE)
```
```{r}
# Using pipes ---------------------------------
# Visualization of all numerical variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_outlier()
```
```{r}
# Positive values select variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_outlier(Sales, Price)
```
```{r}
# Negative values to drop variables, and In-memory mode and collect size is 200
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_outlier(-Sales, -Price, collect_size = 200)
```
```{r}
# Positions values select variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_outlier(6)
```
```{r}
# Positions values select variables

carseats %>%
plot_outlier(-1, -5)
```
```{r}
# Using pipes & dplyr -------------------------
# Visualization of numerical variables with a ratio of
# outliers greater than 1%
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_outlier(con_sqlite %>%
tbl("TB_CARSEATS") %>%
diagnose_outlier() %>%
filter(outliers_ratio > 1) %>%
select(variables) %>%
pull())
```
