---
title: "Untitled"
author: "Kevin O Brien"
date: "12 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```



plot.bins Visualize Distribution for an "bins" object

### Description 

Visualize both plots on a single screen. The plot at the top is a histogram representing the frequency
of the level. The plot at the bottom is a bar chart representing the frequency of the level.

### Usage 
<pre><code>

## S3 method for class 'bins'
plot(x, ...)

</code></pre>
### Arguments
 
x an object of class "bins", usually, a result of a call to binning().
* ``...``: arguments to be passed to methods. such as graphical parameters (see par).
plot.imputation 59

### See Also
 
binning, print.bins, summary.bins.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
```


```{r}
# Binning the carat variable. default type argument is "quantile"
bin <- binning(carseats$Income, nbins = 5)
plot(bin)
```


```{r}
# Using another type argument
bin <- binning(carseats$Income, nbins = 5, type = "equal")
plot(bin)
bin <- binning(carseats$Income, nbins = 5, type = "pretty")
plot(bin)
bin <- binning(carseats$Income, nbins = 5, type = "kmeans")
plot(bin)
bin <- binning(carseats$Income, nbins = 5, type = "bclust")
plot(bin)
```