---
title: "``dlookr::plot_correlate.tbl_dbi``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

Visualize correlation plot of numerical data

### Description 

The ``plot_correlate()`` visualize correlation plot for find relationship between two numerical(INTEGER,NUMBER, etc.) column of the DBMS table through tbl_dbi.

### Usage 

<pre><code>
## S3 method for class 'tbl_dbi'
plot_correlate(.data, ..., ``in_database = FALSE``,
collect_size = Inf)
</code></pre>

### Arguments
 
* ``.data``:   a tbl_dbi.
* ``...``: one or more unquoted expressions separated by commas. You can treat variable names like they are positions. Positive values select variables; negative values to drop variables. If the first expression is negative, ``plot_correlate()`` will automatically
start with all variables. These arguments are automatically quoted and evaluated in a context where column names represent column positions. They support unquoting and splicing.
*  ``in_database``: Specifies whether to perform in-database operations. If TRUE, most operations are performed in the DBMS. if FALSE, table data is taken in R and operated in-memory. Not yet supported ``in_database = TRUE``.
* ``collect_size``: a integer. The number of data samples from the DBMS to R. Applies only if ``in_database = FALSE``.

See vignette("EDA") for an introduction to these concepts.

### Details 

The scope of the visualization is the provide a correlation information. Since the plot is drawn for
each variable, if you specify more than one variable in the ... argument, the specified number of
plots are drawn.

### See Also
 
plot_correlate.data.frame, plot_outlier.tbl_dbi.

### Examples
```{r}

library(dplyr)
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# connect DBMS
con_sqlite <- DBI::dbConnect(RSQLite::SQLite(), ":memory:")
# copy carseats to the DBMS with a table named TB_CARSEATS
copy_to(con_sqlite, carseats, name = "TB_CARSEATS", overwrite = TRUE)
```


```{r}
# Using pipes ---------------------------------
# Visualize correlation plot of all numerical variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_correlate()
# Positive values select variables, and In-memory mode and collect size is 200
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_correlate(Sales, Price, collect_size = 200)
```


```{r}
# Negative values to drop variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_correlate(-Sales, -Price)
# Positions values select variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_correlate(1)
# Positions values select variables
con_sqlite %>%
tbl("TB_CARSEATS") %>%
plot_correlate(-1, -2, -3, -5, -6)
```


```{r}
# Using pipes & dplyr -------------------------
# Visualize correlation plot of 'Sales' variable by 'ShelveLoc'
# and 'US' variables.
con_sqlite %>%
tbl("TB_CARSEATS") %>%
group_by(ShelveLoc, US) %>%
plot_correlate(Sales)
```


```{r}
# Extract only those with 'ShelveLoc' variable level is "Good",
# and visualize correlation plot of 'Sales' variable by 'Urban'
# and 'US' variables.
con_sqlite %>%
tbl("TB_CARSEATS") %>%
filter(ShelveLoc == "Good") %>%
group_by(Urban, US) %>%
plot_correlate(Sales)
```


