---
title: "``dlookr::plot_correlate``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

plot_correlate Visualize correlation plot of numerical data

### Description 

The plot_correlate() visualize correlation plot for find relationship between two numerical variables.

### Usage 
<pre><code>

plot_correlate(.data, ...)
## S3 method for class 'data.frame'
plot_correlate(.data, ...)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
... one or more unquoted expressions separated by commas. You can treat variable
names like they are positions. Positive values select variables; negative values
to drop variables. If the first expression is negative, plot_correlate() will automatically
start with all variables. These arguments are automatically quoted and
evaluated in a context where column names represent column positions. They
support unquoting and splicing.
See vignette("EDA") for an introduction to these concepts.

### Details 

The scope of the visualization is the provide a correlation information. Since the plot is drawn for
each variable, if you specify more than one variable in the ... argument, the specified number of
plots are drawn.

### See Also
 
plot_correlate.tbl_dbi, plot_outlier.data.frame.

### Examples
```{r}

# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
# Visualize correlation plot of all numerical variables
plot_correlate(carseats)
```

```{r}
# Select the variable to compute
plot_correlate(carseats, Sales, Price)
plot_correlate(carseats, -Sales, -Price)
plot_correlate.tbl_dbi 65
plot_correlate(carseats, "Sales", "Price")
plot_correlate(carseats, 1)
```

```{r}
# Using dplyr::grouped_dt
library(dplyr)
gdata <- group_by(carseats, ShelveLoc, US)
plot_correlate(gdata, "Sales")
plot_correlate(gdata)
```

```{r}
# Using pipes ---------------------------------
# Visualize correlation plot of all numerical variables
carseats %>%
plot_correlate()
# Positive values select variables
carseats %>%
plot_correlate(Sales, Price)
# Negative values to drop variables
carseats %>%
plot_correlate(-Sales, -Price)
# Positions values select variables
carseats %>%
plot_correlate(1)
# Positions values select variables
carseats %>%
plot_correlate(-1, -2, -3, -5, -6)
```

```{r}
# Using pipes & dplyr -------------------------
# Visualize correlation plot of 'Sales' variable by 'ShelveLoc'
# and 'US' variables.
carseats %>%
group_by(ShelveLoc, US) %>%
plot_correlate(Sales)
```

```{r}
# Extract only those with 'ShelveLoc' variable level is "Good",
# and visualize correlation plot of 'Sales' variable by 'Urban'
# and 'US' variables.
carseats %>%
filter(ShelveLoc == "Good") %>%
group_by(Urban, US) %>%
plot_correlate(Sales)
```