---
title: "``VIM::aggr``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

aggr
Aggregations for missing/imputed values

#### Description 

Calculate or plot the amount of missing/imputed values in each variable and the amount of miss-
ing/imputed values in certain combinations of variables.
Print method for objects of class "aggr".
Summary method for objects of class "aggr".

#### Usage 
<pre><code>

aggr(x, delimiter = NULL, plot = TRUE, ...)
## S3 method for class 'aggr'
plot(x, col = c("skyblue", "red", "orange"), bars = TRUE,
numbers = FALSE, prop = TRUE, combined = FALSE, varheight = FALSE,
only.miss = FALSE, border = par("fg"), sortVars = FALSE,
sortCombs = TRUE, ylabs = NULL, axes = TRUE, labels = axes,
cex.lab = 1.2, cex.axis = par("cex"), cex.numbers = par("cex"),
gap = 4, ...)
## S3 method for class 'aggr'
print(x, digits = NULL, ...)
## S3 method for class 'aggr'
summary(object, ...)
</code></pre>

#### Arguments
x
delimiter
plot
...
col
a vector, matrix or data.frame.
a character-vector to distinguish between variables and imputation-indices for imputed variables (therefore, x needs to have colnames). If given, it is used
to determine the corresponding imputation-index for any imputed variable (a logical-vector indicating which values of the variable have been imputed). If
such imputation-indices are found, they are used for highlighting and the colors are adjusted according to the given colors for imputed variables (see col).
a logical indicating whether the results should be plotted (the default is TRUE).
for aggr and TKRaggr, further arguments and graphical parameters to be passed to plot.aggr. For plot.aggr, further graphical parameters to be passed down.
par("oma") will be set appropriately unless supplied (see par).
a vector of length three giving the colors to be used for observed, missing and imputed data. If only one color is supplied, it is used for missing and imputed
data and observed data is transparent. If only two colors are supplied, the first one is used for observed data and the second color is used for missing and im-
puted data.aggr
5
bars a logical indicating whether a small barplot for the frequencies of the different
combinations should be drawn.
numbers a logical indicating whether the proportion or frequencies of the different com-
binations should be represented by numbers.
prop a logical indicating whether the proportion of missing/imputed values and com-
binations should be used rather than the total amount.
combined a logical indicating whether the two plots should be combined. If FALSE, a
separate barplot on the left hand side shows the amount of missing/imputed
values in each variable. If TRUE, a small version of this barplot is drawn on
top of the plot for the combinations of missing/imputed and non-missing values.
See “
#### Details 
” for more information.
varheight a logical indicating whether the cell heights are given by the frequencies of
occurrence of the corresponding combinations.
only.miss a logical indicating whether the small barplot for the frequencies of the combina-
tions should only be drawn for combinations including missing/imputed values
(if bars is TRUE). This is useful if most observations are complete, in which case
the corresponding bar would dominate the barplot such that the remaining bars
are too compressed. The proportion or frequency of complete observations (as
determined by prop) is then represented by a number instead of a bar.
border the color to be used for the border of the bars and rectangles. Use border=NA to
omit borders.
sortVars a logical indicating whether the variables should be sorted by the number of
missing/imputed values.
sortCombs a logical indicating whether the combinations should be sorted by the frequency
of occurrence.
ylabs if combined is TRUE, a character string giving the y-axis label of the combined
plot, otherwise a character vector of length two giving the y-axis labels for the
two plots.
axes a logical indicating whether axes should be drawn.
labels either a logical indicating whether labels should be plotted on the x-axis, or a
character vector giving the labels.
cex.lab the character expansion factor to be used for the axis labels.
cex.axis the character expansion factor to be used for the axis annotation.
cex.numbers the character expansion factor to be used for the proportion or frequencies of the
different combinations
gap if combined is FALSE, a numeric value giving the distance between the two plots
in margin lines.
digits the minimum number of significant digits to be used (see print.default).
object an object of class "aggr".6
aggr

#### Details 

Often it is of interest how many missing/imputed values are contained in each variable. Even more
interesting, there may be certain combinations of variables with a high number of missing/imputed
values.
If combined is FALSE, two separate plots are drawn for the missing/imputed values in each variable
and the combinations of missing/imputed and non-missing values. The barplot on the left hand
side shows the amount of missing/imputed values in each variable. In the aggregation plot on the
right hand side, all existing combinations of missing/imputed and non-missing values in the ob-
servations are visualized. Available, missing and imputed data are color coded as given by col.
Additionally, there are two possibilities to represent the frequencies of occurrence of the different
combinations. The first option is to visualize the proportions or frequencies by a small bar plot
and/or numbers. The second option is to let the cell heights be given by the frequencies of the cor-
responding combinations. Furthermore, variables may be sorted by the number of missing/imputed
values and combinations by the frequency of occurrence to give more power to finding the structure
of missing/imputed values.
If combined is TRUE, a small version of the barplot showing the amount of missing/imputed values
in each variable is drawn on top of the aggregation plot.
The graphical parameter oma will be set unless supplied as an argument.
Value
for aggr, a list of class "aggr" containing the following components: - x the data used. - combina-
tions a character vector representing the combinations of variables. - count the frequencies of these
combinations. - percent the percentage of these combinations. - missings a data.frame contain-
ing the amount of missing/imputed values in each variable. - tabcomb the indicator matrix for the
combinations of variables.
a list of class "summary.aggr" containing the following components: - missings a data.frame
containing the amount of missing or imputed values in each variable. - combinations a data.frame
containing a character vector representing the combinations of variables along with their frequencies
and percentages.
Note
Some of the argument names and positions have changed with version 1.3 due to extended func-
tionality and for more consistency with other plot functions in VIM. For back compatibility, the
arguments labs and names.arg can still be supplied to ...{} and are handled correctly. Neverthe-
less, they are deprecated and no longer documented. Use ylabs and labels instead.
Author(s)
Andreas Alfons, Matthias Templ, modifications for displaying imputed values by Bernd Prantner
Matthias Templ, modifications by Andreas Alfons and Bernd Prantner
Matthias Templ, modifications by Andreas Alfonsalphablend
7
References
M. Templ, A. Alfons, P. Filzmoser (2012) Exploring incomplete data using visualization tools.
Journal of Advances in Data Analysis and Classification, Online first. DOI: 10.1007/s11634-011-
0102-y.
See Also
print.aggr, summary.aggr
aggr
print.summary.aggr, aggr

#### Examples 
```{r}
data(sleep, package="VIM")
## for missing values
a <- aggr(sleep)
a
summary(a)
## for imputed values
sleep_IMPUTED <- kNN(sleep)
a <- aggr(sleep_IMPUTED, delimiter="_imp")
a
summary(a)
data(sleep, package = "VIM")
a <- aggr(sleep, plot=FALSE)
a
data(sleep, package = "VIM")
summary(aggr(sleep, plot=FALSE))
