---
title: "``VIM::growdotMiss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

Growing dot map with information about missing/imputed values

#### Description 

Map with dots whose sizes correspond to the values in a certain variable. Observations with missing/imputed values in additional variables are highlighted.

#### Usage 
<pre><code>

growdotMiss(x, coords, map, pos = 1, delimiter = NULL,
  selection = c("any", "all"), log = FALSE, col = c("skyblue", "red",
  "skyblue4", "red4", "orange", "orange4"), border = par("bg"),
  alpha = NULL, scale = NULL, size = NULL, exp = c(0, 0.95, 0.05),
  col.map = grey(0.5), legend = TRUE, legtitle = "Legend",
  cex.legtitle = par("cex"), cex.legtext = par("cex"), ncircles = 6,
  ndigits = 1, interactive = TRUE, ...)

#### Arguments
* ``x``: a vector, matrix or data.frame.
* ``coords``: a matrix or data.frame with two columns giving the spatial coordinates of the observations.
* ``map``: a background map to be passed to bgmap.
* ``pos``: a numeric value giving the index of the variable determining the dot sizes.
* ``delimiter``: a character-vector to distinguish between variables and imputation-indices for imputed variables (therefore, x needs to have colnames). If given, it is used
to determine the corresponding imputation-index for any imputed variable (a logical-vector indicating which values of the variable have been imputed). If
such imputation-indices are found, they are used for highlighting and the colors are adjusted according to the given colors for imputed variables (see col).
* ``selection``: the selection method for highlighting missing/imputed values in multiple additional variables. Possible values are "any" (highlighting of missing/imputed values in any of the additional variables) and "all" (highlighting of missing/imputed values in all of the additional variables).
* ``log``: a logical indicating whether the variable given by pos should be log-transformed.
* ``col``: a vector of length six giving the colors to be used in the plot. If only one color is supplied, it is used for the borders of non-highlighted dots and the surface area
of highlighted dots. Else if two colors are supplied, they are recycled.
* ``border``: a vector of length four giving the colors to be used for the borders of the growing
dots. Use NA to omit borders.
* ``alpha``: a numeric value between 0 and 1 giving the level of transparency of the colors,
or NULL. This can be used to prevent overplotting.
* scale scaling factor of the map.
* size a vector of length two giving the sizes for the smallest and largest dots.
* ``exp``: a vector of length three giving the factors that define the shape of the exponential function (see ‘Details ’).
* ``col.map``: the color to be used for the background map.
* ``legend``: a logical indicating whether a legend should be plotted.
* ``legtitle``: the title for the legend.
* ``cex.legtitle``: the character expansion factor to be used for the title of the legend.
* ``cex.legtext``: the character expansion factor to be used in the legend.
* ``ncircles``: the number of circles displayed in the legend.
* ``ndigits``: the number of digits displayed in the legend. Note that \ this is just a suggestion
(see format).
* ``interactive``: a logical indicating whether information about certain observations can be displayed interactively (see ‘Details ’).
* ``...``: for growdotMiss, further arguments and graphical parameters to be passed to bgmap. For bubbleMiss, the arguments to be passed to growdotMiss.


#### Examples 
```{r}
data(chorizonDL, package = "VIM")
data(kola.background, package = "VIM")
coo <- chorizonDL[, c("XCOO", "YCOO")]
## for missing values
x <- chorizonDL[, c("Ca","As", "Bi")]
growdotMiss(x, coo, kola.background, border = "white")
## for imputed values
x_imp <- kNN(chorizonDL[,c("Ca","As","Bi" )])
growdotMiss(x_imp, coo, kola.background, delimiter = "_imp", border = "white")
```

#### Details 

The smallest dots correspond to the 10% quantile and the largest dots to the 99% quantile. In between, the dots grow exponentially, with exp defining the shape of the exponential function.

Missings/imputed missings in the variable of interest will be drawn as rectangles. If interactive=TRUE, detailed information for an observation can be printed on the console by clicking on the corresponding point. Clicking in a region that does not contain any points quits the interactive session.

#### Note
The function was renamed to growdotMiss in version 1.3. bubbleMiss is a (deprecated) wrapper for growdotMiss for back compatibility with older versions. However, due to extended functionality, some of the argument positions have changed.
The code is based on bubbleFIN from package StatDA.

#### Author(s)
Andreas Alfons, Matthias Templ, Peter Filzmoser, Bernd Prantner

#### References
* M. Templ, A. Alfons, P. Filzmoser (2012) Exploring incomplete data using visualization tools.
* Journal of Advances in Data Analysis and Classification, Online first. DOI: 10.1007/s11634-011-0102-y.

