---
title: "``VIM::imri``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

---
title: "``VIM::imri``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

Iterative robust model-based imputation (IRMI)

#### Description 

In each step of the iteration, one variable is used as a response variable and the remaining variables
serve as the regressors.

#### Usage 
<pre><code>

irmi(x, eps = 5, maxit = 100, mixed = NULL, mixed.constant = NULL,
count = NULL, step = FALSE, robust = FALSE, takeAll = TRUE,
noise = TRUE, noise.factor = 1, force = FALSE, robMethod = "MM",
force.mixed = TRUE, mi = 1, addMixedFactors = FALSE, trace = FALSE,
init.method = "kNN", modelFormulas = NULL, multinom.method = "multinom",
imp_var = TRUE, imp_suffix = "imp")
</code></pre>

#### Arguments
* ``x``: data.frame or matrix
* ``eps``: threshold for convergency
* ``maxit``: maximum number of iterations
mixed column index of the semi-continuous variables
* ``mixed.constant`` vector with length equal to the number of semi-continuous variables specifying
the point of the semi-continuous distribution with non-zero probability
count column index of count variables
* ``step``: a stepwise model selection is applied when the parameter is set to TRUE
robust if TRUE, robust regression methods will be applied
takeAll takes information of (initialised) missings in the response as well for regression imputation.
* ``noise``: irmi has the option to add a random error term to the imputed values, this creates the possibility for multiple imputation. The error term has mean 0 and variance
corresponding to the variance of the regression residuals.
* ``noise.factor``: amount of noise.
* ``force``: if TRUE, the algorithm tries to find a solution in any case, possible by using different robust methods automatically.
* ``robMethod``: regression method when the response is continuous.
force.mixed if TRUE, the algorithm tries to find a solution in any case, possible by using different robust methods automatically.
* ``mi``: number of multiple imputations.
* ``addMixedFactors``:
if TRUE add additional factor variable for each mixed variable as X variable in the regression
* ``trace``: Additional information about the iterations when trace equals TRUE.
* ``init.method``: Method for initialization of missing values (kNN or median)
* ``modelFormulas``: a named list with the name of variables for the rhs of the formulas, which must contain a rhs formula for each variable with missing values, it should look like list(y1=c("x1","x2"),y2=c("x1","x3"))
if factor variables for the mixed variables should be created for the regression models multinom.method
Method for estimating the multinomial models (current default and only available method is multinom)
* ``imp_var``: TRUE/FALSE if a TRUE/FALSE variables for each imputed variable should be created show the imputation status
* ``imp_suffix``: suffix for the TRUE/FALSE variables showing the imputation status 


#### Examples 
```{r}
data(sleep)
irmi(sleep)
data(testdata)
imp_testdata1 <- irmi(testdata$wna,mixed=testdata$mixed)
# mixed.constant != 0 (-10)
testdata$wna$m1[testdata$wna$m1==0] <- -10
testdata$wna$m2 <- log(testdata$wna$m2+0.001)
imp_testdata2 <- irmi(testdata$wna,mixed=testdata$mixed,mixed.constant=c(-10,log(0.001)))
imp_testdata2$m2 <- exp(imp_testdata2$m2)-0.001
#example with fixed formulas for the variables with missing
form=list(
NonD=c("BodyWgt","BrainWgt"),
Dream=c("BodyWgt","BrainWgt"),
Sleep=c("BrainWgt"),
Span=c("BodyWgt"),
Gest=c("BodyWgt","BrainWgt")
)
irmi(sleep,modelFormulas=form,trace=TRUE)
# Example with ordered variable
td <- testdata$wna
td$c1 <- as.ordered(td$c1)
irmi(td)
```
#### Details 

The method works sequentially and iterative. The method can deal with a mixture of continuous,
semi-continuous, ordinal and nominal variables including outliers.
A full description of the method can be found in the mentioned reference.

#### Value
the imputed data set.

#### Author(s)
Matthias Templ, Alexander Kowarik

#### References
M. Templ, A. Kowarik, P. Filzmoser (2011) Iterative stepwise regression imputation using standard
and robust methods. Journal of Computational Statistics and Data Analysis, Vol. 55, pp. 2793-
2806.
A. Kowarik, M. Templ (2016) Imputation with R package VIM. Journal of Statistical Software,
74(7), 1-16.
See Also
mi
