---
title: "``VIM::kNN``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

## k-Nearest Neighbour Imputation

#### Description 

k-Nearest Neighbour Imputation based on a variation of the Gower Distance for numerical, cate-
gorical, ordered and semi-continous variables.

#### Usage 
<pre><code>

kNN(data, variable = colnames(data), metric = NULL, k = 5,
dist_var = colnames(data), weights = NULL, numFun = median,
catFun = maxCat, makeNA = NULL, NAcond = NULL, impNA = TRUE,
donorcond = NULL, mixed = vector(), mixed.constant = NULL,
trace = FALSE, imp_var = TRUE, imp_suffix = "imp", addRF = FALSE,
onlyRF = FALSE, addRandom = FALSE, useImputedDist = TRUE,
weightDist = FALSE)
</code></pre>

#### Arguments
* data data.frame or matrix
* ``variable``: variables where missing values should be imputed
* metric metric to be used for calculating the distances between
* ``k`` number of Nearest Neighbours used
* ``dist_var``: names or variables to be used for distance calculation
* ``weights``: weights for the variables for distance calculation. If weights = "auto" weights will be selected based on variable importance from random forest regression, using function ranger. Weights are calculated for each variable seperately.
numFun function for aggregating the k Nearest Neighbours in the case of a numerical variable
* ``catFun``: function for aggregating the k Nearest Neighbours in the case of a categorical variable
makeNA list of length equal to the number of variables, with values, that should be converted to NA for each variable
* ``NAcond``: list of length equal to the number of variables, with a condition for imputing a NA
impNA TRUE/FALSE whether NA should be imputed
* ``donorcond``: condition for the donors e.g. list(">5"), must be NULL or a list of same length as variable
mixed names of mixed variables
* ``mixed.constant``: vector with length equal to the number of semi-continuous variables specifying
the point of the semi-continuous distribution with non-zero probability
trace TRUE/FALSE if additional information about the imputation process should be printed
* ``imp_var`` TRUE/FALSE if a TRUE/FALSE variables for each imputed variable should be created show the imputation status
imp_suffix suffix for the TRUE/FALSE variables showing the imputation status 
addRF TRUE/FALSE each variable will be modelled using random forest regression (ranger) and used as additional distance variable.
onlyRF TRUE/FALSE if TRUE only additional distance variables created from random forest regression will be used as distance variables.
* ``addRandom``: TRUE/FALSE if an additional random variable should be added for distance calculation
useImputedDist TRUE/FALSE if an imputed value should be used for distance calculation for imputing another variable. Be aware that this results in a dependency on the ordering of the variables.
* ``weightDist``: TRUE/FALSE if the distances of the k nearest neighbours should be used as
weights in the aggregation step


#### Examples 
```{r}
data(sleep)
kNN(sleep)
library(laeken)
kNN(sleep, numFun = weightedMean, weightDist=TRUE)
```

#### Details 

The function sampleCat samples with probabilites corresponding to the occurrence of the level
in the NNs. The function maxCat chooses the level with the most occurrences and random if
the maximum is not unique. The function gowerD is used by kNN to compute the distances for
numerical, factor ordered and semi-continous variables.
Value
the imputed data set.32
kola.background
Author(s)
Alexander Kowarik, Statistik Austria
References
A. Kowarik, M. Templ (2016) Imputation with R package VIM. Journal of Statistical Software,
74(7), 1-16.
