---
title: "``VIM::pairsVIM`` - Scatterplot Matrices"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

#### Description 

Create a scatterplot matrix.

#### Usage 
<pre><code>

pairsVIM(x, ..., delimiter = NULL, main = NULL, sub = NULL, panel = points, lower = panel, upper = panel, diagonal = NULL,
   labels = TRUE, pos.labels = NULL, cex.labels = NULL, font.labels = par("font"), layout = c("matrix", "graph"), gap = 1)
   
</code></pre>

#### Arguments

*	``	x	``:	a matrix or data.frame.
*	``	...	``:	further arguments and graphical parameters to be passed down. par("oma") 	will be set appropriately unless supplied (see par).
*	``	delimiter	``:	a character-vector to distinguish between variables and imputation-indices for imputed variables (therefore, x needs to have colnames). If given, it is used to determine the corresponding imputation-index for any imputed variable (a logical-vector indicating which values of the variable have been imputed). If such imputation-indices are found, they are used for highlighting and the colors	are adjusted according to the given colors for imputed variables (see col).
*	``	main, sub	``:	main and sub title.
*	``	panel	``:	a function(x, y, ...{}), which is used to plot the contents of each off-diagonal panel of the display.
*	``	lower, upper	``:	separate panel functions to be used below and above the diagonal, respectively.
*	``	diagonal	``:	optional function(x, ...{}) to be applied on the diagonal panels.
*	``	labels	``:	either a logical indicating whether labels should be plotted in the diagonal panels, or a character vector giving the labels.
*	``	pos.labels	``:	the vertical position of the labels in the diagonal panels.
*	``	cex.labels	``:	the character expansion factor to be used for the labels.
*	``	font.labels	``:	the font to be used for the labels.
*	``	layout	``:	a character string giving the layout of the scatterplot matrix. Possible values are "matrix" (a matrix-like layout with the first row on top) and "graph" (a graph-like layout with the first row at the bottom).
*	``	gap	``:	a numeric value giving the distance between the panels in margin lines.




#### Examples 
```{r}
data(sleep, package = "VIM")
x <- sleep[, -(8:10)]
x[,c(1,2,4,6,7)] <- log10(x[,c(1,2,4,6,7)])
pairsVIM(x)
```

#### Details 

* This function is the workhorse for marginmatrix and scattmatrixMiss.
* The graphical parameter oma will be set unless supplied as an argument.
* A panel function should not attempt to start a new plot, since the coordinate system for each panel is set up by pairsVIM.

#### Note
The code is based on pairs. Starting with version 1.4, infinite values are no longer removed before passing the x and y vectors to the panel functions.

#### Author(s)
Andreas Alfons, modifications by Bernd Prantner

#### References
M. Templ, A. Alfons, P. Filzmoser (2012) Exploring incomplete data using visualization tools.
Journal of Advances in Data Analysis and Classification, Online first. DOI: 10.1007/s11634-011-
0102-y.

#### See Also
marginmatrix, scattmatrixMiss
