---
title: "``VIM::regressionImp``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

## Regression Imputation

#### Description 

Impute missing values based on a regression model.

#### Usage 
<pre><code>

regressionImp(formula, data, family = "AUTO", robust = FALSE,
imp_var = TRUE, imp_suffix = "imp", mod_cat = FALSE)
</code></pre>

#### Arguments
* formula model formula to impute one variable
*  data A data.frame or survey object containing the data
* family family argument for "glm" ("AUTO" tries to choose automatically, only really tested option!!!)
robust TRUE/FALSE if robust regression should be used
* imp_var TRUE/FALSE if a TRUE/FALSE variables for each imputed variable should be
created show the imputation status
* imp_suffix suffix used for TF imputation variables
* mod_cat TRUE/FALSE if TRUE for categorical variables the level with the highest prediction probability is selected, otherwise it is sampled according to the probabilities.



#### Examples 
```{r}
data(sleep)
sleepImp1 <- regressionImp(Dream+NonD~BodyWgt+BrainWgt,data=sleep)
sleepImp2 <- regressionImp(Sleep+Gest+Span+Dream+NonD~BodyWgt+BrainWgt,data=sleep)
data(testdata)
imp_testdata1 <- regressionImp(b1+b2~x1+x2,data=testdata$wna)
imp_testdata3 <- regressionImp(x1~x2,data=testdata$wna,robust=TRUE)
```

#### Details 

"lm" is used for family "normal" and glm for all other families. (Robust=TRUE: lmrob, glmrob)

#### Value
the imputed data set.

#### Author(s)
Alexander Kowarik
References
A. Kowarik, M. Templ (2016) Imputation with R package VIM. Journal of Statistical Software,
74(7), 1-16.
