myGrob
graphreduce Make each space in a node apprear only once

#### Description 

Reduce a graph to have unique node names

#### Usage
<pre><code>

graphreduce(graph, separator)
grid.loon 13

</code></pre>
#### Arguments 

graph graph of class loongraph
separator one character that separates the spaces in node names

#### Details 

Note this is a string based operation. Node names must not contain the separator character!
Value
graph object of class loongraph

#### Examples 
```{r}
G <- completegraph(nodes=LETTERS[1:4])
LG <- linegraph(G)
LLG <- linegraph(LG)
graphreduce(LLG)
if (requireNamespace("Rgraphviz", quietly = TRUE)) {
plot(graphreduce(LLG))
}
grid.loon Create and optionally draw a grid grob from a loon widget handle

#### Description 

Create and optionally draw a grid grob from a loon widget handle

#### Usage
<pre><code>

grid.loon(target, name = NULL, gp = gpar(), draw = TRUE, vp = NULL)

</code></pre>
#### Arguments 

target either an object of class loon or a vector that specifies the widget, layer, glyph,
navigator or context completely. The widget is specified by the widget path
name (e.g. '.l0.plot'), the remaining objects by their ids.
name a character identifier for the grob, or NULL. Used to find the grob on the display
list and/or as a child of another grob.
gp a gpar object, or NULL, typically the output from a call to the function gpar.
This is basically a list of graphical parameter settings.
draw a logical value indicating whether graphics output should be produced.
vp a grid viewport object (or NULL).
14 hex12tohex6
Value
a grid grob of the loon plot
See Also
loonGrob, plot.loon

#### Examples 
```{r}
library(grid)
widget <- with(iris, l_plot(Sepal.Length, Sepal.Width))
grid.loon(widget)
