


names.loon Get State Names of Loon Object

#### Description 

States of loon objects can be accessed `[` and l_cget and modified with l_configure.

#### Usage
<pre><code>

## S3 method for class 'loon'
names(x)

</code></pre>
#### Arguments 

* ``x``:   loon object
Value
state names


ndtransitiongraph Create a n-d transition graph

#### Description 

A n-d transition graph has k-d nodes and all edges that connect two nodes that from a n-d subspace

#### Usage
<pre><code>

ndtransitiongraph(nodes, n, separator = ":")

</code></pre>
#### Arguments 

* ``nodes``: node names of graph
* ``n``: integer, dimension an edge should represent
* ``separator``: character that separates spaces in node names

#### Details 

For more information run: l_help("learn_R_display_graph.html.html#graph-utilities")

#### Value
graph object of class loongraph

#### Examples 
```{r}
g <- ndtransitiongraph(nodes=c('A:B', 'A:F', 'B:C', 'B:F'), n=3, separator=':')
```
olive Fatty Acid Composition of Italian Olive Oils

#### Description 

This data set records the percentage composition of 8 fatty acids (palmitic, palmitoleic, stearic,
oleic, linoleic, linolenic, arachidic, eicosenoic) found in the lipid fraction of 572 Italian olive oils.
The oils are samples taken from three Italian regions varying number of areas within each region.
The regions and their areas are recorded as shown in the following table:
Region Area
North North-Apulia, South-Apulia, Calabria, Sicily
South East-Liguria, West-Liguria, Umbria
Sardinia Coastal-Sardinia, Inland-Sardinia
oliveAcids 207

#### Usage
<pre><code>
olive
</code></pre>

#### Format 

A data frame containing 572 cases and 10 variates.
References
Forina, M., Armanino, C., Lanteri, S., and Tiscornia, E. (1983) "Classification of Olive Oils from
their Fatty Acid Composition", in Food Research and Data Analysis (Martens, H., Russwurm, H.,
eds.), p. 189, Applied Science Publ., Barking.
oliveAcids Fatty Acid Composition of Italian Olive Oils

#### Description 

This is the olive data set minus the Region and Area variables.

#### Usage
<pre><code>

oliveAcids

#### Format 

A data frame containing 572 cases and 8 variates.
See Also
olive


plot.loon Plot the current view of any loon plot in the current device.

#### Description 

This is a wrapper for ``grid.loon()`` to simplify the plotting of loon plots on any device. Frequent
users are recommended to use ``grid.loon()`` for more control.

#### Usage
<pre><code>

## S3 method for class 'loon'
plot(x, y = NULL, ...)

</code></pre>
#### Arguments 

* x the loon plot to be plotted on the current device
* y NULL, will be ignored.
* ... parameters passed to loonGrob

#### Value
invisible()
See Also
loonGrob, grid.loon

#### Examples 
```{r}
loonPlot <- with(iris, l_plot(Sepal.Length, Sepal.Width))
loonPlot['color'] <- iris$Species
loonPlot['selected'] <- iris$Species == "versicolor"
l_scaleto_selected(loonPlot)
loonPlot['showGuides'] <- TRUE
plot(loonPlot)
```

print.measures1d Print function names from measure1d object

#### Description 

Prints the function names of a measure1d object using print.default.

#### Usage
<pre><code>

## S3 method for class 'measures1d'
print(x, ...)

</code></pre>
#### Arguments 


...  passed on to print.default

print.measures2d Print function names from measure2d object

#### Description 

Prints the function names of a measure2d object using print.default.

#### Usage
<pre><code>

## S3 method for class 'measures2d'
print(x, ...)

</code></pre>
#### Arguments 

x measures2d object
... Arguments 
 passed on to print.default
scagnostics2d Closure of Two Dimensional Scagnostic Measures

#### Description 

Function creates a 2d measures object that can be used with l_ng_plots and l_ng_ranges.

#### Usage
<pre><code>

scagnostics2d(data, scagnostics = c("Clumpy", "Monotonic", "Convex",
"Stringy", "Skinny", "Outlying", "Sparse", "Striated", "Skewed"),
separator = ":")

</code></pre>
#### Arguments 

* ``data``:   a data.frame with the data used to calculate the measures
* scagnostics vector with valid scanostics meausure names, i.e "Clumpy", "Monotonic", "Convex",
"Stringy", "Skinny", "Outlying", "Sparse", "Striated", "Skewed". Also the
* prefix "Not" can be added to each measure which equals 1-measure.
separator string the separates variable names in 2d graph nodes

#### Details 

For more information run: l_help("learn_R_display_graph.html#measures")
Value
a measures object

See Also
l_ng_plots, l_ng_ranges, measures2d

#### Examples 
```{r}
## Not run:
m <- scagnostics2d(oliveAcids, separator='**')
m
m()
m(olive$palmitoleic > 80)
m('data')
m('grid')
m('measures')
## End(Not run)
```

tkcolors List the valid Tk color names

#### Description 

The core of Loon is implemented in Tcl and Tk. Hence, when defining colors using color names,
Loon uses the Tcl color representation and not those of R. The colors are taken from the Tk sources:
doc/colors.n.
If you want to make sure that the color names are represented exactly as they are in R then you can
convert the color names to hexencoded color strings, see the examples 
```{r} below.

#### Usage
<pre><code>

tkcolors()
</code></pre>
  
#### Examples 
```{r}
# check if R colors names and TK color names are the same
setdiff(tolower(colors()), tolower(tkcolors()))
setdiff(tolower(tkcolors()), tolower(colors()))
# hence there are currently more valid color names in Tk than there are in R
# Lets compare the colors of the R color names in R and Tk
tohex <- function(x) {
sapply(x, function(xi) {
crgb <- as.vector(col2rgb(xi))
rgb(crgb[1], crgb[2], crgb[3], maxColorValue = 255)
})
}
df <- data.frame(
R_col = tohex(colors()),

Tcl_col = hex12tohex6(l_hexcolor(colors())),
row.names = colors(),
stringsAsFactors = FALSE
)
df_diff <- df[df$R_col != df$Tcl_col,]
if (requireNamespace("grid", quietly = TRUE)) {
grid::grid.newpage()
grid::pushViewport(grid::plotViewport())
x_col <- grid::unit(0, "npc")
x_R <- grid::unit(6, "lines")
x_Tcl <- grid::unit(10, "lines")
grid::grid.text('color', x=x_col, y=grid::unit(1, "npc"),
just='left', gp=grid::gpar(fontface='bold'))
grid::grid.text('R', x=x_R, y=grid::unit(1, "npc"), just='center',
gp=grid::gpar(fontface='bold'))
grid::grid.text('Tcl', x=x_Tcl, y=grid::unit(1, "npc"), just='center',
gp=grid::gpar(fontface='bold'))
for (i in 1:nrow(df_diff)) {
y <- grid::unit(1, "npc") - grid::unit(i*1.2, "lines")
grid::grid.text(rownames(df_diff)[i], x=x_col, y=y, just='left')
grid::grid.rect(x=x_R, y=y, width=grid::unit(3, "line"),
height=grid::unit(1, "line"), gp=grid::gpar(fill=df_diff[i,1]))
grid::grid.rect(x=x_Tcl, y=y, width=grid::unit(3, "line"),
height=grid::unit(1, "line"), gp=grid::gpar(fill=df_diff[i,2]))
}
}
```
