---
title: "``completegraph ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```

Create a complete graph or digraph with a set of nodes

#### Description 

From Wikipedia: "a complete graph is a simple undirected graph in which every pair of distinct
vertices is connected by a unique edge. A complete digraph is a directed graph in which every pair
of distinct vertices is connected by a pair of unique edges (one in each direction

#### Usage
<pre><code>

completegraph(nodes, isDirected = FALSE)

</code></pre>

#### Arguments 

* nodes a character vector with node names, each element defines a node hence the elements need to be unique
* isDirected a boolean scalar to indicate wheter the returned object is a complete graph (undirected) or a complete digraph (directed).

#### Examples 

```{r}
g <- loon::completegraph(letters[1:5])
```

#### Details 

Note that this function masks the completegraph function of the graph package. Hence it is a good
idead to specify the package namespace with ::, i.e. loon::completegraph and graph::completegraph.
For more information run: l_help("learn_R_display_graph.html.html#graph-utilities")

#### Value
graph object of class loongraph