---
title: "condGrob "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```

Create a named grob or a template grob depending on a test

#### Description 

Creates and returns a grid object using the function given by 'grobFun' when 'test' is 'TRUE'
Otherwise a simple '``grob()``' is produced with the same parameters. All grob parameters are given
in '...'.

#### Usage
<pre><code>

condGrob(test = TRUE, grobFun = grob, name = "grob name", ...)

</code></pre>
#### Arguments 

* test Either 'TRUE' or 'FALSE' to indicate whether 'grobFun' is to be used (default
'TRUE') or not.
* grobFun The function to be used to create the grob when 'test = TRUE' (e.g. 'textGrob','polygonGrob', etc.).
* name The name to be used for the returned grob.
* ... The Arguments  to be given to the 'grobFun' (or to 'grob()' when 'test = FALSE').


#### Examples 
```{r}
myGrob <- condGrob(test = (runif(1) > 0.5),
grobFun = textGrob,
name = "my label",
label = "Some random text")
```
#### Value
A grob as produced by either the 'grobFun' given or by 'grob()' using the remaining Arguments 
. If
'test = FALSE' then the name is suffixed by ": 'grobFun name' arguments ".