---
title: "``l_make_glyphs``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```

Make arbitrary glyphs with R graphic devices

#### Description 

Loon's primitive glyph types are limited in terms of compound shapes. With this function you can
create each point glyph as a png and re-import it as a tk img object to be used as point glyphs in
loon. See the Examples.

#### Usage
<pre><code>

l_make_glyphs(data, draw_fun, width = 50, height = 50, ...)

</code></pre>

#### Arguments 

data list where each element contains a data object used for the draw_fun
draw_fun function that draws a glyph using R base graphics or the grid (including ggplot2
and lattice) engine
width width of each glyph in pixel
height height of each glyph in pixel
... additional arguments 
 passed on to the png function

#### Examples 
```{r}
## Not run:
if (requireNamespace("maps", quietly = TRUE)) {
data(minority)
p <- l_plot(minority$long, minority$lat)
canada <- maps::map("world", "Canada", fill=TRUE, plot=FALSE)
l_map <- l_layer(p, canada, asSingleLayer=TRUE)
l_scaleto_world(p)
img <- l_make_glyphs(lapply(1:nrow(minority), function(i)minority[i,]), function(m) {
par(mar=c(1,1,1,1)*.5)
mat <- as.matrix(m[1,1:10]/max(m[1:10]))
barplot(height = mat,
beside = FALSE,
ylim = c(0,1),
axes= FALSE,
axisnames=FALSE)
}, width=120, height=120)
l_imageviewer(img)
g <- l_glyph_add_image(p, img, "barplot")
p['glyph'] <- g
}
## with grid
if (requireNamespace("grid", quietly = TRUE)) {
li <- l_make_glyphs(runif(6), function(x) {
if(any(x>1 | x<0))
stop("out of range")
grid::pushViewport(grid::plotViewport(grid::unit(c(1,1,1,1)*0, "points")))
grid::grid.rect(gp=grid::gpar(fill=NA))
grid::grid.rect(0, 0, height = grid::unit(x, "npc"), just = c("left", "bottom"),
gp=grid::gpar(col=NA, fill="steelblue"))
l_move_grid 151
})
l_imageviewer(li)
p <- l_plot(1:6)
g <- l_glyph_add_image(p, li, "bars")
p['glyph'] <- g
}
## End(Not run)
```

Value
vector with tk img object references
