---
title: "``l_plot.density ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```
Loon methods for Kernel Density Estimation

#### Description 

The loon plot method for density objects.

#### Usage
<pre><code>

## S3 method for class 'density'
l_plot(x, y = NULL, ylabel = NULL, xlabel = NULL,
title = NULL, linewidth = 2, color = NULL, size = 0.5, ...)

</code></pre>
#### Arguments 
* x a density object
* y NULL . This argument is ignored.
* ylabel the graphical parameter ylabel labelling the y axis of the plot. If NULL (the default), an ylabel is created based on the combination of data name and "density".
* xlabel the graphical parameter xlabel labelling the x axis of the plot. If NULL (the default), an xlabel is created based on the information available from the density objects.
* title providing a title for the plot. If NULL (the default), the title will be the call which produced the result.
* linewidth line width, default value is 2.
* color line colour. If NULL (the default) colour will be taken from l_getOption("foreground").
* size points size, default value is 0.5
... named arguments  being states passed to ``l_plot()``.

#### Examples 
```{r}
ds <- density(faithful$eruptions)
p <- l_plot(ds, color = "steelblue")
```