---
title: "``l_setColorList_ColorBrewer``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(loon)
```


Set loon's color mapping list to the colors from ColorBrewer

#### Description 

Loon's color list is used to map nominal values to colors. See the documentation for l_setColorList.

#### Usage
<pre><code>

l_setColorList_ColorBrewer(palette = c("Set1", "Set2", "Set3", "Pastel1",
"Pastel2", "Paired", "Dark2", "Accent"))


</code></pre>
#### Arguments 

palette one of the following RColorBrewer palette name: Set1, Set2, Set3, Pastel1,
Pastel2, Paired, Dark2, or Accent

#### Details 

Only the following palettes in ColorBrewer are available: Set1, Set2, Set3, Pastel1, Pastel2, Paired,
Dark2, and Accent. See the Examples  below.
See Also
l_setColorList, l_setColorList_loon, l_setColorList_ColorBrewer, l_setColorList_hcl,
l_setColorList_baseR, l_setColorList_ggplot2

#### Examples 
```{r}
## Not run:
if (requireNamespace("RColorBrewer", quietly = TRUE)) {
RColorBrewer::display.brewer.all()
}
## End(Not run)
l_setColorList_ColorBrewer("Set1")
p <- l_plot(iris)
```