---
title: "``loonGrob``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```

Create a grid grob from a loon widget handle

#### Description 

Grid grobs are useful to create publication quality graphics.

#### Usage
<pre><code>

loonGrob(target, name = NULL, gp = NULL, vp = NULL)
## S3 method for class 'l_compound'
loonGrob(target, name = NULL, gp = NULL, vp = NULL)
## S3 method for class 'l_layer_graph'

loonGrob(target, name = NULL, gp = NULL,vp = NULL)

## S3 method for class 'l_layer_histogram'
loonGrob(target, name = NULL, gp = NULL,vp = NULL)

## S3 method for class 'l_layer_scatterplot'
loonGrob(target, name = NULL, gp = NULL, vp = NULL)

## S3 method for class 'l_navgraph'
loonGrob(target, name = NULL, gp = NULL,vp = NULL)
## S3 method for class 'l_navigator'

loonGrob(target, name = NULL, gp = NULL,vp = NULL)
## S3 method for class 'l_serialaxes'
loonGrob(target, name = NULL, gp = NULL,vp = NULL)

## S3 method for class 'l_ts'
loonGrob(target, name = NULL, gp = NULL, vp = NULL)

</code></pre>
#### Arguments 

*target either an object of class loon or a vector that specifies the widget, layer, glyph,
navigator or context completely. The widget is specified by the widget path
name (e.g. '.l0.plot'), the remaining objects by their ids.
* name a character identifier for the grob, or NULL. Used to find the grob on the display
list and/or as a child of another grob.
* gp a gpar object, or NULL, typically the output from a call to the function gpar.
This is basically a list of graphical parameter settings.
* vp a grid viewport object (or NULL).


#### Examples 
```{r}
widget <- with(iris, l_plot(Sepal.Length, Sepal.Width))
lgrob <- loonGrob(widget)
library(grid)
grid.ls(lgrob, viewports=TRUE, fullNames=TRUE)
grid.newpage(); grid.draw(lgrob)

```

```{r}
p <- demo("l_layers", ask = FALSE)$value
lgrob <- loonGrob(p)
grid.newpage(); grid.draw(lgrob)
p <- demo("l_glyph_sizes", ask = FALSE)$value
lgrob <- loonGrob(p)
grid.newpage()

grid.draw(lgrob)
## End(Not run)
```

```{r}
library(grid)
## l_pairs (scatterplot matrix) 
#### Examples 

p <- l_pairs(iris[,-5], color=iris$Species)
lgrob <- loonGrob(p)
grid.newpage()
grid.draw(lgrob)
## Time series decomposition 
#### Examples 

decompose <- decompose(co2)
# or decompose <- stl(co2, "per")
p <- l_plot(decompose, title = "Atmospheric carbon dioxide over Mauna Loa")
# To print directly use either
plot(p)
# or
grid.loon(p)
# or to save structure
lgrob <- loonGrob(p)
grid.newpage()
grid.draw(lgrob)
## End(Not run)
## Not run:
## graph 
#### Examples 
```{r}
G <- completegraph(names(iris[,-5]))
LG <- linegraph(G)
g <- l_graph(LG)
nav0 <- l_navigator_add(g)
l_configure(nav0, label = 0)
con0 <- l_context_add_geodesic2d(navigator=nav0, data=iris[,-5])
nav1 <- l_navigator_add(g, from = "Sepal.Length:Petal.Width",
to = "Petal.Length:Petal.Width", proportion = 0.6)
l_configure(nav1, label = 1)
con1 <- l_context_add_geodesic2d(navigator=nav1, data=iris[,-5])
nav2 <- l_navigator_add(g, from = "Sepal.Length:Petal.Length",
to = "Sepal.Width:Petal.Length", proportion = 0.5)
l_configure(nav2, label = 2)
loonGrob 21
con2 <- l_context_add_geodesic2d(navigator=nav2, data=iris[,-5])
# To print directly use either
plot(g)
# or
grid.loon(g)
# or to save structure
library(grid)
lgrob <- loonGrob(g)
grid.newpage(); grid.draw(lgrob)
## End(Not run)
## Not run:
## histogram 
#### Examples 

h <- l_hist(iris$Sepal.Length, color=iris$Species)
g <- loonGrob(h)
```


```{r}
library(grid)
grid.newpage(); grid.draw(g)
h['showStackedColors'] <- TRUE
g <- loonGrob(h)
grid.newpage(); grid.draw(g)
h['colorStackingOrder'] <- c("selected", unique(h['color']))
g <- loonGrob(h)
grid.newpage(); grid.draw(g)
h['colorStackingOrder'] <- rev(h['colorStackingOrder'])
# To print directly use either
plot(h)
# or
grid.loon(h)
```


```{r}
## l_plot scatterplot 
#### Examples 
```{r}
p <- l_plot(x = c(0,1), y = c(0,1))
l_layer_rectangle(p, x = c(0,1), y = c(0,1))
g <- loonGrob(p)
```


```{r}
library(grid)
grid.newpage(); grid.draw(g)
p['glyph'] <- "ctriangle"
p['color'] <- "blue"
p['size'] <- c(10, 20)
p['selected'] <- c(TRUE, FALSE)
g <- loonGrob(p)
grid.newpage(); grid.draw(g)
```


```{r}
## navgraph 
#### Examples 

ng <- l_navgraph(oliveAcids, separator='-', color=olive$Area)
# To print directly use either
plot(ng)
# or
grid.loon(ng)
# or to save structure
lgrob <- loonGrob(ng)
library(grid)
grid.newpage()
grid.draw(lgrob)
```


```{r}
## Serial axes (radial and parallel coordinate) 
#### Examples 

s <- l_serialaxes(data=oliveAcids, color=olive$Area, title="olive data")
sGrob_radial <- loonGrob(s)
library(grid)
grid.newpage(); grid.draw(sGrob_radial)
s['axesLayout'] <- 'parallel'
sGrob_parallel <- loonGrob(s)
grid.newpage(); grid.draw(sGrob_parallel)
```


```{r}
## Time series decomposition 
#### Examples 
```{r}
decompose <- decompose(co2)
# or decompose <- stl(co2, "per")
p <- l_plot(decompose, title = "Atmospheric carbon dioxide over Mauna Loa")
# To print directly use either
plot(p)
# or
grid.loon(p)
# or to save structure
loonGrob_layoutType 23
lgrob <- loonGrob(p)
grid.newpage()
grid.draw(lgrob)
```


