---
title: "loongraph"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```
loongraph Create a graph object of class loongraph

#### Description 

The loongraph class provides a simple alternative to the graph class to create common graphs that
are useful for use as navigation graphs.

#### Usage
<pre><code>

loongraph(nodes, from = character(0), to = character(0),
isDirected = FALSE)
</code></pre>

#### Arguments 

* nodes a character vector with node names, each element defines a node hence the elements need to be unique
* from a character vector with node names, each element defines an edge
* to a character vector with node names, each element defines an edge
* isDirected boolean scalar, defines whether from and to define directed edges


#### Examples 
```{r}
g <- loongraph(
nodes = c("A", "B", "C", "D"),
from = c("A", "A", "B", "B", "C"),
to = c("B", "C", "C", "D", "D")
)
## Not run:
# create a loon graph plot
p <- l_graph(g)
## End(Not run)
lg <- linegraph(g)
```

#### Details 

loongraph objects can be converted to graph objects (i.e. objects of class graph which is defined in
the graph package) with the as.graph function.
For more information run: l_help("learn_R_display_graph.html.html#graph-utilities")

#### Value
graph object of class loongraph
See Also
completegraph, linegraph, complement, as.graph
18 loonGrob