```{r include=FALSE, echo=FALSE}
library(knitr)
library(broom)
library(magrittr)
library(quickReg)
```

display_table
===================================
Display a table used in paper
Description
Display count
, frequency or mean, standard deviation and test of normality, etc.

#### Usage

<pre><code>
display_table(data
mean_or_median =
discrete_limit =
normtest = NULL,
= NULL, variables = NULL, group = NULL,
"mean", addNA = TRUE, table_margin = 2,
10, exclude_discrete = TRUE, save_to_file = NULL,
fill_variable = FALSE)

display_table_group(data = NULL, variables = NULL, group = NULL,
  super_group = NULL, group_combine = FALSE, mean_or_median = "mean",
  addNA = TRUE, table_margin = 2, discrete_limit = 10,
  exclude_discrete = TRUE, normtest = NULL, fill_variable = FALSE)
</code></pre>

#### Arguments
* ``data``: A data.frame
* ``variables`` Column indices or names of the variables in the dataset to display, the default
columns are all the variables except group variable
* ``group``: Column indices or names of the first subgroup variables. Must provide.
mean_or_median A character to specify mean or median to used for continuous variables, either
"mean" or "median". The default is "mean"
* ``addNA``: Whether to include NA values in the table, see table for more details
* `` table_margin``: Index of generate margin for, see prop.table for more details
* `` discrete_limit ``:Defining the minimal of unique value to display the variable as count and frequency, the default is 10
exclude_discrete
Logical, whether to exclude discrete variables with more unique values specified
by ``discrete_limit``
* `` save_to_file `` : A character, containing file name or path
* normtest A character indicating test of normality, the default method is shapiro.test
when sample size no more than 5000, otherwise lillie.test Kolmogorov-Smirnov is used, see package nortest for more methods.Use ’shapiro.test’, ’lil-
lie.test’, ’ad.test’, etc to specify methods.
* fill_variable A logical, whether to fill the variable column in result, the default is FALSE
* super_group Column indices or names of the further subgroup variables.
* group_combine A logical, subgroup analysis for combination of variables or for each variable.
The default is FALSE (subgroup analysis for each variable)

#### Functions
• display_table_group: Allow more subgroup analysis, see the package vignette for more
details

#### Note
The return table is a data.frame.
- P.value1 is ANOVA P value for continuous variables and chi-square test P value for discrete
variables
- P.value2 is Kruskal-Wallis test P value for continuous variables and fisher test P value for discrete
variables if expected counts less than 5
- normality is normality test P value for each group

#### Examples
```{r}
## Not run:
data(diabetes)
head(diabetes)
library(dplyr);
#library(rlang)
```

```{r}
result_1<-diabetes %>%
group_by(sex) %>%
do(display_table(data=.,variables=c("age","smoking"),group="CFHrs2230199")) %>%
ungroup()
```

```{r}
result_1
```

```{r}
result_2<-display_table_group(data=diabetes,variables=c("age","smoking"),
group="CFHrs2230199",super_group = "sex")
identical(result_1,result_2)
```

```{r}
result_2
```

```{r}
result_3<-display_table_group(data=diabetes,variables=c("age","education"),
group=c("smoking"),super_group = c("CFHrs2230199","sex"))
```

```{r}
result_3
```


```{r}
result_4<-display_table_group(data=diabetes,variables=c("age","education"),
group=c("smoking"),super_group = c("CFHrs2230199","sex"),group_combine=TRUE)
## End(Not run)
```

```{r}
result_4
```
