---
title``: "``quickregression::plot.reg``"
output``: html_document
---

```{r setup, include=FALSE}
knitr``:``:opts_chunk$set(echo = TRUE)
library(quickregression)
```


## plot the result of regression result

#### Description
plot coefficients, OR or HR of regression models.

#### Usage
<pre><code>
## S3 method for class 'reg'
plot(x, limits = c(NA, NA), sort = "order", title = NULL,
remove = TRUE, ...)
plot_reg(x, limits = c(NA, NA), sort = "order", title = NULL,
remove = TRUE, term = NULL, center = NULL, low = NULL, high = NULL,
model = NULL, ...)
</code></pre>

#### Arguments

* `` x	``:	A reg, reg_y or reg_x object without covariates information, ’``cov_show=FALSE``’
* `` limits``:	A numeric vector of length two providing limits of the scale. Use NA to refer to
			the existing minimum or maximum value.
* `` sort``:	A character determining the order of variables to plot, ’alphabetical’ or ’order’.
			The later is the default to sort variables according to their effect size.
* `` title``:	title of plot
* `` remove``:	A logical, whether to remove infinite and NA value. The default is TRUE
* `` ...``:	additional arguments. When using your own regression results rather than from
			’quickReg’, please provide ‘term‘,‘center‘,‘lower‘, ‘high‘ and ‘model‘ for plot.
* `` term``:	A character of x axis variable in plot
* `` center``:	A character of coefficient, OR or HR variable in plot
* `` low``:	A character of lower confidence interval variable
* `` high``:	A character of upper confidence interval variable
* `` model``:	A character of model, "lm", "glm" or "coxph"reg

See Also
reg, reg_x, reg_y

#### Examples
```{r}
reg_glm<-reg(data = diabetes, y = 5, factor = c(1, 3, 4), model = 'glm')
plot(reg_glm)
plot(reg_glm, limits = c(NA, 3))
```
