---
title: "``dygraph::dyAxis`` -  dygraph axis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
library(tidyverse)
```

#### Description

Define options for an axis on a dygraph plot. Note that options will use the default global setting
(as determined by dyOptions) when not specified explicitly.

#### Usage

<pre><code>

dyAxis(dygraph, name, label = NULL, valueRange = NULL, logscale = NULL,
  ticker = NULL, rangePad = NULL, labelWidth = NULL, labelHeight = NULL,
  axisHeight = NULL, axisLineColor = NULL, axisLineWidth = NULL,
  pixelsPerLabel = NULL, axisLabelColor = NULL, axisLabelFontSize = NULL,
  axisLabelWidth = NULL, axisLabelFormatter = NULL, valueFormatter = NULL,
  drawGrid = NULL, gridLineColor = NULL, gridLineWidth = NULL,
  independentTicks = NULL)
<code><pre>

#### Arguments

* ``dygraph``: Dygraph to add an axis definition to
* name Axis name (’x’, ’y’, or ’y2’)
* label Label to display for axis (defaults to none).
* valueRange Explicitly set the vertical range of the graph to c(low, high). This may be set on a per-axis basis to define each y-axis separately. If either limit is unspecified, it will be calculated automatically (e.g. c(NULL, 30) to automatically calculate
just the lower bound).
* ``logscale``: When set for the y-axis or x-axis, the graph shows that axis in log scale. Any values less than or equal to zero are not displayed. Showing log scale with ranges that go below zero will result in an unviewable graph. Not compatible with showZero. connectSeparatedPoints is ignored. This is ignored for datebased x-axes.
* ``ticker``: This lets you specify an arbitrary JavaScript function to generate tick marks on an axis. The tick marks are an array of (value, label) pairs. The built-in functions go to great lengths to choose good tick marks so, if you set this option, you’ll most likely want to call one of them and modify the result. See dygraphtickers.
js and the dygraphs documentation for additional details).
* ``rangePad``: Add the specified amount of extra space (in pixels) around the value range to ensure points at the edges remain visible.
labelWidth Width of the div which contains the y-axis label. Since the y-axis label appears rotated 90 degrees, this actually affects the height of its div.
* ``labelHeight``: Height of the x-axis label, in pixels. This also controls the default font size of the x-axis label. If you style the label on your own, this controls how much space is set aside below the chart for the x-axis label’s div.
* ``axisHeight``: Height, in pixels, of the x-axis. If not set explicitly, this is computed based on axisLabelFontSize and axisTickSize.
axisLineColor Color of the x- and y-axis lines. Accepts any value which the HTML canvas
strokeStyle attribute understands, e.g. ’black’ or ’rgb(0, 100, 255)’.
axisLineWidth Thickness (in pixels) of the x- and y-axis lines.
pixelsPerLabel Number of pixels to require between each x- and y-label. Larger values will yield a sparser axis with fewer ticks. Defaults to 50 (x-axis) or 30 (y-axes).
 * ``axisLabelColor``: Color for x- and y-axis labels. This is a CSS color string. This may also be set
globally using dyOptions.
axisLabelFontSize
Size of the font (in pixels) to use in the axis labels, both x- and y-axis. This may also be set globally using dyOptions.
axisLabelWidth Width, in pixels, of the axis labels
axisLabelFormatter
JavaScript function to call to format the tick values that appear along an axis (see the dygraphs documentation for additional details).
valueFormatter JavaScript function to call to provide a custom display format for the values
displayed on mouseover (see the dygraphs documentation for additional details).
drawGrid Whether to display grid lines in the chart.
gridLineColor The color of the grid lines.
gridLineWidth Thickness (in pixels) of the grid lines drawn under the chart.
independentTicks
Only valid for y and y2, has no effect on x: This option defines whether the y
axes should align their ticks or if they should be independent. Possible combinations:
1.) y=true, y2=false (default): y is the primary axis and the y2 ticks
are aligned to the the ones of y. (only 1 grid) 2.) y=false, y2=true: y2 is the
primary axis and the y ticks are aligned to the the ones of y2. (only 1 grid) 3.)
y=true, y2=true: Both axis are independent and have their own ticks. (2 grids)
4.) y=false, y2=false: Invalid configuration causes an error.

#### Value

Axis options
Note
See the online documentation for additional details and examples.

#### Examples
```{r}

library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>%
dyAxis("y", label = "Temp (F)", valueRange = c(40, 60)) %>%
dyOptions(axisLineWidth = 1.5, fillGraph = TRUE, drawGrid = FALSE)
```
