---
title: "dygraph::dyCandlestick "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
```


 Employ a dygraph plotter on a series, a group of series, or the whole
dygraph

#### Description

Plotters provide variuos ways to customize how your data appears on the dygraph. Series-based plotters allow users to mix-and-match different plotters on a per-series or (with dyGroup) a pergroup basis. See dyPlotter for additional detail.

#### Usage

<pre><code>

dyCandlestick(dygraph, compress = FALSE)
dyBarChart(dygraph)
dyStackedBarChart(dygraph)
dyMultiColumn(dygraph)
dyBarSeries(dygraph, name, ...)
dyStemSeries(dygraph, name, ...)
dyShadow(dygraph, name, ...)
dyFilledLine(dygraph, name, ...)
dyErrorFill(dygraph, name, ...)
dyMultiColumnGroup(dygraph, name, ...)
dyCandlestickGroup(dygraph, name, ...)
dyStackedBarGroup(dygraph, name, ...)
dyStackedLineGroup(dygraph, name, ...)
dyStackedRibbonGroup(dygraph, name, ...)

</code></pre>

#### Arguments

* ``dygraph``: Dygraph to add plotter to compress (For dyCandlestick) If true, compress data yearly, quarterly, monthly, weekly or daily according to overall amount of bars and/or current zoom level.
name name - or chrarcter vector of names - of (the) series within the data set
... additional options to pass to dySeries

#### Value

A dygraph with the specified plotter(s) employed.
Available plotters
Currently the dygraphs package provides the following plotters:
dyBarChart() Draws a bar plot rather than a line plot. If the provided dygraph features more than
one series, dyBarChart will call dyMultiColumn instead.
dyStackedBarChart() Draws a bar chart stacking all the underlying series.
dyMultiColumn() Draws multiple column bar chart.
dyBarSeries() Draws a single set of bars for just the provided series.
dyStemSeries() Draws a single set of stems for just the provided series.
dyShadow() An extraction of the _fillplotter from dygraph-combined-dev.js, drawing the filled
area without the line.
dyFilledLIne() An extraction of the _fillplotter and _lineplotter combo from dygraph-combineddev.
js. dyFilledLine allows users to fill only a single series.
dyMultiColumnGroup() The multicolumn plotter, but on a subset of the series, leaving the others
for other plotters.
dyCandlestick() Draw a candlestick chart.
dyCandleStickGroup() Employed on the provided series, but still plotting the others.
dyStackerBarGroup() Return the data group as stacked bars
dyStackerRibbonGroup() Return the data group as stacked ribbons


#### Examples
```{r}

## The following two examples will results in the same dygraph:
dygraph(mdeaths) %>%
dyBarChart()
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
dyMultiColumn()
```


```{r}
## Per-series plotters:
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
dyBarSeries('fdeaths')
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
dyStemSeries('fdeaths')
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
dyShadow('fdeaths')
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
dyFilledLine('fdeaths')
```


```{r}
## A bunch of different plotters together:
lungDeaths <- cbind(fdeaths, mdeaths, ldeaths, foo = fdeaths/2, bar = fdeaths/3)
dygraph(lungDeaths) %>%
dyRangeSelector() %>%
dyBarSeries('bar') %>%
dyStemSeries('mdeaths') %>%
dyShadow('foo') %>%
dyFilledLine('fdeaths')
```


```{r}
## Group-based plotters:
## Candlestick plotters:
library(xts)
data(sample_matrix)
library(dygraphs)
dygraph(sample_matrix) %>%
dyCandlestick()
sample<-data.frame(sample_matrix)
sample_2<-sample*2
10 dyCrosshair
names(sample_2)<-c('O', 'H', 'L', 'C')
sample<-cbind(sample, sample_2)
dygraph(sample) %>%
dyOptions(stackedGraph = TRUE) %>%
dyCandlestickGroup(c('Open', 'High', 'Low', 'Close')) %>%
dyCandlestickGroup(c('O', 'H', 'L', 'C'))
```


```{r}
## Stacked Bar and Ribbon Graphs:
dygraph(lungDeaths) %>%
dySeries('mdeaths', axis = 'y2') %>%
dyAxis('y', valueRange = c(-100, 1000)) %>%
dyStackedBarGroup(c('ldeaths', 'fdeaths'))
lungDeaths <- cbind(ldeaths, fdeaths, mdeaths,
additive = rep.int(200, length(ldeaths)),
line = rep.int(3000, length(ldeaths)))
dygraph(lungDeaths) %>%
dySeries('line', strokePattern = 'dashed') %>%
dySeries('ldeaths', stepPlot = TRUE) %>%
dyStackedBarGroup(c('additive', 'mdeaths')) %>%
dyStackedRibbonGroup(c('fdeaths', 'ldeaths'))
