---
title: "dygraph::dyCrosshair "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
```



The dyCrosshair plugin draws a crosshair line over the point closest to the mouse when the user hovers over the graph. It has a "direction"
option which is provided in the R wrapper function and then forwarded to the plugin using the "options" argument to dyPlugin.

#### Description

The dyCrosshair plugin draws a crosshair line over the point closest to the mouse when the user hovers over the graph. It has a "direction" option which is provided in the R wrapper function and then forwarded to the plugin using the "options" argument to dyPlugin.

#### Usage


<pre><code>

dyCrosshair(dygraph, direction = c("both", "horizontal", "vertical"))

<code><pre>
#### Arguments

* ``dygraph``: Dygraph to add plugin to
* ``direction``: Crosshair direction. Valid options are: "both", "horizontal", "vertical"

#### Value

Dygraph with Crosshair plugin enabled
dyCSS 11

#### Examples
```{r}

library(dygraphs)
dygraph(ldeaths) %>%
dyRangeSelector() %>%
dyCrosshair(direction = "vertical")
```
