---
title: "``dygraph::dyEvent`` dygraph event line"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
library(tidyverse)
```



#### Description

Add a vertical event line to a dygraph

#### Usage
<pre><code>

dyEvent(dygraph, x, label = NULL, labelLoc = c("top", "bottom"),
color = "black", strokePattern = "dashed", date)

<code><pre>

#### Arguments

* ``dygraph``: Dygraph to add event line to
* x Either numeric or date/time for the event, depending on the format of the xaxis of the dygraph. (For date/time must be a POSIXct object or another object convertible to POSIXct via as.POSIXct)
* label Label for event. Defaults to blank.
* ``labelLoc``: Location for label (top or bottom)
* ``color``: Color of event line. This can be of the form "#AABBCC" or "rgb(255,100,200)" or "yellow". Defaults to black.
* strokePattern A predefined stroke pattern type ("dotted", "dashed", "dotdash", or "solid") or a
custom pattern array where the even index is a draw and odd is a space in pixels. Defaults to dashed.
* date (deprecated) See argument x.



#### Examples
```{r}

library(dygraphs)
dygraph(presidents, main = "Presidential Approval") %>%
dyAxis("y", valueRange = c(0, 100)) %>%
dyEvent("1950-6-30", "Korea", labelLoc = "bottom") %>%
dyEvent("1965-2-09", "Vietnam", labelLoc = "bottom")
dygraph(presidents, main = "Presidential Approval") %>%
dyAxis("y", valueRange = c(0, 100)) %>%
dyEvent(c("1950-6-30", "1965-2-09"), c("Korea", "Vietnam"), labelLoc = "bottom")

```

#### Value

A dygraph with the specified event line.

#### Note
See the online documentation for additional details and examples.
