  
  
---
title: "``dygraph::dyHighlight `` -   dygraph series mouse-over highlighting"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
library(tidyverse)
```


#### Description

Configure options for data series mouse-over highlighting. Note that highlighting is always enabled
for dygraphs so this function is used to customize rather than enable highlighting.

#### Usage

<pre><code>

dyHighlight(dygraph, highlightCircleSize = 3,
   highlightSeriesBackgroundAlpha = 0.5, 
   highlightSeriesOpts = list(),
   hideOnMouseOut = TRUE)

<code><pre>
#### Arguments

* ``dygraph``: Dygraph to configure highlighting behavior for.
* ``highlightCircleSize```: The size in pixels of the dot drawn over highlighted points.
* ``highlightSeriesBackgroundAlpha``: Fade the background while highlighting series. 1=fully visible background (disable fading), 0=hidden background (show highlighted series only).
* ``highlightSeriesOpts``:
When set, the options from this list are applied to the series closest to the mouse pointer for interactive highlighting. 
 - Example: list(strokeWidth = 3). See the documentation on dySeries for additional details on options that can be set.
* ``hideOnMouseOut``: Whether to hide the highlighting effects when the mouse leaves the chart area.
Note that this also affects the hiding of the dyLegend on mouse out.



#### Examples

```{r}
library(dygraphs)
lungDeaths <- cbind(ldeaths, mdeaths, fdeaths)
dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
dyHighlight(highlightCircleSize = 5,
highlightSeriesBackgroundAlpha = 0.2,
hideOnMouseOut = FALSE)
```

#### Value

A dygraph with customized highlighting options

#### Note

See the online documentation for additional details and examples.
