  
---
title: "``dygraph::dyLimit `` -  dygraph limit line"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
library(tidyverse)
```



#### Description

Add a horizontal limit line to a dygraph

#### Usage

<pre><code>
dyLimit(dygraph, limit, label = NULL, labelLoc = c("left", "right"),
color = "black", strokePattern = "dashed")
</code></pre>

#### Arguments

* ``dygraph``: Dygraph to add limit line to
* limit Numeric position of limit.
* label Label for limit. Defaults to blank.
* labelLoc Location for label (left or right).
* color Color of limit line. This can be of the form "#AABBCC" or "rgb(255,100,200)" or "yellow". Defaults to black.
* strokePattern A predefined stroke pattern type ("dotted", "dashed", "dotdash", or "solid") or a
* custom pattern array where the even index is a draw and odd is a space in pixels.
* Defaults to dashed.

#### Value

A dygraph with the specified limit line.
Note
See the online documentation for additional details and examples.

#### Examples
```{r}

library(dygraphs)
dygraph(presidents, main = "Presidential Approval") %>%
  dyAxis("y", valueRange = c(0, 100)) %>%
  dyLimit(max(presidents, na.rm = TRUE), "Max",
  strokePattern = "solid", color = "blue")
```
