---
title: "``dygraph::dyRangeSelector``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dygraph)
```

 dygraph interactive range selection and zooming

#### Description

Add a range selector to the bottom of the chart that allows users to pan and zoom to various date ranges.

#### Usage

<pre><code>
dyRangeSelector(dygraph, dateWindow = NULL, height = 40,
  fillColor = " #A7B1C4", strokeColor = "#808FAB", keepMouseZoom = TRUE,
  retainDateWindow = FALSE)
</code></ pre>

#### Arguments

* ``dygraph``: Dygraph to add range selector to
* ``dateWindow``: Initially zoom in on a section of the graph. Is a two element vector [earliest, latest], where earliest/latest objects convertible via as.POSIXct.
* ``height``: Height, in pixels, of the range selector widget.
* ``fillColor``: The range selector mini plot fill color. This can be of the form "#AABBCC" or "rgb(255,100,200)" or "yellow". You can also specify "" to turn off fill.
* ``strokeColor``: The range selector mini plot stroke color. This can be of the form "#AABBCC" or "rgb(255,100,200)" or "yellow". You can also specify "" to turn off stroke.
* ``keepMouseZoom``: Keep mouse zoom when adding a range selector
* ``retainDateWindow``: Whether to retain the user’s current date window (zoom level) when updating an existing dygraph with new data and/or options.


#### Examples
```{r}

library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>%
  dyRangeSelector()

dygraph(nhtemp, main = "New Haven Temperatures") %>%
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))

dygraph(nhtemp, main = "New Haven Temperatures") %>%
  dyRangeSelector(height = 20, strokeColor = "")

```

#### Value

A dygraph that displays a range selector


### Note
See the online documentation for additional details and examples.

Shiny applications can respond to changes in the dateWindow via a special date window shiny input value. For example, if the output id of a dygraph is ‘series‘ then the current date window can be read from input$series_date_window as an array of two date values (from and to).
