grouped_augment
Augmented data from grouped analysis of any function that has data
argument in its function call.

#### Description

Augmented data from grouped analysis of any function that has data argument in its function call.

#### Usage

grouped_augment(data, grouping.vars, ..f, ..., augment.args = list())

#### Arguments

data Dataframe (or tibble) from which variables are to be taken.
grouping.vars Grouping variables.
..f A function, or function name as a string.
... 
#### Arguments
 to function.
These dots support tidy-dots features.
augment.args A list of arguments to be used in the relevant S3 method.
Value
A tibble::tibble() with information about data points.
Methods
No methods found in currently loaded packages.

#### Examples
```{r}
set.seed(123)
# to speed up computation, let's use only 50% of the data
# linear model
broomExtra::grouped_augment(
data = dplyr::sample_frac(tbl = ggplot2::diamonds, size = 0.5),
grouping.vars = c(cut, color),
formula = price ~ carat - 1,
..f = stats::lm,
na.action = na.omit
)
```

```{r}
# linear mixed effects model
broomExtra::grouped_augment(
 data = dplyr::sample_frac(tbl = ggplot2::diamonds, size = 0.5),
 grouping.vars = cut,
 ..f = lme4::lmer,grouped_glance
)

formula = price ~ carat + (carat | color) - 1,
control = lme4::lmerControl(optimizer = "bobyqa")
```

Author(s)
Indrajeet Patil
