
---
title: "``l_bind_canvas_ids ``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```



l_bind_canvas_ids List canvas binding ids

#### Description 

List all user added canvas binding ids

#### Usage
<pre><code>
l_bind_canvas_ids(widget)
</code></pre>

#### Arguments 
* ``widget``: widget path as a string or as an object handle

#### Examples 
```{r}
# binding for when plot is resized
p <- l_plot(iris[,1:2], color=iris$Species)
printSize <- function(p) {
size <- l_size(p)
cat(paste('Size of widget ', p, ' is: ',
size[1], 'x', size[2], ' pixels\n', sep=''))
}
l_bind_canvas(p, event='<Configure>', function(W) {printSize(W)})
id <- l_bind_canvas_ids(p)
id
```


#### Details 

Bindings, callbacks, and binding substitutions are described in detail in loon's documentation webpage,
i.e. run l_help("learn_R_bind")

##### Value
vector with canvas binding ids
See Also
l_bind_canvas, l_bind_canvas_get, l_bind_canvas_delete, l_bind_canvas_reorder
