
---
title: "``l_bind_canvas_get``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```


l_bind_canvas_get Get the event pattern and callback Tcl code of a canvas binding

#### Description 

This function returns the registered event pattern and the Tcl callback code that the Tcl interpreter
evaluates after a event occurs that machtches the event pattern.

#### Usage
<pre><code>

l_bind_canvas_get(widget, id)
28 l_bind_canvas_ids

</code></pre>
#### Arguments 

* ``widget``: widget path as a string or as an object handle
* ``id``: canvas binding id

#### Details 

Bindings, callbacks, and binding substitutions are described in detail in loon's documentation webpage,
i.e. run l_help("learn_R_bind")

#### Value
Character vector of length two. First element is the event pattern, the second element is the Tcl
callback code.

#### See Also
l_bind_canvas, l_bind_canvas_ids, l_bind_canvas_delete, l_bind_canvas_reorder

#### Examples 
```{r}
# binding for when plot is resized
p <- l_plot(iris[,1:2], color=iris$Species)
printSize <- function(p) {
  size <- l_size(p)
  cat(paste('Size of widget ', p, ' is: ',
            size[1], 'x', size[2], ' pixels\n', sep=''))
}
l_bind_canvas(p, event='<Configure>', function(W) {printSize(W)})
id <- l_bind_canvas_ids(p)
id

l_bind_canvas_get(p, id)
```
