---
title: "``VIM::bgmap``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

#### Description 

Plot a background map.

#### Usage 

<pre><code>
bgmap(map, add = FALSE, ...)
</code></pre>

#### Arguments
* ``map``: either a matrix or data.frame with two columns, a list with components x and y, or an object of any class that can be used for maps and provides its own plot method (e.g., "SpatialPolygons" from package sp). A list of the previously
mentioned types can also be provided.
* ``add``: a logical indicating whether map should be added to an already existing plot (the default is FALSE).
* ``...``: further arguments and graphical parameters to be passed to plot and/or lines.

#### Examples 
```{r}
data(kola.background, package = "VIM")
bgmap(kola.background)
```


#### Author(s)
Andreas Alfons
References
M. Templ, A. Alfons, P. Filzmoser (2012) Exploring incomplete data using visualization tools.
Journal of Advances in Data Analysis and Classification, Online first. DOI: 10.1007/s11634-011-
0102-y.
