---
title: "``prettyR::brkdn``"
output: html_document
---

  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(PrettyR)
```


brkdn Breakdown of a numeric variable by grouping variable(s)

#### Description
Calculates means, variances and ns for subgroups of numeric observations and displays the results.

#### Usage
<pre><code>
brkdn(formula,data,maxlevels=10,num.desc=c("mean","var","valid.n"),
width=10,round.n=2)
</code></pre>

#### Arguments 
* ``formula``: a formula with the variable to be broken down on the left and the names of one or more variables defining subgroups on the right data the data frame from which to select the variables
* ``maxlevels``: the maximum number of levels in any subgroup
* ``num.desc``: names of the summary functions to apply to the variable on the left side of the formula
* ``width``: The number of characters to allow for each column in the summary output.
* ``round.n``: The number of decimal places to round the output.


#### Examples 
```{r}
test.df<-data.frame(Age=rnorm(100)+3*10,Sex=sample(c("M","F"),100,TRUE),
Employ=sample(c("FT","PT","NO"),100,TRUE))
# add value labels for Employ in alphabetical order so they match
attr(test.df$Employ,"value.labels")<-c("Full time","None","Part time")
brkdn(Age~Sex+Employ,test.df)
```
#### Details
‘brkdn’ will accept a formula referring to columns in a data frame. It calls ‘describe.numeric’ for the calculations and displays a table of results.

#### Value
The results of ‘describe.numeric’, or a multi-level list if more than one grouping variable is specified.

#### Author(s)
Jim Lemon

