---
title: "``prettyR::describe.numeric``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Description

Describes a numeric variable.

#### Usage
<pre><code>
describe.numeric(x,varname="",
num.desc=c("mean","median","var","sd","valid.n"))
</code></pre>

#### Arguments 
* ``x``: A numeric vector.
* ``varname``: The variable name to display.
* ``num.desc``: The names of the functions to apply to the vector.

#### Examples 
```{r}
x<-rnorm(100)
# include a function that calculates the "smoothness" of a vector
# of numbers by calculating the mean of the absolute difference
# between each successive value - all values equal would be 0

smoothness<-function(x,na.rm=TRUE) {
  if(na.rm) x<-x[!is.na(x)]
  xspan<-diff(range(x))
  return(mean(abs(diff(x))/xspan,na.rm=TRUE))
  }
  
describe(x,num.desc=c("mean","median","smoothness"),xname="x")

# now sort the values to make the vector "smoother"
describe(sort(x),num.desc=c("mean","median","smoothness"),xname="x")
```

#### Details
describe.numeric’ displays the name of the vector and the results of the functions whose names are passed in ‘num.desc’. Note that any functions that are called by ‘describe.numeric’ must have an ‘na.rm’ argument, even if it is a dummy.

#### Value
The vector of values returned from the functions in ‘num.desc’.
Author(s)
Jim Lemon

