---

title: "``freq``"

output: html_document

---

  

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(PrettyR)

```



freq Calculate a frequency table
#### Description
Calculates one or more frequency table(s) from a vector, matrix or data frame.

#### Usage
<pre><code>
freq(x,variable.labels=NULL,display.na=TRUE,decr.order=TRUE)
</code></pre>

#### Arguments 
* x a vector, matrix or data frame.
* variable.labels optional labels for the variables. The default is the name of the variable passed
or the ‘names’ attribute if the variable has more than 1 dimension.
* display.na logical - whether to display counts of NAs.
* decr.order Whether to order each frequency table in decreasing order.


#### Examples 
```{r}
A<-sample(1:10,130,TRUE)
A[sample(1:130,6)]<-NA
C<-sample(LETTERS[1:14],130,TRUE)
C[sample(1:130,7)]<-NA
test.df<-data.frame(A,C)
freq(test.df)
```


#### Details
‘freq’ calls ‘table’ to get the frequency counts and builds a list with one or more components
containing the value labels and counts.

#### Value
A list with one or more components. Each component includes the values of the relevant variable
as the names.

#### Note
The limit on the number of bins has been removed, so passing a numeric vector with many levels
may produce a huge, useless "frequency" table.
Author(s)
Jim Lemon
See Also
print.freq
