---
title: "prettyR::stretch_df"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(prettyR)
```

Reshape a data frame from "long" to "wide" format

#### Description

Reshape a data frame by reducing the multiple rows of repeated variables to a single row for each instance (usually a "case" or object) and stretching out the variables that are not repeated within each case.

#### Usage
<pre><code>
stretch_df(x,idvar,to.stretch,ordervar=NA,include.ordervar=TRUE)
</code></pre>

#### Arguments 
* ``x``: A data frame.
* ``idvar``: A variable that identifies instances (cases or objects).
* ``to.stretch``: Which variables are to be stretched out in the single row.
* ``ordervar``: Variable that gives the order of the stretched variables.
* ``include.ordervar``: Include the ordering variable in the output.


#### Examples 
```{r}
# create a data frame with two repeated variables
longdf<-data.frame(ID=c(rep(111,3),rep(222,4),rep(333,6),rep(444,3)),
name=c(rep("Joe",3),rep("Bob",4),rep("Sue",6),rep("Bea",3)),
score1=sample(1:10,16,TRUE),score2=sample(0:100,16),
scoreorder=c(1,2,3,4,3,2,1,4,6,3,5,1,2,1,2,3))
stretch_df(longdf,"ID",c("score1","score2"),"scoreorder")
```

#### Details
‘stretch_df’ takes a data frame in which at least some instances have multiple rows and reshapes it into a "wide" format with one row per instance. The variable passed as ‘idvar’ distinguishes the instances, and will be the first column in the new data frame. All other variables in the data frame except those named in ‘to.stretch’ and ‘ordervar’ will follow ‘idvar’. The variables named in ‘to.stretch’ will follow the variables that are not repeated in the initial data frame, along with the order variable if ‘include.ordervar’ is TRUE.

#### Value
The reshaped data frame.
32 toNA

#### Note
‘stretch_df’ mostly does what other reshaping functions can do, but may be more easy to understand.
It will stretch multiple variables, something that some reshaping functions will not do.
Author(s)
Jim Lemon
See Also
reshape
