---
title: "xtab Crosstabulate variables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(PrettyR)
```


#### Description
Crosstabulates variables with small numbers of unique values.
Usage
xtab(formula,data,varnames=NULL,or=TRUE,chisq=FALSE,phi=FALSE,html=FALSE,
bgcol="lightgray")
xtab 35
#### Arguments 
* formula a formula containing the variables to be crosstabulated
* data the data frame from which to select the variables
* varnames optional labels for the variables (defaults to ‘names(data))’ or whether to calculate the odds ratio (only for 2x2 tables).
* chisq logical - whether to display chi squared test(s) of the table(s)
* phi whether to calculate and display the phi coefficient of association - only for 2x2 tables
* html whether to format the resulting table with HTML tags. 
* bgcol background color for the table if html=TRUE.


#### Examples 
```{r}
test.df<-data.frame(sex=sample(c("MALE","FEMALE"),1000,TRUE),
suburb=sample(1:4,1000,TRUE),social.type=sample(LETTERS[1:4],1000,TRUE))
xtab(sex~suburb+social.type,test.df,chisq=TRUE)
# now add some value labels
attr(test.df$suburb,"value.labels")<-1:4
names(attr(test.df$suburb,"value.labels"))<-
c("Upper","Middle","Working","Slum")
attr(test.df$social.type,"value.labels")<-LETTERS[1:4]
names(attr(test.df$social.type,"value.labels"))<-
c("Gregarious","Mixer","Aloof","Hermit")
xtab(sex~suburb+social.type,test.df)
```

now have some fun with ridiculously long factor labels

```{r}
testxtab<-data.frame(firstbit=sample(c("Ecomaniacs","Redneck rogues"),50,TRUE),
secondbit=sample(c("Macho bungy jumpers","Wimpy quiche munchers"),50,TRUE))
# and format the table in HTML and add some tests
xtab(secondbit~firstbit,testxtab,html=TRUE,chisq=TRUE,phi=TRUE)
```

#### Details
‘xtab’ will accept a formula referring to columns in a data frame or two explicit variable names. It
calls ‘calculate.xtab’ for the calculations and displays one or more tables of results by calling
‘print.xtab’. If ‘html’ is TRUE, the resulting table will be formatted with HTML tags.
Value
The result of ‘calculate.xtab’ if there is only one table to display, otherwise a nested list of tables.
Author(s)
Jim Lemon
See Also
table, calculate.xtab, print.xtab
