---
title: "``timevis::centerItem``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(timevis)
```

#### Description

Move the window such that given item or items are centered

#### Usage

<pre><code>
centerItem(id, itemId, options)
<code></pre>

#### Arguments

id
itemId
options
Timeline id or a timevis object (the output from timevis())
A vector (or single value) of the item ids to center
Named list of options controlling mainly the animation. Most common option is "animation" = TRUE/FALSE. For a full list of options, see the "focus" method in the official Timeline documentation

#### Examples
```{r}
timevis(data.frame(
  id = 1:3,
  start = c(Sys.Date() - 1, Sys.Date(), Sys.Date() + 1),
  content = c("Item 1", "Item 2", "Item 3"))
) %>%
  centerItem(1)

if (interactive()) {
  library(shiny)
  shinyApp(
    ui = fluidPage(
      timevisOutput("timeline"),
      actionButton("btn", "Center around item 1")
    ),
    server = function(input, output) {
      output$timeline <- renderTimevis(
        timevis(
          data.frame(id = 1:3,
                     start = c(Sys.Date() - 1, Sys.Date(), Sys.Date() + 1),
                     content = c("Item 1", "Item 2", "Item 3"))
        )
      )
      observeEvent(input$btn, {
        centerItem("timeline", 1)
      })
    }
  )
}
```
