---
title: "Untitled"
author: "Kevin O Brien"
date: "28 August 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


find_skewness Finding skewed variables

### Description 

Find the numerical variable that skewed variable that inherits the data.frame or data.frame.

### Usage 
<pre><code>

find_skewness(.data, index = TRUE, value = FALSE, thres = NULL)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* `index``:  logical. When representing the information of a skewed variable, specify whether
or not the variable is represented by an index. Returns an index if TRUE or a variable names if FALSE.
value logical. If TRUE, returns the skewness value in the individual variable.
* thres Returns a skewness threshold value that has an absolute skewness greater than thres. The default is NULL to ignore the threshold. but, If value = TRUE, default to 0.5.
get_class 47

### Value 

Information on variables including skewness.

### See Also
 
find_na, find_outliers.

### Examples
```{r}

## Not run:
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
find_skewness(carseats)
find_skewness(carseats, index = FALSE)
find_skewness(carseats, thres = 0.1)
find_skewness(carseats, value = TRUE)
find_skewness(carseats, value = TRUE, thres = 0.1)
```

```{r}
## using dplyr -------------------------------------
library(dplyr)
# Perform simple data quality diagnosis of variables with outliers.
carseats %>%
select(find_skewness(.)) %>%
diagnose()
## End(Not run)
```