---
title: "``dlookr::find_outliers``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```



### Description 

Find the numerical variable that contains outliers in the object that inherits the data.frame or data.frame.

### Usage 
<pre><code>

find_outliers(.data, index = TRUE, rate = FALSE)

</code></pre>
### Arguments
 
* ``.data``: a data.frame or a tbl_df.
* `index``:  logical. When representing the information of a variable including outliers,
specify whether or not the variable is represented by an index. Returns an index
if TRUE or a variable names if FALSE.
rate logical. If TRUE, returns the percentage of outliers in the individual variable.

### Value 

Information on variables including outliers.
46 find_skewness

### See Also
 
find_na, imputate_outlier.

### Examples
```{r}

## Not run:
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
find_outliers(carseats)
find_outliers(carseats, index = FALSE)
find_outliers(carseats, rate = TRUE)
```

```{r}
## using dplyr -------------------------------------
library(dplyr)
# Perform simple data quality diagnosis of variables with outliers.
carseats %>%
select(find_outliers(.)) %>%
diagnose()
## End(Not run)
```