---
title: "Untitled"
author: "Kevin O Brien"
date: "28 August 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

find_class Extract variable names or indices of a specific class

### Description 

The find_class() extracts variable information having a certain class from an object inheriting
data.frame.

### Usage 
<pre><code>

find_class(df, type = c("numerical", "categorical", "categorical2"),
index = TRUE)

</code></pre>
### Arguments
 
df a data.frame or objects inheriting from data.frame
type character. Defines a group of classes to be searched. "numerical" searches for "numeric" and "integer" classes, "categorical" searches for "factor" and "ordered"
classes. "categorical2" adds "character" class to "categorical".
* `index``:  logical. If TRUE is return numeric vector that is variables index. and if FALSE is return character vector that is variables name. defalut is TRUE.

### Value 

character vector or numeric vector. The meaning of vector according to data type is as follows.
*  character vector : variables name
*  numeric vector : variables index
44 find_na

### See Also
 
get_class.

### Examples
```{r}

## Not run:
# data.frame
find_class(iris, "numerical")
find_class(iris, "numerical", index = FALSE)
find_class(iris, "categorical")
find_class(iris, "categorical", index = FALSE)
# tbl_df
find_class(ISLR::Carseats, "numerical")
find_class(ISLR::Carseats, "numerical", index = FALSE)
find_class(ISLR::Carseats, "categorical")
find_class(ISLR::Carseats, "categorical", index = FALSE)
# type is "categorical2"
iris2 <- data.frame(iris, char = "chars",
stringsAsFactors = FALSE)
find_class(iris2, "categorical", index = FALSE)
find_class(iris2, "categorical2", index = FALSE)
## End(Not run)
```
