---
title: "``dlookr::find_na``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dlookr)
```

### Description 

Find the variable that contains the missing value in the object that inherits the data.frame or data.frame.

### Usage 

<pre><code>

find_na(.data, index = TRUE, rate = FALSE)

</code></pre>

### Arguments
 
* ``.data``: a data.frame or a ``tbl_df``.
* `index``:  logical. When representing the information of a variable including missing values,
specify whether or not the variable is represented by an index. Returns an index if TRUE or a variable names if FALSE.
* ``rate``: logical. If TRUE, returns the percentage of missing values in the individual variable.

### Value 

Information on variables including missing values.
find_outliers 45

### See Also
 
imputate_na, find_na.

### Examples
```{r}

## Not run:
# Generate data for the example
carseats <- ISLR::Carseats
carseats[sample(seq(NROW(carseats)), 20), "Income"] <- NA
carseats[sample(seq(NROW(carseats)), 5), "Urban"] <- NA
find_na(carseats)
find_na(carseats, index = FALSE)
find_na(carseats, rate = TRUE)
```

```{r}
## using dplyr -------------------------------------
library(dplyr)
# Perform simple data quality diagnosis of variables with missing values.
carseats %>%
select(find_na(.)) %>%
diagnose()
## End(Not run)
```