---
title: "Statistics with R"
subtitle: "Statistical Modelling with R for Actuarial Students"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(flashlight)
library(janitor)

options(scipen = 2, digits = 3) #set to two decimal 
```

```{css, echo=FALSE}
pre {
  background: #ADD8E6;
  max-width: 100%;
  overflow-x: scroll;
}
```

---

Grouped Weighted Means or Quartiles

#### Description

Calculates weighted means or quartiles (and counts) of a variable grouped by optional columns.

---

#### Usage
<pre><code>

grouped_stats(data, xNULL, by = NULL, stats = c("mean",
"quartiles"), counts = TRUE, counts_weighted = FALSE,
counts_name = "counts", value_name = x, q1_name = "q1",
q3_name = "q3", ...)
</code></pre>

---

#### Arguments
data A data.frame.
x Variable name in data to summarize.
w Optional name of the column in data with case weights.
* ***by***: An optional vector of column names in data used to group the results.
stats Statistic to calculate: "mean" or "quartiles".
counts Should group counts be added?
counts_weighted
Should counts be weighted by the case weights? If TRUE, the sum of w is
returned by group.

--- 

* ***counts_name***:  Name of column in the resulting data.frame containing the counts.
value_name Name of the resulting column with mean or median.
q1_name Name of the resulting column with first quartile values. Only relevant for stats "quartiles".
q3_name Name of the resulting column with third quartile values. Only relevant for stats "quartiles".
... Additional arguments passed to MetricsWeighted::weighted_mean or weighted_quartiles.


---

#### Value

A data.frame with columns by, x and optionally counts_name.

#### Examples

```{r}

grouped_stats(iris, "Sepal.Width")
grouped_stats(iris, "Sepal.Width", stats = "quartiles")
```

---

```{r}
grouped_stats(iris, "Sepal.Width", w = "Petal.Width")
grouped_stats(iris, "Sepal.Width", w = "Petal.Width", counts_weighted = TRUE)
grouped_stats(iris, "Sepal.Width", by = "Species")
```

---

```{r}
grouped_stats(iris, "Sepal.Width", stats = "quartiles", by = "Species")
grouped_stats(iris, "Sepal.Width", w = "Petal.Width", by = "Species")
```

---

```{r}
grouped_stats(iris, "Sepal.Width", w = "Petal.Width",
counts_weighted = TRUE, by = "Species")
```
---

```{r}
grouped_stats(iris, "Sepal.Width", counts = FALSE)
grouped_stats(iris, "Sepal.Width", counts_name = "n",
stats = "quartiles", q1_name = "p25", q3_name = "p75")
```
