---
title: "``dist_t ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Visualize t distribution

#### Description 
 
Visualize how degrees of freedom affect the shape of t-distribution, visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_t_plot(df = 3)
dist_t_perc(probs = 0.95, df = 4, type = c("lower", "upper", "both"))
dist_t_prob(perc, df, type = c("lower", "upper", "interval", "both"))

</code></pre>
#### Arguments 
 
* ``df`` :  Degrees of freedom.
* ``probs ``: Probability value.
* ``type``: Lower tail, upper tail, interval or both.
perc Quantile value.


#### Examples 
```{r}

# visualize t distribution
dist_t_plot()
dist_t_plot(6)
dist_t_plot(df = 8)
# visualize quantiles out of given probability
dist_t_perc(probs = 0.95, df = 4, type = 'lower')
dist_t_perc(probs = 0.35, df = 4, type = 'upper')
dist_t_perc(probs = 0.69, df = 7, type = 'both')
# visualize probability from a given quantile
dist_t_prob(2.045, 7, 'lower')
dist_t_prob(0.945, 7, 'upper')
dist_t_prob(1.445, 7, 'interval')
dist_t_prob(1.6, 7, 'both')
```

#### Value
Percentile for the probs based on df and type or probability value for the perc based on df and
type.
Deprecated functions
t_plot(), t_prob() and t_per() have been deprecated. Instead use dist_t_plot(), dist_t_prob()
and dist_t_perc().
See Also
TDist
