---
title: "``dist_norm_plot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```


Visualize normal distribution

#### Description 
 
* Visualize how changes in mean and standard deviation affect the shape of the normal distribution.

* Compute & visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_norm_plot(mean = 0, sd = 1)
dist_norm_perc(probs = 0.95, mean = 0, sd = 1, type = c("lower","upper", "both"))
dist_norm_prob(perc, mean = 0, sd = 1, type = c("lower", "upper", "both"))

</code></pre>
#### Arguments 
 
mean Mean of the normal distribution.
sd Standard deviation of the normal distribution.
probs Probability value.
type Lower tail, upper tail or both.
perc Quantile value.



#### Examples 
```{r}

# visualize normal distribution
dist_norm_plot()
dist_norm_plot(mean = 2, sd = 0.6)
# visualize probability from a given quantile
dist_norm_prob(3.78, mean = 2, sd = 1.36)
dist_norm_prob(3.43, mean = 2, sd = 1.36, type = 'upper')
dist_norm_prob(c(-1.74, 1.83), type = 'both')
# visualize quantiles out of given probability
dist_norm_perc(0.95, mean = 2, sd = 1.36)
dist_norm_perc(0.3, mean = 2, sd = 1.36, type = 'upper')
dist_norm_perc(0.95, mean = 2, sd = 1.36, type = 'both')
```

#### Value
Percentile for the probs based on mean, sd and type or probability value for perc based on mean,
sd and type.

#### Deprecated functions
norm_plot(), norm_prob() and norm_per() have been deprecated. Instead use dist_norm_plot(),
dist_norm_prob() and dist_norm_per().
See Also
Normal
