---
title: "dist_chi_plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```

### Visualize chi square distribution

#### Description 
 
Visualize how changes in degrees of freedom affect the shape of the chi square distribution. Compute
& visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_chi_plot(df = 3, normal = FALSE)
dist_chi_perc(probs = 0.95, df = 3, type = c("lower", "upper"))
dist_chi_prob(perc, df, type = c("lower", "upper"))

</code></pre>
#### Arguments 
 
* ``df`` :  Degrees of freedom.
normal If TRUE, normal curve with same mean and sd as the chi square distribution is
drawn.
* ``probs ``: Probability value.
type Lower tail or upper tail.
perc Quantile value.

#### Examples 
```{r}

# visualize chi square distribution
dist_chi_plot()
dist_chi_plot(df = 5)
dist_chi_plot(df = 5, normal = TRUE)
# visualize quantiles out of given probability
dist_chi_perc(0.165, 8, 'upper')
dist_chi_perc(0.22, 13, 'upper')
# visualize probability from a given quantile.
dist_chi_prob(13.58, 11, 'lower')
dist_chi_prob(15.72, 13, 'upper')
```

Value
Percentile for the probs based on df and type or probability value for perc based on df and type.
Deprecated functions
chi_plot(), chi_prob() and chi_per() have been deprecated. Instead use dist_chi_plot(),
dist_chi_prob() and dist_chi_perc().
dist_f_plot 5
See Also
Chisquare
