---
title: "``dist_f_plot``"
author: "Kevin O'Brien"
date: "26 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```
 Visualize f distribution

#### Description 
 
Visualize how changes in degrees of freedom affect the shape of the F distribution. Compute &
visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_f_plot(num_df = 4, den_df = 30, normal = FALSE)
dist_f_perc(probs = 0.95, num_df = 3, den_df = 30, type = c("lower",
"upper"))
dist_f_prob(perc, num_df, den_df, type = c("lower", "upper"))

</code></pre>
#### Arguments 
 
num_* ``df`` :  Degrees of freedom.associated with the numerator of f statistic.
den_* ``df`` :  Degrees of freedom.associated with the denominator of f statistic.
normal If TRUE, normal curve with same mean and sd as the F distribution is drawn.
* ``probs ``: Probability value.
type Lower tail or upper tail.
perc Quantile value.


#### Examples 
```{r}

# visualize F distribution
dist_f_plot()
dist_f_plot(6, 10, normal = TRUE)
# visualize probability from a given quantile
dist_f_perc(0.95, 3, 30, 'lower')
dist_f_perc(0.125, 9, 35, 'upper')
# visualize quantiles out of given probability
dist_f_prob(2.35, 5, 32)
dist_f_prob(1.5222, 9, 35, type = "upper")
```

6 dist_norm_plot
Value
Percentile for the probs based on num_df, den_df and type or probability value for perc based on
num_df, den_df and type.
Deprecated functions
f_plot(), f_prob() and f_per() have been deprecated. Instead use dist_f_plot(), dist_f_prob()
and dist_f_perc().
See Also
FDist