---
title: "``dist_binom_plot ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```
Visualize binomial distribution

#### Description 
 
Visualize how changes in number of trials and the probability of success affect the shape of the
binomial distribution. Compute & visualize probability from a given quantile and quantiles out of
given probability.

#### Usage 
<pre><code>

dist_binom_plot(n, p)
dist_binom_prob(n, p, s, type = c("lower", "upper", "exact", "interval"))
dist_binom_perc(n, p, tp, type = c("lower", "upper"))

</code></pre>
#### Arguments 
 
n Number of trials.
p Aggregate probability.
s Number of success.
type Lower/upper/exact/interval.
tp Probability of success in a trial.
Value
A list containing the following components:
avg Mean of the binomial distribution,
stdev Standard deviation of the binomial distribution.
prob Probability of success.

#### Examples 
```{r}

# visualize binomial distribution
dist_binom_plot(10, 0.3)
# visualize probability from a given quantile
dist_binom_prob(10, 0.3, 4, type = 'exact')
dist_binom_prob(10, 0.3, 4, type = 'lower')
dist_binom_prob(10, 0.3, 4, type = 'upper')
dist_binom_prob(10, 0.3, c(4, 6), type = 'interval')
# visualize quantiles out of given probability
dist_binom_perc(10, 0.5, 0.05)
dist_binom_perc(10, 0.5, 0.05, "upper")
```

Deprecated functions
binom_plot(), binom_prob(), binom_perc() have been deprecated. Instead use dist_binom_plot(),
dist_binom_prob() and dist_binom_perc().
See Also
Binomial
4 dist_chi_plot
