---
title: "``l_layer.SpatialPolygons``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```



Layer polygons in SpatialPolygons object

#### Description 

Methods to plot map data defined in the sp package

#### Usage
<pre><code>

## S3 method for class 'SpatialPolygons'
l_layer(widget, x, asSingleLayer = TRUE, ...)

</code></pre>
#### Arguments 

widget * ``widget``: widget path as a string or as an object handle
* ``x ``:  an object defined in the class sp
* ``asSingleLayer ``:   If TRUE then prefer a single layer over groups with nested 1-dimensinal layers
... Arguments 
 forwarded to the relative l_layer function

#### Examples 
```{r}
if (requireNamespace("rworldmap", quietly = TRUE)) {
world <- rworldmap::getMap(resolution = "coarse")
p <- l_plot()
lmap <- l_layer(p, world, asSingleLayer=TRUE)
l_scaleto_world(p)
attr(lmap,'hole')
attr(lmap,'NAME')
}

```


#### Details 

Note that currently loon does neither support holes and ring directions.


#### Value
layer id
References
Applied Spatial Data Analysis with R by Bivand, Roger S. and Pebesma, Edzer and Gomez-Rubio
and Virgilio http://www.springer.com/us/book/9781461476177
See Also
sp, l_layer

