---
title: "``l_layer_hide``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```
### Hide a Layer

#### Description 

A hidden layer is not rendered. If a group layer is set to be hidden then all its descendants are not
rendered either.

#### Usage
<pre><code>

l_layer_hide(widget, layer)

</code></pre>
#### Arguments 

* ``widget``: widget path or layer object of class 'l_layer'
* ``layer``:   layer id. If the widget argument is of class 'l_layer' then the layer argument
is not used

#### Details 

Visibile layers are rendered, invisible ones are not. If any ancestor of a layer is set to be invisible then
the layer is not rendered either. The layer visibility flag can be checked with l_layer_isVisible
and the actual visibility (i.e. are all the ancesters visibile too) can be checked with l_layer_layerVisibility.
Note that layer visibility is not a state of the layer itself, instead is information that is part of the
layer collection (i.e. its parent widget).
Value
0 if success otherwise the function throws an error
See Also
l_layer, l_layer_show, l_layer_isVisible, l_layer_layerVisibility, l_layer_groupVisibility

#### Examples 
```{r}
p <- l_plot()
l <- l_layer_rectangle(p, x=0:1, y=0:1, color="steelblue")
l_layer_hide(p, l)
```