---
title: "``l_layer_groupVisibility``"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Queries visibility status of decendants

#### Description 

Query whether all, part or none of the group layers descendants are visible.

#### Usage

<pre><code>
l_layer_groupVisibility(widget, layer)
</code></pre>

#### Arguments 

* ``widget``: widget path or layer object of class 'l_layer'
* ``layer``:   layer id. If the widget argument is of class 'l_layer' then the layer argument
is not used

#### Details 

Visibile layers are rendered, invisible ones are not. If any ancestor of a layer is set to be invisible then
the layer is not rendered either. The layer visibility flag can be checked with l_layer_isVisible
and the actual visibility (i.e. are all the ancesters visibile too) can be checked with l_layer_layerVisibility.
Note that layer visibility is not a state of the layer itself, instead is information that is part of the
layer collection (i.e. its parent widget).

#### Value
'all', 'part' or 'none' depending on the visibility status of the descendants.
See Also
l_layer, l_layer_show, l_layer_hide, l_layer_isVisible, l_layer_layerVisibility
l_layer_heatImage 123

#### Examples 
```{r}
p <- l_plot()
g <- l_layer_group(p)
l1 <- l_layer_rectangle(p, x=0:1, y=0:1, parent=g)
l2 <- l_layer_oval(p, x=0:1, y=0:1, parent=g)
l_layer_groupVisibility(p, g)
l_layer_hide(p, l2)
l_layer_groupVisibility(p, g)
l_layer_hide(p, l1)
l_layer_groupVisibility(p, g)
l_layer_hide(p, g)
l_layer_groupVisibility(p, g)
```