---
title: "l_layer_contourLines"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```
l_layer_contourLines Layer Contour Lines

#### Description 

This function is a wrapper around contourLines that adds the countourlines to a loon plot which
is based on the cartesian coordinate system.


#### Usage
<pre><code>

l_layer_contourLines(widget, x = seq(0, 1, length.out = nrow(z)),
y = seq(0, 1, length.out = ncol(z)), z, nlevels = 10,
levels = pretty(range(z, na.rm = TRUE), nlevels),
asSingleLayer = TRUE, parent = "root", index = "end", ...)

</code></pre>
#### Arguments 

* ``widget``: widget path as a string or as an object handle
* x locations of grid lines at which the values in z are measured. These must be in ascending order. By default, equally spaced values from 0 to 1 are used. If x is a list, its components x$x and x$y are used for x and y, respectively. If the list has component z this is used for z.
* y see description for the x argument
* z a matrix containing the values to be plotted (NAs are allowed). Note that x can be used instead of z for convenience.
*``nlevels  ``: number of contour levels desired iff levels is not supplied.
* * ``levels``: numeric vector of levels at which to draw contour lines.
* * ``asSingleLayer ``:   If TRUE a lines layer is used for the line, otherwise if FALSE a group with nested
* line layers for each line is created
* ``parent ``:  parent widget path
* index position among its siblings. valid values are 0, 1, 2, ..., 'end'
* ... argumnets forwarded to l_layer_line

#### Details 

For more information run: l_help("learn_R_layer.html#countourlines-heatimage-rasterimage")
Value
layer id of group or lines layer

#### Examples 
```{r}
p <- l_plot()
x <- 10*1:nrow(volcano)
y <- 10*1:ncol(volcano)
lcl <- l_layer_contourLines(p, x, y, volcano)
l_scaleto_world(p)
if (requireNamespace("MASS", quietly = TRUE)) {
p1 <- with(iris, l_plot(Sepal.Length~Sepal.Width, color=Species))
lcl <- with(iris, l_layer_contourLines(p1, MASS::kde2d(Sepal.Width,Sepal.Length)))
p2 <- with(iris, l_plot(Sepal.Length~Sepal.Width, color=Species))
layers <- sapply(split(cbind(iris, color=p2['color']), iris$Species), function(dat) {

kest <- with(dat, MASS::kde2d(Sepal.Width,Sepal.Length))
l_layer_contourLines(p2, kest, color=as.character(dat$color[1]), linewidth=2,
label=paste0(as.character(dat$Species[1]), " contours"))
})
}
```