---
title: "l_layer_texts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
l_layer_texts Layer a texts

#### Description 

Loon's displays that are based on Cartesian coordinates (i.e. scatterplot, histogram and graph display)
allow for layering visual information including polygons, text and rectangles.

#### Usage
<pre><code>

l_layer_texts(widget, x, y, text, color = "gray60", size = 6,
angle = 0, label = "texts", parent = "root", index = 0, ...)

</code></pre>
#### Arguments 

* ``widget``: widget path name as a string
* x the coordinates of line. Alternatively, a single plotting structure, function or any R object with a plot method can be provided as x and y are passed on to xy.coords
* ``y``:  the y coordinates of the line, optional if x is an appropriate structure.
text vector with text strings color color of line
* size font size
* angle text rotation
* ``label``:  label used in the layers inspector
* parent group layer index of the newly added layer in its parent group
... additional state initialization arguments, see l_info_states



#### Examples 
```{r}
p <- l_plot()
l <- l_layer_texts(p, x=1:3, y=3:1, text=c("This is", "a", "test"), size=20)
l_scaleto_world(p)
```

#### Details 

For more information run: l_help("learn_R_layer")
Value
layer object handle, layer id
See Also
l_layer, l_info_states