---
title: "``l_layer_text``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(loon)
```

l_layer_text Layer a text

#### Description 

Loon's displays that are based on Cartesian coordinates (i.e. scatterplot, histogram and graph display)
allow for layering visual information including polygons, text and rectangles.
layer a single character string

#### Usage
<pre><code>

l_layer_text(widget, x, y, text, color = "gray60", size = 6,
angle = 0, label = "text", parent = "root", index = 0, ...)

</code></pre>
#### Arguments 

* ``widget``: widget path name as a string
x coordinate
y coordinate
text character string
color color of text
size size of the font
angle rotation of text
* ``label``:  label used in the layers inspector
parent group layer
index of the newly added layer in its parent group
... additional state initialization Arguments 
, see l_info_states

#### Details 

As a side effect of Tcl's text-based design, it is best to use l_layer_text if one would like to layer
a single character string (and not l_layer_texts with n=1).
For more information run: l_help("learn_R_layer")
Value
layer object handle, layer id
See Also
l_layer, l_info_states

#### Examples 
```{r}
p <- l_plot()
l <- l_layer_text(p, 0, 0, "Hello World")
```