---
title: "descriptr"
author: "Kevin O'Brien"
date: "26 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Package ‘descriptr’
March 20, 2018
Type Package
Title Generate Descriptive Statistics & Explore Statistical
Distributions
Version 0.4.1

#### Description 
  Generate descriptive statistics such as measures of location,
dispersion, frequency tables, cross tables, group summaries and multiple
one/two way tables. Visualize and compute percentiles/probabilities of
normal, t, f, chi square and binomial distributions.
Depends R(>= 3.2.4)
Imports dplyr, forcats, ggplot2, graphics, magrittr, rlang, scales,
shiny, tibble, tidyr
Suggests covr, haven, jsonlite, knitr, lubridate, readr, readxl,
rmarkdown, shinyBS, shinythemes, stringr, testthat, tools,
vdiffr
License MIT + file LICENSE
URL https://descriptr.rsquaredacademy.com/,
https://github.com/rsquaredacademy/descriptr
BugReports https://github.com/rsquaredacademy/descriptr/issues
Encoding UTF-8
LazyData true
VignetteBuilder knitr
RoxygenNote 6.0.1
NeedsCompilation no
Author Aravind Hebbali [aut, cre]
Maintainer Aravind Hebbali <hebbali.aravind@gmail.com>
Repository CRAN
Date/Publication 2018-03-20 09:41:04 UTC
1
2 descriptr
R topics documented:
descript2
dist_binom_plo3
dist_chi_plo. 4
dist_f_plo. . . 5
dist_norm_plo6
dist_. 7
ds_cross_tabl. 9
ds_cs. 10
ds_cva11
ds_extreme_ob11
ds_freq_con. 12
ds_freq_tabl. 13
ds_gmea. . . 14
ds_group_summar. . 14
ds_hmea. . . 16
ds_kurtosi. . 16
ds_launch_shiny_ap. 17
ds_mde18
ds_measures_locatio. 19
ds_measures_symmetr19
ds_measures_variatio20
ds_mod20
ds_multi_stat. 21
ds_oway_table22
ds_percentile. 23
ds_rang23
ds_rinde. . . 24
ds_screene. . 25
ds_skewnes. . 26
ds_std_erro. . 27
ds_summary_stat. . . 27
ds_tailob. . . 28
hs. . . 29
mtcar. 29
Index 30
descriptr descriptr package

#### Description 
 
Generate descriptive statistics and explore statistical distributions
dist_binom_plot 3
dist_binom_plot Visualize binomial distribution

#### Description 
 
Visualize how changes in number of trials and the probability of success affect the shape of the
binomial distribution. Compute & visualize probability from a given quantile and quantiles out of
given probability.

#### Usage 
<pre><code>

dist_binom_plot(n, p)
dist_binom_prob(n, p, s, type = c("lower", "upper", "exact", "interval"))
dist_binom_perc(n, p, tp, type = c("lower", "upper"))

</code></pre>
#### Arguments 
 
n Number of trials.
p Aggregate probability.
s Number of success.
type Lower/upper/exact/interval.
tp Probability of success in a trial.
Value
A list containing the following components:
avg Mean of the binomial distribution,
stdev Standard deviation of the binomial distribution.
prob Probability of success.
Deprecated functions
binom_plot(), binom_prob(), binom_perc() have been deprecated. Instead use dist_binom_plot(),
dist_binom_prob() and dist_binom_perc().
See Also
Binomial
4 dist_chi_plot

#### Examples 
```{r}

# visualize binomial distribution
dist_binom_plot(10, 0.3)
# visualize probability from a given quantile
dist_binom_prob(10, 0.3, 4, type = 'exact')
dist_binom_prob(10, 0.3, 4, type = 'lower')
dist_binom_prob(10, 0.3, 4, type = 'upper')
dist_binom_prob(10, 0.3, c(4, 6), type = 'interval')
# visualize quantiles out of given probability
dist_binom_perc(10, 0.5, 0.05)
dist_binom_perc(10, 0.5, 0.05, "upper")
dist_chi_plot Visualize chi square distribution

#### Description 
 
Visualize how changes in degrees of freedom affect the shape of the chi square distribution. Compute
& visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_chi_plot(df = 3, normal = FALSE)
dist_chi_perc(probs = 0.95, df = 3, type = c("lower", "upper"))
dist_chi_prob(perc, df, type = c("lower", "upper"))

</code></pre>
#### Arguments 
 
* ``df`` :  Degrees of freedom.
normal If TRUE, normal curve with same mean and sd as the chi square distribution is
drawn.
* ``probs ``: Probability value.
type Lower tail or upper tail.
perc Quantile value.
Value
Percentile for the probs based on df and type or probability value for perc based on df and type.
Deprecated functions
chi_plot(), chi_prob() and chi_per() have been deprecated. Instead use dist_chi_plot(),
dist_chi_prob() and dist_chi_perc().
dist_f_plot 5
See Also
Chisquare

#### Examples 
```{r}

# visualize chi square distribution
dist_chi_plot()
dist_chi_plot(df = 5)
dist_chi_plot(df = 5, normal = TRUE)
# visualize quantiles out of given probability
dist_chi_perc(0.165, 8, 'upper')
dist_chi_perc(0.22, 13, 'upper')
# visualize probability from a given quantile.
dist_chi_prob(13.58, 11, 'lower')
dist_chi_prob(15.72, 13, 'upper')
dist_f_plot Visualize f distribution

#### Description 
 
Visualize how changes in degrees of freedom affect the shape of the F distribution. Compute &
visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_f_plot(num_df = 4, den_df = 30, normal = FALSE)
dist_f_perc(probs = 0.95, num_df = 3, den_df = 30, type = c("lower",
"upper"))
dist_f_prob(perc, num_df, den_df, type = c("lower", "upper"))

</code></pre>
#### Arguments 
 
num_* ``df`` :  Degrees of freedom.associated with the numerator of f statistic.
den_* ``df`` :  Degrees of freedom.associated with the denominator of f statistic.
normal If TRUE, normal curve with same mean and sd as the F distribution is drawn.
* ``probs ``: Probability value.
type Lower tail or upper tail.
perc Quantile value.
6 dist_norm_plot
Value
Percentile for the probs based on num_df, den_df and type or probability value for perc based on
num_df, den_df and type.
Deprecated functions
f_plot(), f_prob() and f_per() have been deprecated. Instead use dist_f_plot(), dist_f_prob()
and dist_f_perc().
See Also
FDist

#### Examples 
```{r}

# visualize F distribution
dist_f_plot()
dist_f_plot(6, 10, normal = TRUE)
# visualize probability from a given quantile
dist_f_perc(0.95, 3, 30, 'lower')
dist_f_perc(0.125, 9, 35, 'upper')
# visualize quantiles out of given probability
dist_f_prob(2.35, 5, 32)
dist_f_prob(1.5222, 9, 35, type = "upper")
```


dist_t Visualize t distribution

#### Description 
 
Visualize how degrees of freedom affect the shape of t-distribution, visualize quantiles out of given probability and probability from a given quantile.

#### Usage 
<pre><code>

dist_t_plot(df = 3)
dist_t_perc(probs = 0.95, df = 4, type = c("lower", "upper", "both"))
dist_t_prob(perc, df, type = c("lower", "upper", "interval", "both"))

</code></pre>
#### Arguments 
 
* ``df`` :  Degrees of freedom.
* ``probs ``: Probability value.
* ``type``: Lower tail, upper tail, interval or both.
perc Quantile value.

#### Value
Percentile for the probs based on df and type or probability value for the perc based on df and
type.
Deprecated functions
t_plot(), t_prob() and t_per() have been deprecated. Instead use dist_t_plot(), dist_t_prob()
and dist_t_perc().
See Also
TDist

#### Examples 
```{r}

# visualize t distribution
dist_t_plot()
dist_t_plot(6)
dist_t_plot(df = 8)
# visualize quantiles out of given probability
dist_t_perc(probs = 0.95, df = 4, type = 'lower')
dist_t_perc(probs = 0.35, df = 4, type = 'upper')
dist_t_perc(probs = 0.69, df = 7, type = 'both')
# visualize probability from a given quantile
dist_t_prob(2.045, 7, 'lower')
dist_t_prob(0.945, 7, 'upper')
dist_t_prob(1.445, 7, 'interval')
dist_t_prob(1.6, 7, 'both')
ds_cross_table 9
ds_cross_table Two way table

#### Description 
 
Creates two way tables of categorical variables. The tables created can be visualized as barplots
and mosaicplots.

#### Usage 
<pre><code>

ds_cross_table(data, var1, var2)
## S3 method for class 'ds_cross_table'
plot(x, stacked = FALSE, proportional = FALSE, ...)
ds_twoway_table(data, var1, var2)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* ``var1``:  First categorical variable.
var2 Second categorical variable.
* ``x`` : An object of class cross_table.
stacked If FALSE, the columns of height are portrayed as stacked bars, and if TRUE the
columns are portrayed as juxtaposed bars.
proportional If TRUE, the height of the bars is proportional.
... Further Arguments 
  to be passed to or from methods.

#### Deprecated function
ds_cross_table() has been deprecated. Instead use ds_cross_table().

#### Examples 
```{r}

k <- ds_cross_table(mtcarz, cyl, gear)
k
# bar plots
plot(k)
plot(k, stacked = TRUE)
plot(k, proportional = TRUE)
# alternate
ds_twoway_table(mtcarz, cyl, gear)
10 ds_css
ds_css Corrected Sum of Squares

#### Description 
 
Compute the corrected sum of squares

#### Usage 
<pre><code>

ds_css(x, na.rm = FALSE)

</code></pre>
#### Arguments 
 
* ``x``: a numeric vector containing the values whose mode is to be computed
* ``na.rm`` : a logical value indicating whether NA values should be stripped before the computation
proceeds.

#### Details
Any NA values are stripped from x before computation takes place.

#### Value
Corrected sum of squares of x

#### Deprecated Function
stat_css() has been deprecated. Instead use ds_css().
References
NIST/SEMATECH e-Handbook of Statistical Methods

#### Examples 
```{r}

ds_css(mtcars$mpg)
```



ds_freq_cont Frequency distribution of continuous data

#### Description 
 
Frequency distribution of continuous data by splitting into equidistant intervals created based on the
number of bins specified. hist.ds_freq_cont() creates histogram for the frequency table created
using ds_freq_cont().

#### Usage 
<pre><code>

ds_freq_cont(data, variable, bins = 5)
## S3 method for class 'ds_freq_cont'
plot(x, ...)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* ``variable`` :   Column in data.
* ``bins``: Number of intervals into which the data must be split.
* ``x`` : An object of class ds_freq_cont.
... Further Arguments 
  to be passed to or from methods.

#### Value
A tibble.

#### Deprecated functions
freq_cont() has been deprecated. Instead use ds_freq_cont().

#### See Also
ds_freq_table ds_cross_table

#### Examples 
```{r}

# frequency table
ds_freq_cont(mtcarz, mpg, 4)
# histogram
k <- ds_freq_cont(mtcarz, mpg, 4)
plot(k)
```

ds_freq_table Frequency table

#### Description 
 
Frequency table for factor data and returns the frequency, cumulative frequency, frequency percent and cumulative frequency percent. barplot.ds_freq_table() creates bar plot for the frequency table created using ds_freq_table().

#### Usage 
<pre><code>

ds_freq_table(data, variable)
## S3 method for class 'ds_freq_table'
plot(x, ...)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* ``variable`` :   Column in data.
* ``x`` : An object of class ds_freq_table.
* ... Further Arguments to be passed to or from methods.

#### Value
ds_freq_table returns an object of class "ds_freq_table". An object of class "ds_freq_table"
is a list containing the following components:
ftable Frequency table.

#### Deprecated function
freq_table() has been deprecated. Instead use ds_freq_table().

#### See Also
ds_freq_cont ds_cross_table

#### Examples 
```{r}

# frequency table
ds_freq_table(mtcarz, cyl)
# barplot
k <- ds_freq_table(mtcarz, cyl)
plot(k)
```

ds_gmean Geometric Mean

#### Description 
 
Compute the geometric mean

#### Usage 
<pre><code>

ds_gmean(x, na.rm = FALSE, ...)

</code></pre>
#### Arguments 
 
* ``x``: a numeric vector containing the values whose geometric mean is to be computed
* ``na.rm`` : a logical value indicating whether NA values should be stripped before the computation
proceeds.
... further Arguments   passed to or from other methods #’ @details Any NA values
are stripped from x before computation takes place.

#### Value
Returns the geometric mean of x

#### Deprecated function
gmean() has been deprecated. Instead use ds_gmean().
See Also
ds_hmean mean

#### Examples 
```{r}

ds_gmean(mtcars$mpg)
```

ds_group_summary Groupwise descriptive statistics

#### Description 
 
Descriptive statistics of a continuous variable for the different levels of a categorical variable.
boxplot.group_summary() creates boxplots of the continuous variable for the different levels of
the categorical variable.

#### Usage 
<pre><code>

ds_group_summary(data, gvar, cvar)
## S3 method for class 'ds_group_summary'
plot(x, ...)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* gvar Column in data.
* cvar Column in data.
* x An object of the class ds_group_summary.
* ... Further Arguments to be passed to or from methods.

#### Value
ds_group_summary() returns an object of class "ds_group_summary". An object of class "ds_group_summary"
is a list containing the following components:
stats A data frame containing descriptive statistics for the different levels of the factor
variable.
tidy_stats A tibble containing descriptive statistics for the different levels of the factor
variable.
plotdata Data for boxplot method.
Deprecated function
ds_group_summary() has been deprecated. Instead use ds_group_summary().
See Also
ds_summary_stats

#### Examples 
```{r}

# ds_group summary
ds_group_summary(mtcarz, cyl, mpg)
# boxplot
k <- ds_group_summary(mtcarz, cyl, mpg)
plot(k)
# tibble
k$tidy_stats
```

ds_hmean Harmonic Mean

#### Description 
 
Compute the harmonic mean

#### Usage 
<pre><code>

ds_hmean(x, na.rm = FALSE, ...)

</code></pre>
#### Arguments 
 
* ``x``: a numeric vector containing the values whose harmonic mean is to be computed
* ``na.rm`` : a logical value indicating whether NA values should be stripped before the computation proceeds.
... further arguments   passed to or from other methods #’@details Any NA values are stripped from x before computation takes place.

#### Value
Returns the harmonic mean of x

#### Deprecated function
hmean() has been deprecated. Instead use ds_hmean().

#### See Also
ds_gmean mean

#### Examples 
```{r}

ds_hmean(mtcars$mpg)
```

ds_kurtosis Kurtosis

#### Description 
 
Compute the kurtosis of a probability distribution.

#### Usage 
<pre><code>

ds_kurtosis(x, na.rm = FALSE)

</code></pre>
#### Arguments 
 
* ``x``: a numeric vector containing the values whose kurtosis is to be computed
* ``na.rm`` : a logical value indicating whether NA values should be stripped before the computation
proceeds.
Details
Any NA values are stripped from x before computation takes place.
Value
Kurtosis of x

#### Deprecated Function
kurtosis() has been deprecated. Instead use ds_kurtosis().

#### References
Sheskin, D.J. (2000) Handbook of Parametric and Nonparametric Statistical Procedures, Second
Edition. Boca Raton, Florida: Chapman & Hall/CRC.

#### See Also
ds_skewness

#### Examples 
```{r}

ds_kurtosis(mtcars$mpg)
```
ds_launch_shiny_app Launch Shiny App

#### Description 
 
Launches shiny app

#### Usage 
<pre><code>
ds_launch_shiny_app()
</code></pre>

#### Deprecated Function
launch_descriptr() has been deprecated. Instead use ds_launch_shiny_app().


#### Examples 
```{r}

## Not run:
ds_launch_shiny_app()
## End(Not run)
```

ds_mdev Mean Absolute Deviation

#### Description 
 
Compute the mean absolute deviation about the mean

#### Usage 
<pre><code>

ds_mdev(x, na.rm = FALSE)

</code></pre>
#### Arguments 
 
* ``x``: a numeric vector
* ``na.rm`` : a logical value indicating whether NA values should be stripped before the computation
proceeds.

#### Details
The stat_mdev function computes the mean absolute deviation about the mean. It is different from
mad in stats package as the statistic used to compute the deviations is not median but mean. Any
NA values are stripped from x before computation takes place
Value
Mean absolute deviation of x

#### Deprecated Function
stat_mdev() has been deprecated. Instead use ds_mdev().
See Also
mad

#### Examples 
```{r}

ds_mdev(mtcars$mpg)
```







ds_tailobs Tail Observations

#### Description 
 
Returns the n highest/lowest observations from a numeric vector.

#### Usage 
<pre><code>

ds_tailobs(data, n, type = c("low", "high"))

</code></pre>
#### Arguments 
 
* ``data``: a numeric vector
n number of observations to be returned
type if low, the n lowest observations are returned, else the highest n obervations are
returned
Details
Any NA values are stripped from data before computation takes place.
Value
n highest/lowest observations from data
Deprecated function
tailobs() has been deprecated. Instead use ds_tailobs().
See Also
top_n

#### Examples 
```{r}

ds_tailobs(mtcarz$mpg, 5)
ds_tailobs(mtcarz$mpg, 5, type = "high")
hsb 29
hsb High School and Beyond Data Set

#### Description 
 
A dataset containing demographic information and standardized test scores of high school students.

#### Usage 
<pre><code>

hsb
Format
A data frame with 200 rows and 10 variables:
id id of the student
female gender of the student
race ethnic background of the student
ses socio-economic status of the student
schtyp school type
prog program type
read scores from test of reading
write scores from test of writing
math scores from test of math
science scores from test of science
socst scores from test of social studies
Source
http://www.ats.ucla.edu/stat/spss/whatstat/whatstat.htm
mtcarz mtcarz

#### Description 
 
Copy of mtcars data set with modified variable types

#### Usage 
<pre><code>
mtcarz
</code></pre>

#### Format
An object of class data.frame with 32 rows and 11 columns.
