---
title: "ds_freq_cont"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```

Frequency distribution of continuous data

#### Description 
 
Frequency distribution of continuous data by splitting into equidistant intervals created based on the number of bins specified.
``hist.ds_freq_cont()`` creates histogram for the frequency table created using ``ds_freq_cont()``.

#### Usage 
<pre><code>

ds_freq_cont(data, variable, bins = 5)
## S3 method for class 'ds_freq_cont'
plot(x, ...)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* ``variable`` :   Column in data.
* ``bins``: Number of intervals into which the data must be split.
* ``x`` : An object of class ds_freq_cont.
... Further Arguments 
  to be passed to or from methods.

#### Value
A tibble.

#### Deprecated functions
freq_cont() has been deprecated. Instead use ds_freq_cont().

#### See Also
ds_freq_table ds_cross_table

#### Examples 
```{r}

# frequency table
ds_freq_cont(mtcarz, mpg, 4)
# histogram
k <- ds_freq_cont(mtcarz, mpg, 4)
plot(k)
```