---
title: "``ds_group_summary ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```

Groupwise descriptive statistics

#### Description 
 
Descriptive statistics of a continuous variable for the different levels of a categorical variable.
boxplot.group_summary() creates boxplots of the continuous variable for the different levels of
the categorical variable.

#### Usage 
<pre><code>

ds_group_summary(data, gvar, cvar)
## S3 method for class 'ds_group_summary'
plot(x, ...)

</code></pre>
#### Arguments 
 
* ``data`data.frame or a tibble.
* gvar Column in data.
* cvar Column in data.
* x An object of the class ds_group_summary.
* ... Further Arguments to be passed to or from methods.



#### Examples 
```{r}

# ds_group summary
ds_group_summary(mtcarz, cyl, mpg)
# boxplot
k <- ds_group_summary(mtcarz, cyl, mpg)
plot(k)
# tibble
k$tidy_stats
```

#### Value
ds_group_summary() returns an object of class "ds_group_summary". An object of class "ds_group_summary"
is a list containing the following components:
stats A data frame containing descriptive statistics for the different levels of the factor
variable.
tidy_stats A tibble containing descriptive statistics for the different levels of the factor
variable.
plotdata Data for boxplot method.
Deprecated function
ds_group_summary() has been deprecated. Instead use ds_group_summary().
See Also
ds_summary_stats