---
title: "``ds_screener``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(descriptr)
```


 Screen data

#### Description 
 
Screen data and return details such as variable names, class, levels and missing values. plot.ds_screener()
creates bar plots to visualize of missing observations for each variable in a data set.

#### Usage 
<pre><code>

ds_screener(y)
## S3 method for class 'ds_screener'
plot(x, ...)

</code></pre>
#### Arguments 
 
* y A tibble or a data.frame.
* ``x`` : An object of class ds_screener.
* ... Further Arguments to be passed to or from methods.

#### Value
ds_screener() returns an object of class "ds_screener". An object of class "ds_screener" is a
list containing the following components:
Rows Number of rows in the data frame.
Columns Number of columns in the data frame.
Variables Names of the variables in the data frame.
Types Class of the variables in the data frame.
Count Length of the variables in the data frame.
nlevels Number of levels of a factor variable.
levels Levels of factor variables in the data frame.
Missing Number of missing observations in each variable.
MissingPer Percent of missing observations in each variable.
MissingTotal Total number of missing observations in the data frame.
MissingTotPer Total percent of missing observations in the data frame.
MissingRows Total number of rows with missing observations in the data frame.
MissingCols Total number of columns with missing observations in the data frame.
Deprecated function
screener() has been deprecated. Instead use ds_screener().

#### Examples 
```{r}

# screen data
ds_screener(mtcarz)
```
