---
title: "``yardstick::accuracy``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```
accuracy
Accuracy

#### Description

Accuracy is the proportion of the data that are predicted correctly.

#### Usage
<pre><code>
accuracy(data, ...)
## S3 method for class 'data.frame'
accuracy(data, truth, estimate, na_rm = TRUE, ...)
accuracy_vec(truth, estimate, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data Either a data.frame containing the truth and estimate columns, or a table/matrix
where the true class results should be in the columns of the table.
* ... Not currently used.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() functions, a factor vector.
estimate The column identifier for the predicted class results (that is also factor). As
with truth this can be specified different ways but the primary method is to use
an unquoted variable name. For _vec() functions, a factor vector.
* na_rm A logical value indicating whether NA values should be stripped before the computation proceeds.


#### Examples
```{r}
# Two class
data("two_class_example")
accuracy(two_class_example, truth, predicted)
# Multiclass
library(dplyr)
data(hpc_cv)
hpc_cv %>%
filter(Resample == "Fold01") %>%
accuracy(obs, pred)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
accuracy(obs, pred)
# Weighted macro averaging
hpc_cv %>%
group_by(Resample) %>%
accuracy(obs, pred, estimator = "macro_weighted")
# Vector version
accuracy_vec(two_class_example$truth, two_class_example$predicted)
# Making Class2 the "relevant" level
options(yardstick.event_first = FALSE)
accuracy_vec(two_class_example$truth, two_class_example$predicted)
options(yardstick.event_first = TRUE)
```

#### Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For accuracy_vec(), a single numeric value (or NA).

#### Multiclass
Accuracy extends naturally to multiclass scenarios. Because of this, macro and micro averaging are
not implemented.

#### Author(s)
Max Kuhn4
bal_accuracy
See Also
Other class metrics: bal_accuracy, detection_prevalence, f_meas, j_index, kap, mcc, npv,
ppv, precision, recall, sens, spec
