---
title: "``yardstick::ccc``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```

ccc
Concordance correlation coefficient

#### Description

Calculate the concordance correlation coefficient.

#### Usage
<pre><code>
ccc(data, ...)
## S3 method for class 'data.frame'ccc
7
ccc(data, truth, estimate, bias = FALSE,
na_rm = TRUE, ...)
ccc_vec(truth, estimate, bias = FALSE, na_rm = TRUE, ...)
</code></pre>
#### Arguments

data
...
truth
estimate
bias
na_rm
A data.frame containing the truth and estimate columns.
Not currently used.
The column identifier for the true results (that is numeric). This should be an
unquoted column name although this argument is passed by expression and sup-
ports quasiquotation (you can unquote column names). For _vec() functions, a
numeric vector.
The column identifier for the predicted results (that is also numeric). As with
truth this can be specified different ways but the primary method is to use an
unquoted variable name. For _vec() functions, a numeric vector.
A logical; should the biased estimate of variance be used (as is Lin (1989))?
A logical value indicating whether NA values should be stripped before the
computation proceeds.


#### Examples
```{r}
# Supply truth and predictions as bare column names
ccc(solubility_test, solubility, prediction)
library(dplyr)
set.seed(1234)
size <- 100
times <- 10
# create 10 resamples
solubility_resampled <- bind_rows(
replicate(
n = times,
expr = sample_n(solubility_test, size, replace = TRUE),
simplify = FALSE
),
.id = "resample"
)
# Compute the metric by group
metric_results <- solubility_resampled %>%
group_by(resample) %>%
ccc(solubility, prediction)
metric_results
# Resampled mean estimate
metric_results %>%
summarise(avg_estimate = mean(.estimate))
```

#### Details
ccc() is a metric of both consistency/correlation and accuracy, while metrics such as rmse() are
strictly for accuracy and metrics such as rsq() are strictly for consistency/correlation
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For ccc_vec(), a single numeric value (or NA).

#### Author(s)
Max Kuhn
References
Lin, L. (1989). A concordance correlation coefficient to evaluate reproducibility. Biometrics, 45
(1), 255-268.
Nickerson, C. (1997). A note on "A concordance correlation coefficient to evaluate reproducibility".
Biometrics, 53(4), 1503-1507.

#### See Also
Other numeric metrics: huber_loss_pseudo, huber_loss, mae, mape, mase, rmse, rpd, rpiq,
rsq_trad, rsq, smape
Other consistency metrics: rpd, rpiq, rsq_trad, rsq
Other accuracy metrics: huber_loss_pseudo, huber_loss, mae, mape, mase, rmse, smape8
conf_mat
