---
title: "``yardstick::conf_mat``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```


conf_mat
Confusion Matrix for Categorical Data

#### Description

Calculates a cross-tabulation of observed and predicted classes.

#### Usage
<pre><code>
conf_mat(data, ...)
## S3 method for class 'data.frame'
conf_mat(data, truth, estimate,
dnn = c("Prediction", "Truth"), ...)
## S3 method for class 'conf_mat'
tidy(x, ...)conf_mat
9
## S3 method for class 'conf_mat'
autoplot(object, type = "mosaic", ...)
</code></pre>

#### Arguments

* data A data frame or a base::table().
* ... Options to pass to base::table() (not including dnn). This argument is not
currently used for the tidy method.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
estimate The column identifier for the predicted class results (that is also factor). As
with truth this can be specified different ways but the primary method is to use
an unquoted variable name. For _vec() functions, a factor vector.
dnn A character vector of dimnames for the table.
x A conf_mat object.
object The conf_mat data frame returned from conf_mat().
type Type of plot desired, must be "mosaic" or "heatmap", defaults to "mosaic".


#### Examples
```{r}
library(dplyr)
data("hpc_cv")
# The confusion matrix from a single assessment set (i.e. fold)
cm <- hpc_cv %>%
filter(Resample == "Fold01") %>%
conf_mat(obs, pred)
cm
# Now compute the average confusion matrix across all folds in
# terms of the proportion of the data contained in each cell.
# First get the raw cell counts per fold using the `tidy` method
library(purrr)
library(tidyr)
cells_per_resample <- hpc_cv %>%
group_by(Resample) %>%
conf_mat(obs, pred) %>%
mutate(tidied = map(conf_mat, tidy)) %>%
unnest(tidied)
# Get the totals per resample
counts_per_resample <- hpc_cv %>%
group_by(Resample) %>%
summarize(total = n()) %>%
left_join(cells_per_resample, by = "Resample") %>%
# Compute the proportions
mutate(prop = value/total) %>%
group_by(name) %>%
# Average
summarize(prop = mean(prop))
counts_per_resample
# Now reshape these into a matrix
mean_cmat <- matrix(counts_per_resample$prop, byrow = TRUE, ncol = 4)
rownames(mean_cmat) <- levels(hpc_cv$obs)
colnames(mean_cmat) <- levels(hpc_cv$obs)
round(mean_cmat, 3)
# The confusion matrix can quickly be visualized using autoplot()
library(ggplot2)
autoplot(cm, type = "mosaic")
autoplot(cm, type = "heatmap")
```
Details
For conf_mat() objects, a broom tidy() method has been created that collapses the cell counts by
cell into a data frame for easy manipulation.
There is also a summary() method that computes various classification metrics at once. See summary.conf_mat()
There is a ggplot2::autoplot() method for quickly visualizing the matrix. Both a heatmap and
mosaic type is implemented.
The function requires that the factors have exactly the same levels.
Value
conf_mat() produces an object with class conf_mat. This contains the table and other objects.
tidy.conf_mat() generates a tibble with columns name (the cell identifier) and value (the cell
count).
When used on a grouped data frame, conf_mat() returns a tibble containing columns for the groups
along with conf_mat, a list-column where each element is a conf_mat object.
See Also
summary.conf_mat() for computing a large number of metrics from one confusion matrix.10
detection_prevalence
