---
title: "``yardstick::f_meas"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```


f_meas
F Measure

#### Description

These functions calculate the ``f_meas()`` of a measurement system for finding relevant documents compared to reference results (the truth regarding relevance). Highly related functions are ``recall()`` and ``precision()``.

#### Usage
<pre><code>
f_meas(data, ...)
## S3 method for class 'data.frame'
f_meas(data, truth, estimate, beta = 1,
estimator = NULL, na_rm = TRUE, ...)
f_meas_vec(truth, estimate, beta = 1, estimator = NULL, na_rm = TRUE,
...)
</code></pre>

#### Arguments

* data Either a data.frame containing the truth and estimate columns, or a table/matrix
where the true class results should be in the columns of the table.
* ... Not currently used.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
estimate The column identifier for the predicted class results (that is also factor). As
with truth this can be specified different ways but the primary method is to use
an unquoted variable name. For _vec() functions, a factor vector.
beta A numeric value used to weight precision and recall. A value of 1 is traditionally
used and corresponds to the harmonic mean of the two values but other values
weight recall beta times more important than precision.
estimator One of: "binary", "macro", "macro_weighted", or "micro" to specify the
type of averaging to be done. "binary" is only relevant for the two class case.
The other three are general methods for calculating multiclass metrics. The
default will automatically choose "binary" or "macro" based on estimate.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.

#### Details
The measure "F" is a combination of precision and recall (see below).14
f_meas
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For f_meas_vec(), a single numeric value (or NA).
Relevant level
There is no common convention on which factor level should automatically be considered the
"event" or "positive" result. In yardstick, the default is to use the first level. To change this, a
global option called yardstick.event_first is set to TRUE when the package is loaded. This can
be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass
extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.
Multiclass
Macro, micro, and macro-weighted averaging is available for this metric. The default is to select
macro averaging if a truth factor with more than 2 levels is provided. Otherwise, a standard binary
calculation is done. See vignette("multiclass", "yardstick") for more information.
Implementation
Suppose a 2x2 table with notation:
Predicted
Relevant
Irrelevant
Reference
Relevant
A
C
Irrelevant
B
D
The formulas used here are:
recall = A/(A + C)
precision = A/(A + B)
2
F m eas β = (1 + β ) ∗ precision ∗ recall/((β 2 ∗ precision) + recall)
See the references for discussions of the statistics.


#### Examples
```{r}
# Two class
data("two_class_example")
f_meas(two_class_example, truth, predicted)
# Multiclass
library(dplyr)
data(hpc_cv)
hpc_cv %>%
filter(Resample == "Fold01") %>%
f_meas(obs, pred)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
f_meas(obs, pred)
# Weighted macro averaging
hpc_cv %>%
group_by(Resample) %>%
f_meas(obs, pred, estimator = "macro_weighted")
# Vector version
f_meas_vec(two_class_example$truth, two_class_example$predicted)
# Making Class2 the "relevant" level
options(yardstick.event_first = FALSE)
f_meas_vec(two_class_example$truth, two_class_example$predicted)
options(yardstick.event_first = TRUE)
```
Author(s)
Max Kuhn
References
Buckland, M., & Gey, F. (1994). The relationship between Recall and Precision. Journal of the
American Society for Information Science, 45(1), 12-19.
Powers, D. (2007). Evaluation: From Precision, Recall and F Factor to ROC, Informedness,
Markedness and Correlation. Technical Report SIE-07-001, Flinders Universitygain_capture
15
See Also
Other class metrics: accuracy, bal_accuracy, detection_prevalence, j_index, kap, mcc, npv,
ppv, precision, recall, sens, spec
Other relevance metrics: precision, recall
