---
title: "``yardstick::gain_capture``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```


gain_capture
Gain capture

#### Description

gain_capture() is a measure of performance similar to an AUC calculation, but applied to a gain
curve.16
gain_capture

#### Usage
<pre><code>
gain_capture(data, ...)
## S3 method for class 'data.frame'
gain_capture(data, truth, ..., estimator = NULL,
na_rm = TRUE)
gain_capture_vec(truth, estimate, estimator = NULL, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data A data.frame containing the truth and estimate columns.
* ... A set of unquoted column names or one or more dplyr selector functions to
choose which variables contain the class probabilities. If truth is binary, only
1 column should be selected. Otherwise, there should be as many columns as
factor levels of truth.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
estimator One of "binary", "macro", or "macro_weighted" to specify the type of aver-
aging to be done. "binary" is only relevant for the two class case. The other
two are general methods for calculating multiclass metrics. The default will
automatically choose "binary" or "macro" based on truth.
* na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.
estimate If truth is binary, a numeric vector of class probabilities corresponding to the
"relevant" class. Otherwise, a matrix with as many columns as factor levels of
truth. It is assumed that these are in the same order as the levels of truth.



#### Examples
```{r}
# Two class
data("two_class_example")
gain_capture(two_class_example, truth, Class1)
# Multiclass
library(dplyr)
data(hpc_cv)
# You can use the col1:colN tidyselect syntax
hpc_cv %>%
filter(Resample == "Fold01") %>%
gain_capture(obs, VF:L)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
gain_capture(obs, VF:L)
# Weighted macro averaging18
gain_curve
hpc_cv %>%
group_by(Resample) %>%
gain_capture(obs, VF:L, estimator = "macro_weighted")
# Vector version
# Supply a matrix of class probabilities
fold1 <- hpc_cv %>%
filter(Resample == "Fold01")
gain_capture_vec(
truth = fold1$obs,
matrix(
c(fold1$VF, fold1$F, fold1$M, fold1$L),
ncol = 4
)
)
# Visualize gain_capture() --------------------------------------------------
# Visually, this represents the area under the black curve, but above the
# 45 degree line, divided by the area of the shaded triangle.
library(ggplot2)
autoplot(gain_curve(two_class_example, truth, Class1))
```
#### Details
gain_capture() calculates the area under the gain curve, but above the baseline, and then divides
that by the area under a perfect gain curve, but above the baseline. It is meant to represent the
amount of potential gain "captured" by the model.
The ``gain_capture()`` metric is identical to the accuracy ratio (AR), which is also sometimes called
the gini coefficient. These two are generally calculated on a cumulative accuracy profile curve, but
this is the same as a gain curve. See the Engelmann reference for more information.

#### Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For gain_capture_vec(), a single numeric value (or NA).gain_capture
17
Relevant level
There is no common convention on which factor level should automatically be considered the
"event" or "positive" result. In yardstick, the default is to use the first level. To change this, a
global option called yardstick.event_first is set to TRUE when the package is loaded. This can
be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass
extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.
Multiclass
Macro and macro-weighted averaging is available for this metric. The default is to select macro
averaging if a truth factor with more than 2 levels is provided. Otherwise, a standard binary
calculation is done. See vignette("multiclass", "yardstick") for more information.

#### Author(s)
Max Kuhn
References
Engelmann, Bernd & Hayden, Evelyn & Tasche, Dirk (2003). "Measuring the Discriminative Power
of Rating Systems," Discussion Paper Series 2: Banking and Financial Studies 2003,01, Deutsche
Bundesbank.
See Also
gain_curve() to compute the full gain curve.
Other class probability metrics: mn_log_loss, pr_auc, roc_auc
