

---
title: "``yardstick::huber_loss_pseudo``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```


huber_loss_pseudo
Psuedo-Huber Loss

#### Description

Calculate the Pseudo-Huber Loss, a smooth approximation of huber_loss(). Like huber_loss(),
this is less sensitive to outliers than rmse().

#### Usage
<pre><code>
huber_loss_pseudo(data, ...)
## S3 method for class 'data.frame'
huber_loss_pseudo(data, truth, estimate, delta = 1,
na_rm = TRUE, ...)
huber_loss_pseudo_vec(truth, estimate, delta = 1, na_rm = TRUE, ...)
</code></pre>
#### Arguments

data
...
truth
estimate
A data.frame containing the truth and estimate columns.
Not currently used.
The column identifier for the true results (that is numeric). This should be an
unquoted column name although this argument is passed by expression and sup-
ports quasiquotation (you can unquote column names). For _vec() functions, a
numeric vector.
The column identifier for the predicted results (that is also numeric). As with
truth this can be specified different ways but the primary method is to use an
unquoted variable name. For _vec() functions, a numeric vector.26
huber_loss_pseudo
delta A single numeric value. Defines the boundary where the loss function transi-
tions from quadratic to linear. Defaults to 1.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For huber_loss_pseudo_vec(), a single numeric value (or NA).
Author(s)
James Blair
References
Huber, P. (1964). Robust Estimation of a Location Parameter. Annals of Statistics, 53 (1), 73-101.
Hartley, Richard (2004). Multiple View Geometry in Computer Vision. (Second Edition). Page
619.
See Also
Other numeric metrics: ccc, huber_loss, mae, mape, mase, rmse, rpd, rpiq, rsq_trad, rsq, smape
Other accuracy metrics: ccc, huber_loss, mae, mape, mase, rmse, smape

#### Examples
```{r}
# Supply truth and predictions as bare column names
huber_loss_pseudo(solubility_test, solubility, prediction)
library(dplyr)
set.seed(1234)
size <- 100
times <- 10
# create 10 resamples
solubility_resampled <- bind_rows(
replicate(
n = times,
expr = sample_n(solubility_test, size, replace = TRUE),
simplify = FALSE
),
.id = "resample"
)
# Compute the metric by group
metric_results <- solubility_resampled %>%
group_by(resample) %>%j_index
27
huber_loss_pseudo(solubility, prediction)
metric_results
# Resampled mean estimate
metric_results %>%
summarise(avg_estimate = mean(.estimate))
j_index
