---
title: "``yardstick::huber_loss"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```

## Huber loss

#### Description

Calculate the Huber loss, a loss function used in robust regression. This loss function is less sensitive to outliers than ``rmse()``. This function is quadratic for small residual values and linear for large residual values.

#### Usage
<pre><code>
huber_loss(data, ...)
## S3 method for class 'data.frame'
huber_loss(data, truth, estimate, delta = 1,
na_rm = TRUE, ...)
huber_loss_vec(truth, estimate, delta = 1, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data A data.frame containing the truth and estimate columns.
* ... Not currently used.
* truth The column identifier for the true results (that is numeric). This should be an unquoted column name although this argument is passed by expression and supports quasiquotation (you can unquote column names). For _vec() functions, a
numeric vector.
* ``estimate``: The column identifier for the predicted results (that is also numeric). As with truth this can be specified different ways but the primary method is to use an
unquoted variable name. For ``_vec()`` functions, a numeric vector.
* ``delta``: A single numeric value. Defines the boundary where the loss function transi-
tions from quadratic to linear. Defaults to 1.
* ``na_rm``: A logical value indicating whether NA values should be stripped before the computation proceeds.

#### Examples
```{r}
# Supply truth and predictions as bare column names
huber_loss(solubility_test, solubility, prediction)
library(dplyr)
set.seed(1234)
size <- 100
times <- 10
# create 10 resamples
solubility_resampled <- bind_rows(
replicate(
n = times,
expr = sample_n(solubility_test, size, replace = TRUE),
simplify = FALSE
),
.id = "resample"
)
# Compute the metric by group
metric_results <- solubility_resampled %>%
group_by(resample) %>%
huber_loss(solubility, prediction)
metric_results
# Resampled mean estimate
metric_results %>%
summarise(avg_estimate = mean(.estimate))
```
#### Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For huber_loss_vec(), a single numeric value (or NA).
Author(s)
James Blair

#### References
Huber, P. (1964). Robust Estimation of a Location Parameter. Annals of Statistics, 53 (1), 73-101.
See Also
Other numeric metrics: ccc, huber_loss_pseudo, mae, mape, mase, rmse, rpd, rpiq, rsq_trad,
rsq, smape
Other accuracy metrics: ccc, huber_loss_pseudo, mae, mape, mase, rmse, smape
