---
title: "``yardstick::metrics``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```

metrics
General Function to Estimate Performance

#### Description

This function estimates one or more common performance estimates depending on the class of
truth (see Value below) and returns them in a three column tibble.

#### Usage
<pre><code>
metrics(data, ...)
## S3 method for class 'data.frame'
metrics(data, truth, estimate, ...,
options = list(), na_rm = TRUE)
</code></pre>

#### Arguments

* data A data.frame containing the truth and estimate columns and any columns
specified by ....
* ... A set of unquoted column names or one or more dplyr selector functions to
choose which variables contain the class probabilities. If truth is binary, only
1 column should be selected. Otherwise, there should be as many columns as
factor levels of truth.
* truth The column identifier for the true results (that is numeric or factor). This
should be an unquoted column name although this argument is passed by ex-
pression and support quasiquotation (you can unquote column names).
* estimate The column identifier for the predicted results (that is also numeric or factor).
As with truth this can be specified different ways but the primary method is to
* use an unquoted variable name.
* options A list of named options to pass to pROC::roc() such as direction or smooth.
These options should not include response, predictor, or levels.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.


#### Examples
```{r}
# Accuracy and kappa
metrics(two_class_example, truth, predicted)
# Add on multinomal log loss and ROC AUC by specifying class prob columns
metrics(two_class_example, truth, predicted, Class1)
# Regression metrics
metrics(solubility_test, truth = solubility, estimate = prediction)
# Multiclass metrics work, but you cannot specify any averaging
# for roc_auc() besides the default, hand_till. Use the specific function
# if you need more customization
library(dplyr)
hpc_cv %>%
group_by(Resample) %>%
metrics(obs, pred, VF:L) %>%
print(n = 40)
```
Value
A two column tibble.
• When truth is a factor, there are rows for accuracy() and the Kappa statistic (kap()).
• When truth has two levels and 1 column of class probabilities is passed to ..., there are
rows for the two class versions of mn_log_loss() and roc_auc().
• When truth has more than two levels and a full set of class probabilities are passed to ...,
there are rows for the multiclass version of mn_log_loss() and the Hand Till generalization
of roc_auc().
• When truth is numeric, there are rows for rmse(), rsq(), and mae().42
metric_set
See Also
metric_set()
