---
title: "``yardstick::pr_auc``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```

## ``pr_auc``: Area under the precision recall curve

#### Description

pr_auc() is a metric that computes the area under the precision recall curve. See pr_curve() for
the full curve.

#### Usage

<pre><code>
pr_auc(data, ...)
## S3 method for class 'data.frame'
pr_auc(data, truth, ..., estimator = NULL,
na_rm = TRUE)
pr_auc_vec(truth, estimate, estimator = NULL, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data A data.frame containing the truth and estimate columns.
* ... A set of unquoted column names or one or more dplyr selector functions to
choose which variables contain the class probabilities. If truth is binary, only
1 column should be selected. Otherwise, there should be as many columns as
factor levels of truth.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
* estimator One of "binary", "macro", or "macro_weighted" to specify the type of aver-
aging to be done. "binary" is only relevant for the two class case. The other
two are general methods for calculating multiclass metrics. The default will
automatically choose "binary" or "macro" based on truth.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.
estimate If truth is binary, a numeric vector of class probabilities corresponding to the
"relevant" class. Otherwise, a matrix with as many columns as factor levels of
truth. It is assumed that these are in the same order as the levels of truth.
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For pr_auc_vec(), a single numeric value (or NA).pr_auc
59
Multiclass
Macro and macro-weighted averaging is available for this metric. The default is to select macro
averaging if a truth factor with more than 2 levels is provided. Otherwise, a standard binary
calculation is done. See vignette("multiclass", "yardstick") for more information.
Relevant level
There is no common convention on which factor level should automatically be considered the
"event" or "positive" result. In yardstick, the default is to use the first level. To change this, a
global option called yardstick.event_first is set to TRUE when the package is loaded. This can
be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass
extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.


#### Examples
```{r}
# Two class
data("two_class_example")
pr_auc(two_class_example, truth, Class1)
# Multiclass
library(dplyr)
data(hpc_cv)
# You can use the col1:colN tidyselect syntax
hpc_cv %>%
filter(Resample == "Fold01") %>%
pr_auc(obs, VF:L)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
pr_auc(obs, VF:L)
# Weighted macro averaging
hpc_cv %>%
group_by(Resample) %>%
pr_auc(obs, VF:L, estimator = "macro_weighted")
# Vector version
# Supply a matrix of class probabilities
fold1 <- hpc_cv %>%60
pr_curve
filter(Resample == "Fold01")
pr_auc_vec(
truth = fold1$obs,
matrix(
c(fold1$VF, fold1$F, fold1$M, fold1$L),
ncol = 4
)
)
```
Author(s)
Max Kuhn
See Also
pr_curve() for computing the full precision recall curve.
Other class probability metrics: gain_capture, mn_log_loss, roc_auc
