---
title: "``yardstick::precision"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```


precision
Precision

#### Description

These functions calculate the precision() of a measurement system for finding relevant docu-
ments compared to reference results (the truth regarding relevance). Highly related functions are
recall() and f_meas().

#### Usage
<pre><code>
precision(data, ...)
## S3 method for class 'data.frame'
precision(data, truth, estimate, estimator = NULL,
na_rm = TRUE, ...)
precision_vec(truth, estimate, estimator = NULL, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data Either a data.frame containing the truth and estimate columns, or a table/matrix
where the true class results should be in the columns of the table.
* ... Not currently used.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
* estimate The column identifier for the predicted class results (that is also factor). As
with truth this can be specified different ways but the primary method is to use
an unquoted variable name. For _vec() functions, a factor vector.
estimator One of: "binary", "macro", "macro_weighted", or "micro" to specify the
type of averaging to be done. "binary" is only relevant for the two class case.
The other three are general methods for calculating multiclass metrics. The
default will automatically choose "binary" or "macro" based on estimate.56
precision
na_rm
A logical value indicating whether NA values should be stripped before the
computation proceeds.
Details
The precision is the percentage of predicted truly relevant results of the total number of predicted
relevant results and characterizes the "purity in retrieval performance" (Buckland and Gey, 1994).
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For precision_vec(), a single numeric value (or NA).
Relevant level
There is no common convention on which factor level should automatically be considered the
"event" or "positive" result. In yardstick, the default is to use the first level. To change this, a
global option called yardstick.event_first is set to TRUE when the package is loaded. This can
be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass
extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.
Multiclass
Macro, micro, and macro-weighted averaging is available for this metric. The default is to select
macro averaging if a truth factor with more than 2 levels is provided. Otherwise, a standard binary
calculation is done. See vignette("multiclass", "yardstick") for more information.
Implementation
Suppose a 2x2 table with notation:
Predicted
Relevant
Irrelevant
Reference
Relevant
A
C
Irrelevant
B
D
The formulas used here are:
recall = A/(A + C)
precision = A/(A + B)
F m eas β = (1 + β 2 ) ∗ precision ∗ recall/((β 2 ∗ precision) + recall)
See the references for discussions of the statistics.precision
57
Author(s)
Max Kuhn
References
Buckland, M., & Gey, F. (1994). The relationship between Recall and Precision. Journal of the
American Society for Information Science, 45(1), 12-19.
Powers, D. (2007). Evaluation: From Precision, Recall and F Factor to ROC, Informedness,
Markedness and Correlation. Technical Report SIE-07-001, Flinders University
See Also
Other class metrics: accuracy, bal_accuracy, detection_prevalence, f_meas, j_index, kap,
mcc, npv, ppv, recall, sens, spec
Other relevance metrics: f_meas, recall

#### Examples
```{r}
# Two class
data("two_class_example")
precision(two_class_example, truth, predicted)
# Multiclass
library(dplyr)
data(hpc_cv)
hpc_cv %>%
filter(Resample == "Fold01") %>%
precision(obs, pred)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
precision(obs, pred)
# Weighted macro averaging
hpc_cv %>%
group_by(Resample) %>%
precision(obs, pred, estimator = "macro_weighted")
# Vector version
precision_vec(two_class_example$truth, two_class_example$predicted)
# Making Class2 the "relevant" level
options(yardstick.event_first = FALSE)
precision_vec(two_class_example$truth, two_class_example$predicted)
options(yardstick.event_first = TRUE)58
```
