---
title: "``yardstick::roc_auc``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```



Area under the receiver operator curve

#### Description

``roc_auc()`` is a metric that computes the area under the ROC curve. See ``roc_curve()`` for the full curve.

#### Usage
<pre><code>
roc_auc(data, ...)
## S3 method for class 'data.frame'
roc_auc(data, truth, ..., options = list(),
estimator = NULL, na_rm = TRUE)
roc_auc_vec(truth, estimate, options = list(), estimator = NULL,
na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data A data.frame containing the truth and estimate columns.
* ... A set of unquoted column names or one or more dplyr selector functions to
choose which variables contain the class probabilities. If truth is binary, only
1 column should be selected. Otherwise, there should be as many columns as
factor levels of truth.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
* options A list of named options to pass to pROC::roc() such as direction or smooth.
These options should not include response, predictor, or levels.
estimator One of "binary", "hand_till", "macro", or "macro_weighted" to specify
the type of averaging to be done. "binary" is only relevant for the two class
case. The others are general methods for calculating multiclass metrics. The
default will automatically choose "binary" or "hand_till" based on truth.
* na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.
* estimate If truth is binary, a numeric vector of class probabilities corresponding to the
"relevant" class. Otherwise, a matrix with as many columns as factor levels of
truth. It is assumed that these are in the same order as the levels of truth.


#### Examples
```{r}
# Two class
data("two_class_example")
roc_auc(two_class_example, truth, Class1)
# Multiclassroc_curve
69
library(dplyr)
data(hpc_cv)
# You can use the col1:colN tidyselect syntax
hpc_cv %>%
filter(Resample == "Fold01") %>%
roc_auc(obs, VF:L)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
roc_auc(obs, VF:L)
# Weighted macro averaging
hpc_cv %>%
group_by(Resample) %>%
roc_auc(obs, VF:L, estimator = "macro_weighted")
# Vector version
# Supply a matrix of class probabilities
fold1 <- hpc_cv %>%
filter(Resample == "Fold01")
roc_auc_vec(
truth = fold1$obs,
matrix(
c(fold1$VF, fold1$F, fold1$M, fold1$L),
ncol = 4
)
)
# passing options via a list and _not_ `...`
roc_auc(two_class_example, truth = truth, Class1,
options = list(smooth = TRUE))
```

#### Details
For most methods, ``roc_auc()`` makes no effort to ensure that the supplied class probabilities result in a AUC value above 0.5 (random guessing). However, the Hand, Till (2001) method assumes that the individual AUCs are all above 0.5, so if an AUC value below 0.5 is computed, then 1 is subtracted from it to get the correct result.

Generally, an ROC AUC value is between 0.5 and 1, with 1 being a perfect prediction model. If your value is between 0 and 0.5, then this implies that you have meaningful information in your model, but it is being applied incorrectly because doing the opposite of what the model predicts would result in an AUC >0.5.

#### Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For roc_auc_vec(), a single numeric value (or NA).

#### Relevant level
There is no common convention on which factor level should automatically be considered the "event" or "positive" result. In yardstick, the default is to use the first level. To change this, a global option called yardstick.event_first is set to TRUE when the package is loaded. This can be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.

#### Multiclass
The default multiclass method for computing roc_auc() is to use the method from Hand, Till, (2001). Unlike macro-averaging, this method is insensitive to class distributions like the binary ROC AUC case.
Macro and macro-weighted averaging are still provided, even though they are not the default. In fact, macro-weighted averaging corresponds to the same definition of multiclass AUC given by Provost and Domingos (2001).

#### Author(s)
Max Kuhn

#### References
* Hand, Till (2001). "A Simple Generalisation of the Area Under the ROC Curve for Multiple Class
Classification Problems". Machine Learning. Vol 45, Iss 2, pp 171-186.
Fawcett (2005). "An introduction to ROC analysis". Pattern Recognition Letters. 27 (2006), pp
861-874.
* Provost, F., Domingos, P., 2001. "Well-trained PETs: Improving probability estimation trees",
CeDER Working Paper #IS-00-04, Stern School of Business, New York University, NY, NY 10012.

#### See Also
roc_curve() for computing the full ROC curve.
Other class probability metrics: gain_capture, mn_log_loss, pr_auc
