---
title: "``yardstick::roc_curve``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```



Receiver operator curve

#### Description

roc_curve() constructs the full ROC curve and returns a tibble. See roc_auc() for the area under
the ROC curve.

#### Usage

roc_curve(data, ...)
## S3 method for class 'data.frame'
roc_curve(data, truth, ..., options = list(),70
roc_curve
na_rm = TRUE)
## S3 method for class 'roc_df'
autoplot(object, ...)

#### Arguments

data A data.frame containing the truth and estimate columns.
... A set of unquoted column names or one or more dplyr selector functions to
choose which variables contain the class probabilities. If truth is binary, only
1 column should be selected. Otherwise, there should be as many columns as
factor levels of truth.
truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() func-
tions, a factor vector.
options A list of named options to pass to pROC::roc() such as direction or smooth.
These options should not include response, predictor, or levels.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.
object The roc_df data frame returned from roc_curve().
Details
roc_curve() computes the sensitivity at every unique value of the probability column (in addition
to infinity and minus infinity). If a smooth ROC curve was produced, the unique observed values of
the specificity are used to create the curve points. In either case, this may not be efficient for large
data sets.
There is a ggplot2::autoplot() method for quickly visualizing the curve. This works for binary
and multiclass output, and also works with grouped data (i.e. from resamples). See the 
#### Examples
```{r}.
Value
A tibble with class roc_df or roc_grouped_df having columns specificity and sensitivity.
If an ordinary (i.e. non-smoothed) curve is used, there is also a column for .threshold.
Multiclass
If a multiclass truth column is provided, a one-vs-all approach will be taken to calculate multiple
curves, one per level. In this case, there will be an additional column, .level, identifying the "one"
column in the one-vs-all calculation.
Relevant level
There is no common convention on which factor level should automatically be considered the
"event" or "positive" result. In yardstick, the default is to use the first level. To change this, a
global option called yardstick.event_first is set to TRUE when the package is loaded. This canroc_curve
71
be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass
extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.
Author(s)
Max Kuhn
See Also
Compute the area under the ROC curve with roc_auc().
Other curve metrics: gain_curve, lift_curve, pr_curve

#### Examples
```{r}
library(ggplot2)
library(dplyr)
# Two class - a tibbble is returned
roc_curve(two_class_example, truth, Class1)
# Visualize the curve using ggplot2 manually
roc_curve(two_class_example, truth, Class1) %>%
ggplot(aes(x = 1 - specificity, y = sensitivity)) +
geom_path() +
geom_abline(lty = 3) +
coord_equal() +
theme_bw()
# Or use autoplot
autoplot(roc_curve(two_class_example, truth, Class1))
## Not run:
# Multiclass one-vs-all approach
# One curve per level
hpc_cv %>%
filter(Resample == "Fold01") %>%
roc_curve(obs, VF:L) %>%
autoplot()
# Same as above, but will all of the resamples
hpc_cv %>%
group_by(Resample) %>%
roc_curve(obs, VF:L) %>%
autoplot()
## End(Not run)72
