R squared - traditional

#### Description

Calculate the coefficient of determination using the traditional definition of R squared using sum of
squares. For a measure of R squared that is strictly between (0, 1), see rsq().

#### Usage

rsq_trad(data, ...)
## S3 method for class 'data.frame'
rsq_trad(data, truth, estimate, na_rm = TRUE, ...)
rsq_trad_vec(truth, estimate, na_rm = TRUE, ...)

#### Arguments

data A data.frame containing the truth and estimate columns.
... Not currently used.
truth The column identifier for the true results (that is numeric). This should be an
unquoted column name although this argument is passed by expression and sup-
ports quasiquotation (you can unquote column names). For _vec() functions, a
numeric vector.
estimate The column identifier for the predicted results (that is also numeric). As with
truth this can be specified different ways but the primary method is to use an
unquoted variable name. For _vec() functions, a numeric vector.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.
Details
The two estimates for the coefficient of determination, rsq() and rsq_trad(), differ by their for-
mula. The former guarantees a value on (0, 1) while the latter can generate inaccurate values when
the model is non-informative (see the 
#### Examples
```{r}). Both are measures of consistency/correlation and
not of accuracy.
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For rsq_trad_vec(), a single numeric value (or NA).rsq_trad
79
Author(s)
Max Kuhn
References
Kvalseth. Cautionary note about R 2 . American Statistician (1985) vol. 39 (4) pp. 279-285.
See Also
Other numeric metrics: ccc, huber_loss_pseudo, huber_loss, mae, mape, mase, rmse, rpd, rpiq,
rsq, smape
Other consistency metrics: ccc, rpd, rpiq, rsq

#### Examples
```{r}
# Supply truth and predictions as bare column names
rsq_trad(solubility_test, solubility, prediction)
library(dplyr)
set.seed(1234)
size <- 100
times <- 10
# create 10 resamples
solubility_resampled <- bind_rows(
replicate(
n = times,
expr = sample_n(solubility_test, size, replace = TRUE),
simplify = FALSE
),
.id = "resample"
)
# Compute the metric by group
metric_results <- solubility_resampled %>%
group_by(resample) %>%
rsq_trad(solubility, prediction)
metric_results
# Resampled mean estimate
metric_results %>%
summarise(avg_estimate = mean(.estimate))
# With uninformitive data, the traditional version of R^2 can return
# negative values.
set.seed(2291)
solubility_test$randomized <- sample(solubility_test$prediction)
rsq(solubility_test, solubility, randomized)
rsq_trad(solubility_test, solubility, randomized)80
```
