---
title: "``yardstick::sens``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```


sens
Sensitivity

#### Description

These functions calculate the sens() (sensitivity) of a measurement system compared to a reference
result (the "truth" or gold standard). Highly related functions are spec(), ppv(), and npv().

#### Usage
<pre><code>
sens(data, ...)
## S3 method for class 'data.frame'
sens(data, truth, estimate, estimator = NULL,
na_rm = TRUE, ...)
sens_vec(truth, estimate, estimator = NULL, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data Either a data.frame containing the truth and estimate columns, or a table/matrix
where the true class results should be in the columns of the table.
* ... Not currently used.
* truth The column identifier for the true class results (that is a factor). This should be
an unquoted column name although this argument is passed by expression and
supports quasiquotation (you can unquote column names). For _vec() functions, a factor vector.
estimate The column identifier for the predicted class results (that is also factor). As
with truth this can be specified different ways but the primary method is to use
an unquoted variable name. For _vec() functions, a factor vector.
estimator One of: "binary", "macro", "macro_weighted", or "micro" to specify the type of averaging to be done. "binary" is only relevant for the two class case.
The other three are general methods for calculating multiclass metrics. The default will automatically choose "binary" or "macro" based on estimate.
na_rm A logical value indicating whether NA values should be stripped before the
computation proceeds.


#### Examples
```{r}
# Two class
data("two_class_example")
sens(two_class_example, truth, predicted)
# Multiclass
library(dplyr)
data(hpc_cv)
hpc_cv %>%
filter(Resample == "Fold01") %>%
sens(obs, pred)
# Groups are respected
hpc_cv %>%
group_by(Resample) %>%
sens(obs, pred)
# Weighted macro averaging
hpc_cv %>%
group_by(Resample) %>%
sens(obs, pred, estimator = "macro_weighted")
# Vector version
sens_vec(two_class_example$truth, two_class_example$predicted)
# Making Class2 the "relevant" level
options(yardstick.event_first = FALSE)
sens_vec(two_class_example$truth, two_class_example$predicted)
options(yardstick.event_first = TRUE)
```


#### Details
The sensitivity (sens()) is defined as the proportion of positive results out of the number of samples
which were actually positive. When there are no positive results, sensitivity is not defined and a
value of NA is returned.sens
81
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For sens_vec(), a single numeric value (or NA).
Relevant level
There is no common convention on which factor level should automatically be considered the
"event" or "positive" result. In yardstick, the default is to use the first level. To change this, a
global option called yardstick.event_first is set to TRUE when the package is loaded. This can
be changed to FALSE if the last level of the factor is considered the level of interest. For multiclass
extensions involving one-vs-all comparisons (such as macro averaging), this option is ignored and
the "one" level is always the relevant result.
Multiclass
Macro, micro, and macro-weighted averaging is available for this metric. The default is to select
macro averaging if a truth factor with more than 2 levels is provided. Otherwise, a standard binary
calculation is done. See vignette("multiclass", "yardstick") for more information.
Implementation
Suppose a 2x2 table with notation:
Predicted
Positive
Negative
Reference
Positive
A
C
Negative
B
D
The formulas used here are:
Sensitivity = A/(A + C)
Specif icity = D/(B + D)
P revalence = (A + C)/(A + B + C + D)
P P V = (Sensitivity∗P revalence)/((Sensitivity∗P revalence)+((1−Specif icity)∗(1−P revalence)))
N P V = (Specif icity∗(1−P revalence))/(((1−Sensitivity)∗P revalence)+((Specif icity)∗(1−P revalence)))
See the references for discussions of the statistics.
Author(s)
Max Kuhn82
smape
References
Altman, D.G., Bland, J.M. (1994) “Diagnostic tests 1: sensitivity and specificity,” British Medical
Journal, vol 308, 1552.
See Also
Other class metrics: accuracy, bal_accuracy, detection_prevalence, f_meas, j_index, kap,
mcc, npv, ppv, precision, recall, spec
Other sensitivity metrics: npv, ppv, spec

