---
title: "``yardstick::smape``"
output: html_document
---

```{r setup, include=FALSE}
library(yardstick)
```



Symmetric mean absolute percentage error

#### Description

Calculate the symmetric mean absolute percentage error. This metric is in relative units.

#### Usage
<pre><code>
smape(data, ...)
## S3 method for class 'data.frame'
smape(data, truth, estimate, na_rm = TRUE, ...)
smape_vec(truth, estimate, na_rm = TRUE, ...)
</code></pre>

#### Arguments

* data A data.frame containing the truth and estimate columns.
* ... Not currently used.
* truth The column identifier for the true results (that is numeric). This should be an unquoted column name although this argument is passed by expression and supports quasiquotation (you can unquote column names). For _vec() functions, a numeric vector.
* estimate The column identifier for the predicted results (that is also numeric). As with truth this can be specified different ways but the primary method is to use an unquoted variable name. For _vec() functions, a numeric vector.
* ``na_rm``: A logical value indicating whether NA values should be stripped before the computation proceeds.


#### Examples
```{r}
# Supply truth and predictions as bare column names
smape(solubility_test, solubility, prediction)
library(dplyr)
set.seed(1234)
size <- 100
times <- 10
# create 10 resamples
solubility_resampled <- bind_rows(
replicate(
n = times,
expr = sample_n(solubility_test, size, replace = TRUE),
simplify = FALSE
),
.id = "resample"
)
# Compute the metric by group
metric_results <- solubility_resampled %>%
group_by(resample) %>%
smape(solubility, prediction)
metric_results
# Resampled mean estimate
metric_results %>%
summarise(avg_estimate = mean(.estimate))
```

Details
This implementation of smape() is the "usual definition" where the denominator is divided by two.
Value
A tibble with columns .metric, .estimator, and .estimate and 1 row of values.
For grouped data frames, the number of rows returned will be the same as the number of groups.
For smape_vec(), a single numeric value (or NA).
Author(s)
Max Kuhn, Riaz Hedayati
See Also
Other numeric metrics: ccc, huber_loss_pseudo, huber_loss, mae, mape, mase, rmse, rpd, rpiq,
rsq_trad, rsq
Other accuracy metrics: ccc, huber_loss_pseudo, huber_loss, mae, mape, mase, rmse84
solubility_test
